### 2014-01-09 paper/main.tex
starting a draft

\documentclass{emulateapj}
\submitted{{\it Submitted for publication in ApJL}}
\usepackage{multirow,color,wrapfig,ulem}
\usepackage {graphicx}

\usepackage{graphics}
\usepackage[dvips]{epsfig}

\newcommand{\avg}[1]{\langle{#1}\rangle}  
\newcommand{\nscatt}{\langle N_{\rm  scatt}\rangle}
\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha~}\else{Ly$\alpha$~}\fi}}
\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}   
\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc }\fi}}   
\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc }\fi}}  
\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm
        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm
        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
\newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
\newcommand{\lya}{{Lyman$\alpha$~}}
\newcommand{\clara}{{\texttt{CLARA}}~}
\newcommand{\rand}{{\ifmmode{{\mathcal{R}}}\else{${\mathcal{R}}$ }\fi}}  
\newcommand{\hs}{{\hspace{1mm}}}  
\newcommand{\kms}{{\ifmmode{{\mathrm{\,km\ s}^{-1}}}\else{\,km~s$^{-1}$}\fi}}

% definition to produce a "less than or similar to" symbol
\def\lsim{~\rlap{$<$}{\lower 1.0ex\hbox{$\sim$}}}

% definition to produce a "greater than or similar to" symbol
\def\gsim{~\rlap{$>$}{\lower 1.0ex\hbox{$\sim$}}}

\begin{document}

\title{Cosmic Web} 
\author{
  XXXX\altaffilmark{1},
  YYYY\altaffilmark{2},
  ZZZZ\altaffilmark{3}
}

\altaffiltext{1}{Uni A}
\altaffiltext{2}{Uni B}
\altaffiltext{3}{Uni C}
\begin{abstract}
This
\end{abstract}

\begin{keywords}
{galaxies: high-redshift,galaxies: star formation, line: formation}
\end{keywords}

\section{Introduction}
\label{sec:intro}

\section{Simulation and web finding algorithm}
\label{sec:Simulation}

\section{Results}
\label{sec:results}

\citep{Hillier98}

\begin{table}
\begin{center}
\begin{tabular}{lcccc}\hline\hline
Sample & Peak & Filament & Sheet & Void\\
       & $n$ (\%) & $n$ (\%) & $n$ (\%) & $n$ (\%) \\\hline
2$\sigma$ & 10 (8.1) & 59 (48.3) & 48 (39.3) & 5 (4.0)\\  
3$\sigma$ & 4 (8.5) & 24 (51.0) &  18 (38.2) & 1 (2.1)\\\hline
\end{tabular}
\caption{
Number of pairs in the four different kinds of environmtns. In
parethesis the number indicate the same number as a percentage of the
total population. }
\label{table:models}
\end{center}
\end{table}

\begin{figure*}
\begin{center}
  \includegraphics[width=0.45\textwidth]{align_filament_pos_e1_3S.pdf}
  \includegraphics[width=0.45\textwidth]{align_filament_pos_e3_3S.pdf}\\
  \includegraphics[width=0.45\textwidth]{align_sheet_pos_e1_3S.pdf}
  \includegraphics[width=0.45\textwidth]{align_sheet_pos_e3_3S.pdf}
\end{center}
\caption{Distribution for the alignment.
    \label{fig:alignment}}  
\end{figure*}

\section{Discussion}
\label{sec:discussion}

\section{Conclusions}
\label{sec:conclusions}

\section*{Acknowledgements}

\bibliographystyle{apj}
\bibliography{references}

\end{document}

### 2014-01-21 paper/main.tex
updated table

@@
 2$\sigma$ & 10 (8.1) & 59 (48.3) & 48 (39.3) & 5 (4.0)\\  
-3$\sigma$ & 4 (8.5) & 24 (51.0) &  18 (38.2) & 1 (2.1)\\\hline
+3$\sigma$ & 4 (8.5) & 24 (51.0) &  18 (38.2) & 1 (2.1)\\
+General & 1307 (23.8) & 1470 (26.8) & 1769 (32.3) & 927 (16.9)\\\hline
 \end{tabular}
@@
 Number of pairs in the four different kinds of environmtns. In
-parethesis the number indicate the same number as a percentage of the
+parethesis the same number as a percentage of the
 total population. }

### 2014-01-31 paper/main.tex
new table
new plots in the draft

@@
 parethesis the same number as a percentage of the
-total population. }
-\label{table:models}
+total population. 
+\label{table:models}}
 \end{center}
@@
 
-\begin{figure*}
+\begin{table}
 \begin{center}
-  \includegraphics[width=0.45\textwidth]{align_filament_pos_e1_3S.pdf}
-  \includegraphics[width=0.45\textwidth]{align_filament_pos_e3_3S.pdf}\\
-  \includegraphics[width=0.45\textwidth]{align_sheet_pos_e1_3S.pdf}
-  \includegraphics[width=0.45\textwidth]{align_sheet_pos_e3_3S.pdf}
+\begin{tabular}{lccc}\hline\hline
+Sample & $\langle\hat{e}_1\cdot \hat{n}\rangle$ & $\langle\hat{e}_2\cdot \hat{n}\rangle$ & $\langle\hat{e}_3\cdot \hat{n}\rangle$\\\hline
+2$\sigma$ & 0.56 & 0.53 &  0.33\\
+3$\sigma$ & 0.51 & 0.51 &  0.46\\
+General & 0.54 & 0.52 & 0.40\\\hline
+\end{tabular}
+\caption{Average values for the cosinus between the three eigenvectors and the vector normal to the orbital plane.
+\label{table:mu}}
 \end{center}
-\caption{Distribution for the alignment.
-    \label{fig:alignment}}  
-\end{figure*}
+\end{table}
+
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.45\textwidth]{density_histogram.eps}
+\end{center}
+\caption{Overdensity distribution for the pairs in the three samples.
+    \label{fig:density}}  
+\end{figure}
+
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.45\textwidth]{FA_histogram.eps}
+\end{center}
+\caption{Integrated Fractional Anisotropy distribution for the pairs in the three samples.
+    \label{fig:FA}}  
+\end{figure}
+
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.45\textwidth]{FA_delta_scatter.eps}
+\end{center}
+\caption{Density and Fractional Anisotropy distribution for the pairs in the general and $3\sigma$ samples.
+    \label{fig:FA}}  
+\end{figure}
 

### 2014-01-31 paper/main.tex
describing the algorithm

@@
 \label{sec:Simulation}
+
+\subsection{Cosmic web identification}
+The web finding algorithm is based on the tidal tensor computed as the
+Hessian of the  gravitational potential field
+
+\begin{equation}
+T_{ij} = \frac{\partial^2 \psi}{\partial r_i \partial r_j}, 
+\end{equation}
+where $r_{i}$, $i=1,2,3$ refers to the three spatial comoving
+coordiates.
+
+This tensor is real and symmetric, which means that can be
+diagonalized. We note the eigenvalues $\lambda_1\geq \lambda_2\geq
+\lambda_3$ and their corresponding eigenvectors $\hat{e}_1$,
+$\hat{e}_2$ and $\hat{e}_3$. The web classification compares each one
+of the three eigenvalues to a threshold value $\lambda_{\rm th}$.
+If the three, two, one or zero eigenvalues are larger than this threshold the region es classified as peak, filament, sheet or void, respectively.
+
+In \cite{Tweb} we perform a detailed study for the topology of the
+cosmic web and its visual counterpart as a function of the parameter
+$\lambda_{\rm th}$. We find that reasonable results in terms of the
+volume fraction occupied by voids, the visual inspection and the halo
+populations in each web type can be reached by values of $0.2<\lambda_{\rm
+th}<0.4$. In this paper we choose the value of $\lambda_{\rm
+  th}=0.3$. We have veryfied that the main trends reported in this
+paper are unsensitive to the choice of that parameter, as long as it
+is in the range already quoted.
+
+The algorithm to compute the potential is grid based. First we
+interpolate the potential into a cubic grid and smooth it with a
+gaussian kernel. Then we obtain the gravitational potential and use
+finite differences to compute the Hessian at every point in the
+grid. Physically speaking, the cosmic web features are scale
+dependent and the grid size has to be chosen with respect to the
+physical scales of the problem at hand.
+
+In our case we have used a grid size on and a gaussian smoothing with
+two times larger as the typical separation between the two
+halos in the Local Group. The objective is to have both halos in the
+pair a common environment. In this paper we use a grid spacing of
+$s=1.024$ \hMpc, corresponding to a $256^3$ grid in the Bolshoi
+volume. The scale for the gaussian smoothing uses the same value.
 

### 2014-01-31 paper/main.tex
FA paragraph

@@
 
+\subsection{The Bolshoi simulation}
+
 \subsection{Cosmic web identification}
@@
 
+The fractional anisotropy (FA) \citep{Libeskind2013} is a quantity
+that measures the relative strength of the three eigenvalues and
+therefore can be interpreted as the relative strenght of
+compression/tension exterted by the tidal field. It is defined as:
+
+\begin{equation}
+FA=
+\end{equation}
+%
+an additional advantage of the FA is that it does not depend on the
+choice of $\lambda_{\rm th}$ and can be used as a broad gauge of the
+kinds of tidal forces on the Local Group.
+
 The algorithm to compute the potential is grid based. First we
-interpolate the potential into a cubic grid and smooth it with a
+interpolate the density into a cubic grid and smooth it with a
 gaussian kernel. Then we obtain the gravitational potential and use
@@
 
+\section{Local Group Samples}
+
 \section{Results}
@@
 
-\citep{Hillier98}
+The first results we explore is the kind of environment occupied by
+our LGs. We find that LGs in the restricted $2\sigma$ and $3\sigma$
+samples prefer by large to be in filaments and sheets. Almost $\sim 50\%$ of the
+pairs in both cases can be found in filaments while $\sim 40\%$ can be
+found in sheets. This proportion is in stark contrast to the
+environments for the general pair sample. In that case only $\sim
+27\%$ and $\sim 33\%$ can be found in filaments and sheets,
+repectively. There is a considerable fraction of pairs that are
+located in peaks ($\sim 25\%$) and voids ($\sim 15\%$). These results
+and the exact numbers are presented in Table \ref{table:web_type}.
 
@@
 total population. 
-\label{table:models}}
+\label{table:web_type}}
 \end{center}

### 2014-02-04 paper/main.tex
more text

@@
 \begin{equation}
-T_{ij} = \frac{\partial^2 \psi}{\partial r_i \partial r_j}, 
+T_{ij} = \frac{\partial^2 \phi}{\partial r_i \partial r_j}, 
 \end{equation}
 where $r_{i}$, $i=1,2,3$ refers to the three spatial comoving
-coordiates.
+coordiates and $\phi$ is the gravitational potential renormalized to
+follow the following Poisson equation $\nabla\phi=\delta$ where
+$\delta$ is the matter overdensity.
 
@@
 \begin{equation}
-FA=
+{\mathrm FA}=\frac{1}{\sqrt{3}}\sqrt{\frac{(\lambda_1- \lambda_3)^2 + (\lambda_2 - \lambda_3)^2 + (\lambda_1 - \lambda_2)^2}{\lambda_1^2+\lambda_2^2 + \lambda_3^2}}.
 \end{equation}
 %
-an additional advantage of the FA is that it does not depend on the
+An additional advantage of the FA is that it does not depend on the
 choice of $\lambda_{\rm th}$ and can be used as a broad gauge of the
@@
        & $n$ (\%) & $n$ (\%) & $n$ (\%) & $n$ (\%) \\\hline
-2$\sigma$ & 10 (8.1) & 59 (48.3) & 48 (39.3) & 5 (4.0)\\  
-3$\sigma$ & 4 (8.5) & 24 (51.0) &  18 (38.2) & 1 (2.1)\\
+2$\sigma$ & 4 (8.5) & 24 (51.0) &  18 (38.2) & 1 (2.1)\\
+3$\sigma$ & 10 (8.1) & 59 (48.3) & 48 (39.3) & 5 (4.0)\\  
 General & 1307 (23.8) & 1470 (26.8) & 1769 (32.3) & 927 (16.9)\\\hline
@@
 \end{table}
+
+The next result is related to the matter overdensity for the LG
+samples. Figure \ref{fig:density} shows that the range of
+overdensities for the general pair sample spans almost two orders of
+magnitude from underdense regions $\delta<0$ to high density regions
+$\delta\sim 30$, with a distribution peaking around $\delta \sim
+0$. In contrast the $2\sigma$ and $3\sigma$ samples are located within
+a narrower range of overdensities $0.0<\delta<4.0$ peaking at $\delta
+\sim 1.5$. These values are consistent with the fact that these
+samples are mostly found in filaments and sheets.
+
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.45\textwidth]{density_histogram.eps}
+\end{center}
+\caption{Overdensity distribution for the pairs in the three samples.
+    \label{fig:density}}  
+\end{figure}
+
+In Figure \ref{fig:FA} we show the integrated distribution for the
+Fractional Anisotropy in the tree samples. The General Sample clusters
+towards values of ${\mathrm FA}\sim 1.0$, while the $2\sigma$ and
+$3\sigma$ prefer values around $0.6$.
+
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.45\textwidth]{FA_histogram.eps}
+\end{center}
+\caption{Integrated Fractional Anisotropy distribution for the pairs
+  in the three samples. 
+    \label{fig:FA}}  
+\end{figure}
+
+In Figure \ref{fig:delta_FA} we present a joint scatter plot for the
+overdensity and fractional anisotropy. For clarity we only include the
+general and $3\sigma$ samples. In this plane we observe from the general
+sample that there are broad correlations between the overdensity and
+the fractional anisotropy.
+
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.45\textwidth]{FA_delta_scatter.eps}
+\end{center}
+\caption{Density and Fractional Anisotropy distribution for the pairs
+  in the general and $3\sigma$ samples. 
+    \label{fig:delta_FA}}  
+\end{figure}
 
@@
 
-\begin{figure}
-\begin{center}
-  \includegraphics[width=0.45\textwidth]{density_histogram.eps}
-\end{center}
-\caption{Overdensity distribution for the pairs in the three samples.
-    \label{fig:density}}  
-\end{figure}
-
-\begin{figure}
-\begin{center}
-  \includegraphics[width=0.45\textwidth]{FA_histogram.eps}
-\end{center}
-\caption{Integrated Fractional Anisotropy distribution for the pairs in the three samples.
-    \label{fig:FA}}  
-\end{figure}
-
-\begin{figure}
-\begin{center}
-  \includegraphics[width=0.45\textwidth]{FA_delta_scatter.eps}
-\end{center}
-\caption{Density and Fractional Anisotropy distribution for the pairs in the general and $3\sigma$ samples.
-    \label{fig:FA}}  
-\end{figure}
-
 \section{Discussion}

### 2014-02-13 paper/main.tex

@@
 
+\newcommand{\lcdm}{$\Lambda$CDM }
+\newcommand{\mpc}{\rm{Mpc}}
 \newcommand{\avg}[1]{\langle{#1}\rangle}  
@@
 
-\title{Cosmic Web} 
+\title{The Local Group in the Cosmic Web} 
 \author{
@@
 \begin{keywords}
-{galaxies: high-redshift,galaxies: star formation, line: formation}
+{galaxies: Local Group --- dark matter}
 \end{keywords}
@@
 
+%lg rare
+The configuration of galaxies in the Local Group (LG hereafter) is quite rare to find in the local Universe and in cosmological simulations. 
+The LG is dominated by the two big spirals MW and M31, the next most-luminous galaxy is M33 which is $\sim 10$ times less massive than M31, followed by several less luminous dwarf galaxies, up to a distance of $\sim 3$\mpc.
+The velocity vector of M31, with a low tangential velocity is consistent to a head-on collision orbit toward the MW \citep{2008MNRAS.386..461C,2012ApJ...753....8V,2012ApJ...753....7S}.
+Another feature of the Local group is the relatively low velocity dispersion of nearby galaxies up to $\sim 8$ Mpc \citep[][and references therein]{1975ApJ...196..313S,2011MNRAS.415L..16A}.
+Environment around the Local Group has density quite
+close to the average density of the universe \citep{2003ApJ...596...19K,2005AJ....129..178K}.
+In addition, the closest massive galaxy cluster, the Virgo Cluster, is $\approx 16.5\ \mpc$ away \citep{2007ApJ...655..144M}.
+
+All this combination of features make LG analogues very rare to find.
+Using numerical simulatons \citet{lganalogues} found less than $2\%$ MW-sized halos reside in a pair similar to MW-M31 and in a similar environment.
+Furthermore, if we select pairs constrained within $2\sigma$ error fron current observational measurements of the velocity components and distance to M31, there are only $88$ systems in a cube of $250$ \hmpc side.
+\citet{2013ApJ...767L...5F} also study MW-M31 pairs in numerical simulations finding the typical quantities characterizing the orbital parameters of the LG are rare among typical pairs, but not enough to challenge the \lcdm model.
+Another definition of LG analogues is made by \citet{2008MNRAS.384.1459L}, but despite differences ocurr in the definitions and resulting fraction of LG analogues, all are in agreement with a low frequency of these pairs.
+%lw08 also look lg analogues
+
+%larger scales & lg env
+To understand better the properties of the LG and how this uncommon pair configuration fit in the cosmological context, an immediate question arise.
+What else can we say of the LG at larger scales?.
+In particular, which are the typical/prefered locations of these systems within the Cosmic Web?.
+Looking the LG at larger scales we have it is located in a difuse and warped filament/wall conecting Virgo Cluster with Fornax Cluster, some nearby galaxies and groups members of this large structure are the Maffei group, NGC $6744$, NGC $5128$, $M101$, $M81$, $NGC1023$, Cen A group.
+At this scale, there is no evident alignment of the MW-M31 orbital plane with the local filament or the Virgo-Fornax direction.
+However, if we look in a smaller volume below scales of $\sim 6$ \mpc, there is a clear alignment of th the MW-M31 orbit with a local plane as shown by figure $3$ in \citet{2013AJ....146...69C}.
+
+%this paper.
+In this paper we will study the large scale environment of LG analogues using the Bolshoi simulation, in particular which kind of structures they reside and if there is any correlation or alignment with the cosmic web.
+Environment is defined by the cosmic web components identified by \citet{Tweb}, and we use the LG analogues computed by \citet{lganalogues}.
+
+Paper is organized ...
+
 \section{Simulation and web finding algorithm}
@@
 \subsection{The Bolshoi simulation}
+We use the Bolshoi simulation of $\Lambda$CDM cosmology: $\Omega_{\rm m}=1-\Omega_{\Lambda}=0.27$, $H_0=70\,\rm km/s/Mpc$, $\sigma_8=0.82$, $n_s=0.95$ \citep{2011ApJ...740..102K}, compatible with the constraints from the WMAP satellite \citep{hinshaw_etal13}.
+The simulation followed evolution of dark matter in a $250 \hmpc$ box with spatial resolution of $\approx 1h^{-1}$~kpc and mass resolution of $m_{\rm p}=1.35\times 10^8\ \rm M_{\odot}$.
+Halos are identified with the BDM algorithm  \citep{1997astro.ph.12217K}.
+The BDM algorithm is  a spherical overdensity halo finding algorithm and is designed to identify both host halos and subhalos.
 
@@
 
-\section{Local Group Samples}
+\section{Local Group Analogues}
+
+To construct a sample of the MW-M31 pairs at $z\approx 0$, we use a series of simulation snapshots  at $z<0.1$ (i.e.
+in the last $\approx 1.3$ Gyr before present) spaced by $\approx 150-250$ Myr.
+This is done because a particular configuration of MW and M31 is transient and would correspond to a relatively small number of systems at one snapshot.
+By using multiple snapshots we can increase the sample of systems in such configuration during a period of time in which secular cosmological evolution is small.
+Pairs are selected allowing a wide range of masses, following an isolation critera, constraining by orbital measurements such as radial, tangential velocity and separation of the pair, and local environment constrains such as local velocity dispersion and local overdensity within a sphere of radius $5$ \mpc.
+A full description of the selection criteria can be found in \citet{lganalogues,sat}.
+
+We define two samples according to the tolerance in the selection constraints:
+A sample named $2\sigma$, correspondig to LG analogues constrained by two times the observational errors in the orbital values (radial velocity, tangential velocity, and separation), and a more relaxed sample named $3\sigma$ for LG analogues constrained by three times observational errors accordingly.
+The number of pairs in each sample is $46$ and $120$ respectively, notice we have less pairs than in \citet{lganalogues} results, since we removed pairs which are too close at $z=0$, i.e.
+their virial radii overlaps, also we removed a couple pairs who merged or change their mass more than $20\%$ at present time since they were detected at $z<0.1$.
 

### 2014-04-24 paper/main.tex
updated figures

@@
 
-\title{The Local Group in the Cosmic Web} 
+\title{The Place of the Local Group in the Cosmic Web} 
 \author{
@@
 The LG is dominated by the two big spirals MW and M31, the next most-luminous galaxy is M33 which is $\sim 10$ times less massive than M31, followed by several less luminous dwarf galaxies, up to a distance of $\sim 3$\mpc.
-The velocity vector of M31, with a low tangential velocity is consistent to a head-on collision orbit toward the MW \citep{2008MNRAS.386..461C,2012ApJ...753....8V,2012ApJ...753....7S}.
-Another feature of the Local group is the relatively low velocity dispersion of nearby galaxies up to $\sim 8$ Mpc \citep[][and references therein]{1975ApJ...196..313S,2011MNRAS.415L..16A}.
-Environment around the Local Group has density quite
-close to the average density of the universe \citep{2003ApJ...596...19K,2005AJ....129..178K}.
-In addition, the closest massive galaxy cluster, the Virgo Cluster, is $\approx 16.5\ \mpc$ away \citep{2007ApJ...655..144M}.
+The velocity vector of M31, with a low tangential velocity is
+consistent to a head-on collision orbit toward the MW
+\citep{2008MNRAS.386..461C,2012ApJ...753....8V,2012ApJ...753....7S}.
 
-All this combination of features make LG analogues very rare to find.
-Using numerical simulatons \citet{lganalogues} found less than $2\%$ MW-sized halos reside in a pair similar to MW-M31 and in a similar environment.
-Furthermore, if we select pairs constrained within $2\sigma$ error fron current observational measurements of the velocity components and distance to M31, there are only $88$ systems in a cube of $250$ \hmpc side.
-\citet{2013ApJ...767L...5F} also study MW-M31 pairs in numerical simulations finding the typical quantities characterizing the orbital parameters of the LG are rare among typical pairs, but not enough to challenge the \lcdm model.
-Another definition of LG analogues is made by \citet{2008MNRAS.384.1459L}, but despite differences ocurr in the definitions and resulting fraction of LG analogues, all are in agreement with a low frequency of these pairs.
+Another feature of the Local group is the relatively low velocity
+dispersion of nearby galaxies up to $\sim 8$ Mpc \citep[][and
+  references therein]{1975ApJ...196..313S,2011MNRAS.415L..16A}. 
+Environment around the Local Group has density quite close to the
+average density of the universe
+\citep{2003ApJ...596...19K,2005AJ....129..178K}. In addition, the
+closest massive galaxy cluster, the Virgo Cluster, is $\approx
+16.5\ \mpc$ away \citep{2007ApJ...655..144M}.
+
+All this combination of features make LG analogues very rare to
+find. Using numerical simulatons \citet{lganalogues} found less than
+$2\%$ MW-sized halos reside in a pair similar to MW-M31 and in a
+similar environment. Furthermore, if we select pairs constrained
+within $2\sigma$ error fron current observational measurements of the
+velocity components and distance to M31, there are only $88$ systems
+in a cube of $250$ \hmpc side.
+
+\citet{2013ApJ...767L...5F} also study MW-M31 pairs in numerical
+simulations finding the typical quantities characterizing the orbital
+parameters of the LG are rare among typical pairs, but not enough to
+challenge the \lcdm model. 
+Another definition of LG analogues is made by
+\citet{2008MNRAS.384.1459L}, but despite differences ocurr in the
+definitions and resulting fraction of LG analogues, all are in
+agreement with a low frequency of these pairs. 
 %lw08 also look lg analogues
@@
 %larger scales & lg env
-To understand better the properties of the LG and how this uncommon pair configuration fit in the cosmological context, an immediate question arise.
-What else can we say of the LG at larger scales?.
-In particular, which are the typical/prefered locations of these systems within the Cosmic Web?.
-Looking the LG at larger scales we have it is located in a difuse and warped filament/wall conecting Virgo Cluster with Fornax Cluster, some nearby galaxies and groups members of this large structure are the Maffei group, NGC $6744$, NGC $5128$, $M101$, $M81$, $NGC1023$, Cen A group.
-At this scale, there is no evident alignment of the MW-M31 orbital plane with the local filament or the Virgo-Fornax direction.
-However, if we look in a smaller volume below scales of $\sim 6$ \mpc, there is a clear alignment of th the MW-M31 orbit with a local plane as shown by figure $3$ in \citet{2013AJ....146...69C}.
+To understand better the properties of the LG and how this uncommon
+pair configuration fit in the cosmological context, an immediate
+question arise. What else can we say of the LG at larger scales?. In
+particular, which are the typical/prefered locations of these systems
+within the Cosmic Web?.
+
+Looking the LG at larger scales we have it is located in a difuse and
+warped filament/wall conecting Virgo Cluster with Fornax Cluster, some
+nearby galaxies and groups members of this large structure are the
+Maffei group, NGC $6744$, NGC $5128$, $M101$, $M81$, $NGC1023$, Cen A
+group. At this scale, there is no evident alignment of the MW-M31
+orbital plane with the local filament or the Virgo-Fornax direction.
+
+However, if we look in a smaller volume below scales of $\sim 6$ \mpc,
+there is a clear alignment of th the MW-M31 orbit with a local plane
+as shown by figure $3$ in \citet{2013AJ....146...69C}.
 
 %this paper.
-In this paper we will study the large scale environment of LG analogues using the Bolshoi simulation, in particular which kind of structures they reside and if there is any correlation or alignment with the cosmic web.
-Environment is defined by the cosmic web components identified by \citet{Tweb}, and we use the LG analogues computed by \citet{lganalogues}.
+In this paper we will study the large scale environment of LG
+analogues using the Bolshoi simulation, in particular which kind of
+structures they reside and if there is any correlation or alignment
+with the cosmic web.  
+Environment is defined by the cosmic web components identified by
+\citet{Tweb}, and we use the LG analogues computed by
+\citet{lganalogues}.
 
@@
 \subsection{The Bolshoi simulation}
-We use the Bolshoi simulation of $\Lambda$CDM cosmology: $\Omega_{\rm m}=1-\Omega_{\Lambda}=0.27$, $H_0=70\,\rm km/s/Mpc$, $\sigma_8=0.82$, $n_s=0.95$ \citep{2011ApJ...740..102K}, compatible with the constraints from the WMAP satellite \citep{hinshaw_etal13}.
-The simulation followed evolution of dark matter in a $250 \hmpc$ box with spatial resolution of $\approx 1h^{-1}$~kpc and mass resolution of $m_{\rm p}=1.35\times 10^8\ \rm M_{\odot}$.
-Halos are identified with the BDM algorithm  \citep{1997astro.ph.12217K}.
-The BDM algorithm is  a spherical overdensity halo finding algorithm and is designed to identify both host halos and subhalos.
+We use the Bolshoi simulation of $\Lambda$CDM cosmology: $\Omega_{\rm
+  m}=1-\Omega_{\Lambda}=0.27$, $H_0=70\,\rm km/s/Mpc$,
+$\sigma_8=0.82$, $n_s=0.95$ \citep{2011ApJ...740..102K}, compatible
+with the constraints from the WMAP satellite
+\citep{hinshaw_etal13}. The simulation followed evolution of dark
+matter in a $250 \hmpc$ box with spatial resolution of $\approx
+1h^{-1}$~kpc and mass resolution of $m_{\rm p}=1.35\times 10^8\ \rm
+M_{\odot}$. Halos are identified with the BDM algorithm
+\citep{1997astro.ph.12217K}. The BDM algorithm is  a spherical
+overdensity halo finding algorithm and is designed to identify both
+host halos and subhalos.
 
@@
 
-The fractional anisotropy (FA) \citep{Libeskind2013} is a quantity
-that measures the relative strength of the three eigenvalues and
-therefore can be interpreted as the relative strenght of
-compression/tension exterted by the tidal field. It is defined as:
+The ellipticity and the prolatenes are quantities that measure the
+relative strength of the three eigenvalues. They are defined as
+follows
 
 \begin{equation}
-{\mathrm FA}=\frac{1}{\sqrt{3}}\sqrt{\frac{(\lambda_1- \lambda_3)^2 + (\lambda_2 - \lambda_3)^2 + (\lambda_1 - \lambda_2)^2}{\lambda_1^2+\lambda_2^2 + \lambda_3^2}}.
+e= \frac{\lambda_3 - \lambda_1}{2(\lambda_1 + \lambda_2 + \lambda_3)}, 
 \end{equation}
-%
-An additional advantage of the FA is that it does not depend on the
-choice of $\lambda_{\rm th}$ and can be used as a broad gauge of the
-kinds of tidal forces on the Local Group.
+
+\begin{equation}
+p= \frac{\lambda_1 + \lambda_3 - 2\lambda_2}{2(\lambda_1 + \lambda_2 +
+  \lambda_3)}.
+\end{equation}
 
@@
 
-To construct a sample of the MW-M31 pairs at $z\approx 0$, we use a series of simulation snapshots  at $z<0.1$ (i.e.
-in the last $\approx 1.3$ Gyr before present) spaced by $\approx 150-250$ Myr.
-This is done because a particular configuration of MW and M31 is transient and would correspond to a relatively small number of systems at one snapshot.
-By using multiple snapshots we can increase the sample of systems in such configuration during a period of time in which secular cosmological evolution is small.
-Pairs are selected allowing a wide range of masses, following an isolation critera, constraining by orbital measurements such as radial, tangential velocity and separation of the pair, and local environment constrains such as local velocity dispersion and local overdensity within a sphere of radius $5$ \mpc.
-A full description of the selection criteria can be found in \citet{lganalogues,sat}.
+To construct a sample of the MW-M31 pairs at $z\approx 0$, we use a
+series of simulation snapshots  at $z<0.1$ (i.e. in the last $\approx
+1.3$ Gyr before present) spaced by $\approx 150-250$ Myr. This is done
+because a particular configuration of MW and M31 is transient and
+would correspond to a relatively small number of systems at one
+snapshot. By using multiple snapshots we can increase the sample of
+systems in such configuration during a period of time in which secular
+cosmological evolution is small.
+
+Pairs are selected allowing a wide range of masses, following an
+isolation critera, constraining by orbital measurements such as
+radial, tangential velocity and separation of the pair, and local
+environment constrains such as local velocity dispersion and local
+overdensity within a sphere of radius $5$ \mpc. A full description of
+the selection criteria can be found in \citet{lganalogues,sat}.
 
 We define two samples according to the tolerance in the selection constraints:
-A sample named $2\sigma$, correspondig to LG analogues constrained by two times the observational errors in the orbital values (radial velocity, tangential velocity, and separation), and a more relaxed sample named $3\sigma$ for LG analogues constrained by three times observational errors accordingly.
-The number of pairs in each sample is $46$ and $120$ respectively, notice we have less pairs than in \citet{lganalogues} results, since we removed pairs which are too close at $z=0$, i.e.
-their virial radii overlaps, also we removed a couple pairs who merged or change their mass more than $20\%$ at present time since they were detected at $z<0.1$.
+A sample named $2\sigma$, correspondig to LG analogues constrained by
+two times the observational errors in the orbital values (radial
+velocity, tangential velocity, and separation), and a more relaxed
+sample named $3\sigma$ for LG analogues constrained by three times
+observational errors accordingly. The number of pairs in each sample
+is $46$ and $120$ respectively, notice we have less pairs than in
+\citet{lganalogues} results, since we removed pairs which are too
+close at $z=0$, i.e. their virial radii overlaps, also we removed a
+couple pairs who merged or change their mass more than $20\%$ at
+present time since they were detected at $z<0.1$.
 
@@
 
-The first results we explore is the kind of environment occupied by
+\subsection{Pairs in Filaments and Sheets}
+
+The first result we explore is the kind of environment occupied by
 our LGs. We find that LGs in the restricted $2\sigma$ and $3\sigma$
@@
 
+\subsection{Overdensity, Ellipticity and Anisotropy}
+
 The next result is related to the matter overdensity for the LG
@@
 \begin{center}
-  \includegraphics[width=0.45\textwidth]{density_histogram.eps}
+  \includegraphics[width=0.50\textwidth]{density_histogram.pdf}
 \end{center}
@@
 
-\begin{figure}
+\begin{figure*}
 \begin{center}
-  \includegraphics[width=0.45\textwidth]{FA_histogram.eps}
+  \includegraphics[width=0.49\textwidth]{ELL_histogram.pdf}
+  \includegraphics[width=0.49\textwidth]{PROL_histogram.pdf}
 \end{center}
-\caption{Integrated Fractional Anisotropy distribution for the pairs
-  in the three samples. 
-    \label{fig:FA}}  
-\end{figure}
+\caption{Cumulative distributions for the ellipticity and prolateness.
+    \label{fig:ELL_PROL}}  
+\end{figure*}
 
@@
 
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.49\textwidth]{ELL_delta_scatter.pdf}
+  \includegraphics[width=0.49\textwidth]{PROL_delta_scatter.pdf}
+\end{center}
+\caption{Ellipticity and prolateness versus the overdensity for the pairs
+  in the general and $3\sigma$ samples.  \label{fig:delta_ELL_PROL}}  
+\end{figure*}
+
 \begin{figure}
 \begin{center}
-  \includegraphics[width=0.45\textwidth]{FA_delta_scatter.eps}
+  \includegraphics[width=0.50\textwidth]{alignments_e3.pdf} 
 \end{center}
-\caption{Density and Fractional Anisotropy distribution for the pairs
-  in the general and $3\sigma$ samples. 
-    \label{fig:delta_FA}}  
+\caption{Cumulative distributions for the alignment between the normal
+  vector $\hat{n}$ and the third eigenvector $\vec{e}_3$.
+    \label{fig:alignment}}  
 \end{figure}
@@
 
+\subsection{Alignment along the cosmic web}
+
 \section{Discussion}

### 2014-04-28 paper/main.tex
updating the whole text

@@
 \begin{abstract}
-This
+In this Letter we explore the characteristics of the Local Group (LG)
+location in the cosmic web using a cosmological simulation in the
+$\Lambda$ CDM cosmology.
+We use a description for the cosmic web that uses the Hessian of the
+gravitational potential to classify a nieghborhodd in the simulation
+as either peak, sheet, filament or voids. We find that the LG pairs
+are preferentially located in filaments and sheets. Locally their
+locations are also located in a narrow range of overdensity
+$0<\delta<4$, ellipticity $0.2<e<1.0$ and prolateness
+$-0.5<p<0.5$. Furthermore we find a strong anti-alignment between the
+LG angular momentum vector and the filament lines and the sheet 
+planes.  
 \end{abstract}
@@
 
-\citet{2013ApJ...767L...5F} also study MW-M31 pairs in numerical
+\citet{2013ApJ...767L...5F} also studied MW-M31 pairs in numerical
 simulations finding the typical quantities characterizing the orbital
@@
 structures they reside and if there is any correlation or alignment
-with the cosmic web.  
-Environment is defined by the cosmic web components identified by
-\citet{Tweb}, and we use the LG analogues computed by
-\citet{lganalogues}.
+with the cosmic web.   Environment is defined by the cosmic web
+components identified by \citet{Tweb}, and we use the LG analogues
+computed by \citet{lganalogues}.
 
-Paper is organized ...
+This Letter is organized as follows. In Section \ref{sec:simulation}
+we present the N-body cosmological simulation and the algorithm to
+define the cosmic web, next in \ref{sec:lg_analogues} we describe the
+sample of LG analogues extracted from the simulation. In
+Section \ref{sec:results} we presents our results to continue with a
+discussion about their implications for our Local Group in Section
+\ref{sec:discussion} to finally conclude in Section
+\ref{sec:conclusions}.
 
 \section{Simulation and web finding algorithm}
-\label{sec:Simulation}
+\label{sec:simulation}
 
@@
 \end{equation}
+%
 where $r_{i}$, $i=1,2,3$ refers to the three spatial comoving
@@
 This tensor is real and symmetric, which means that can be
-diagonalized. We note the eigenvalues $\lambda_1\geq \lambda_2\geq
+diagonalized. We note the eigenvalues as $\lambda_1\geq \lambda_2\geq
 \lambda_3$ and their corresponding eigenvectors $\hat{e}_1$,
 $\hat{e}_2$ and $\hat{e}_3$. The web classification compares each one
-of the three eigenvalues to a threshold value $\lambda_{\rm th}$.
-If the three, two, one or zero eigenvalues are larger than this threshold the region es classified as peak, filament, sheet or void, respectively.
+of the three eigenvalues to a threshold value $\lambda_{\rm th}$. If
+the three, two, one or zero eigenvalues are larger than this threshold
+the region es classified as peak, filament, sheet or void,
+respectively.
 
@@
 is in the range already quoted.
-
-The ellipticity and the prolatenes are quantities that measure the
-relative strength of the three eigenvalues. They are defined as
-follows
-
-\begin{equation}
-e= \frac{\lambda_3 - \lambda_1}{2(\lambda_1 + \lambda_2 + \lambda_3)}, 
-\end{equation}
-
-\begin{equation}
-p= \frac{\lambda_1 + \lambda_3 - 2\lambda_2}{2(\lambda_1 + \lambda_2 +
-  \lambda_3)}.
-\end{equation}
 
@@
 
+We use the matter overdensity, ellipticity and the prolatenes to characterize
+the relative strength of the three eigenvalues. These quantities are
+defined in terms of the eigenvalues as follows
+
+\begin{equation}
+\delta = \lambda_1 + \lambda_2 + \lambda_3,
+\end{equation}
+
+\begin{equation}
+e= \frac{\lambda_3 - \lambda_1}{2(\lambda_1 + \lambda_2 + \lambda_3)}, 
+\end{equation}
+%
+\begin{equation}
+p= \frac{\lambda_1 + \lambda_3 - 2\lambda_2}{2(\lambda_1 + \lambda_2 +
+  \lambda_3)}.
+\end{equation}
+
+We are also interested in measuring the alignment of the LG halos with
+respect to the cosmic web. To this end we characterize each LG pair by
+the vector that is normal to the orbital plane, which is defined by
+the position and velocities of each halo with respect to the center of
+mass.
+
 \section{Local Group Analogues}
+\label{sec:lg_analogues}
 
@@
 because a particular configuration of MW and M31 is transient and
-would correspond to a relatively small number of systems at one
+corresponds to a relatively small number of systems at one
 snapshot. By using multiple snapshots we can increase the sample of
@@
 couple pairs who merged or change their mass more than $20\%$ at
-present time since they were detected at $z<0.1$.
+present time since they were detected at $z<0.1$.  We also have a
+general sample which...
 
@@
 
-\subsection{Pairs in Filaments and Sheets}
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.50\textwidth]{density_histogram.pdf}
+\end{center}
+\caption{Overdensity distribution for the pairs in the three samples.
+    \label{fig:density}}  
+\end{figure}
+
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.49\textwidth]{ELL_histogram.pdf}
+  \includegraphics[width=0.49\textwidth]{PROL_histogram.pdf}
+\end{center}
+\caption{Cumulative distributions for the ellipticity and prolateness.
+    \label{fig:ELL_PROL}}  
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.49\textwidth]{ELL_delta_scatter.pdf}
+  \includegraphics[width=0.49\textwidth]{PROL_delta_scatter.pdf}
+\end{center}
+\caption{Ellipticity and prolateness versus the overdensity for the pairs
+in the general and $3\sigma$ samples. \label{fig:delta_ELL_PROL}} 
+\end{figure*}
+
+\subsection{The prefered environment for LGs}
 
 The first result we explore is the kind of environment occupied by
-our LGs. We find that LGs in the restricted $2\sigma$ and $3\sigma$
-samples prefer by large to be in filaments and sheets. Almost $\sim 50\%$ of the
-pairs in both cases can be found in filaments while $\sim 40\%$ can be
-found in sheets. This proportion is in stark contrast to the
-environments for the general pair sample. In that case only $\sim
-27\%$ and $\sim 33\%$ can be found in filaments and sheets,
-repectively. There is a considerable fraction of pairs that are
-located in peaks ($\sim 25\%$) and voids ($\sim 15\%$). These results
-and the exact numbers are presented in Table \ref{table:web_type}.
+our LGs. We find that the LGs in the general sample are located across
+all different evironment without any strong preferences; $1/3$  are
+located in sheets, $1/4$ in peaks, $1/4$ in filaments and the remaning
+$1/6$ in voids.
+
+The situation in the restricted $2\sigma$ and $3\sigma$ samples is very
+different. By large the LGs in these samples are located in
+filaments and sheets. In both samples, $\sim 50\%$ of the
+pairs can be found in filaments while $\sim 40\%$ are in
+in sheets.
+
+These absolute numbers in each environment for each sample are
+presented in Table \ref{table:web_type}.
 
@@
 
-The next result is related to the matter overdensity for the LG
-samples. Figure \ref{fig:density} shows that the range of
-overdensities for the general pair sample spans almost two orders of
-magnitude from underdense regions $\delta<0$ to high density regions
-$\delta\sim 30$, with a distribution peaking around $\delta \sim
-0$. In contrast the $2\sigma$ and $3\sigma$ samples are located within
-a narrower range of overdensities $0.0<\delta<4.0$ peaking at $\delta
-\sim 1.5$. These values are consistent with the fact that these
-samples are mostly found in filaments and sheets.
+We now describe the preferred place of the LG samples in terms of the
+overdensity, ellipticiy and anisotropy as defined in Section
+\ref{sec:simulation}.
 
-\begin{figure}
-\begin{center}
-  \includegraphics[width=0.50\textwidth]{density_histogram.pdf}
-\end{center}
-\caption{Overdensity distribution for the pairs in the three samples.
-    \label{fig:density}}  
-\end{figure}
+Figure \ref{fig:density} shows that the range of overdensities for the
+general pair sample spans almost two orders of magnitude from
+underdense regions $\delta<0$ to high density regions $\delta\sim 30$,
+with a distribution peaking around $\delta \sim 0$. In contrast the
+$2\sigma$ and $3\sigma$ samples are located within a narrower range of
+overdensities $0.0<\delta<4.0$ peaking at $\delta \sim 1.5$. This is
+consistent with the fact that these samples are mostly found in
+filaments and sheets.
 
-In Figure \ref{fig:FA} we show the integrated distribution for the
-Fractional Anisotropy in the tree samples. The General Sample clusters
-towards values of ${\mathrm FA}\sim 1.0$, while the $2\sigma$ and
-$3\sigma$ prefer values around $0.6$.
+Figure \ref{fig:ELL_PROL} presents the cumulative distribution for
+the ellipticity and prolateness. The general sample presents a wide
+range in ellipticity that can range from $-30<e<30$. For the $2\sigma$
+and $3\sigma$ samples most of the pairs are now located in a narrow
+range for ellipticities in the range $0.1<e<1.0$. This condition on
+the ellipticity together with the fact that $\delta>0$ implies that
+the prolateness in these samples must be bounded by
+$-1.0<p<1.0$. We actually find that they most of the pairs are bounded
+to an even narrower range $0.5<p<0.5$.
 
-\begin{figure*}
-\begin{center}
-  \includegraphics[width=0.49\textwidth]{ELL_histogram.pdf}
-  \includegraphics[width=0.49\textwidth]{PROL_histogram.pdf}
-\end{center}
-\caption{Cumulative distributions for the ellipticity and prolateness.
-    \label{fig:ELL_PROL}}  
-\end{figure*}
-
-In Figure \ref{fig:delta_FA} we present a joint scatter plot for the
-overdensity and fractional anisotropy. For clarity we only include the
-general and $3\sigma$ samples. In this plane we observe from the general
-sample that there are broad correlations between the overdensity and
-the fractional anisotropy.
-
-\begin{figure*}
-\begin{center}
-  \includegraphics[width=0.49\textwidth]{ELL_delta_scatter.pdf}
-  \includegraphics[width=0.49\textwidth]{PROL_delta_scatter.pdf}
-\end{center}
-\caption{Ellipticity and prolateness versus the overdensity for the pairs
-  in the general and $3\sigma$ samples.  \label{fig:delta_ELL_PROL}}  
-\end{figure*}
+Figure \ref{fig:delta_FA} shows two panels with the joint scatter plot
+for the ellipticity and the prolateness as a function of the
+overdensity. For clarity we only include the general and $3\sigma$
+samples. In the left panel (ellipticity) we see the a simple cut in
+the overdensity is not enough to explain the narrow ranges in the
+ellipticity; the LG pairs in the $3\sigma$ sample are located towards
+low ellipticity values. In the right panel (prolateness) we find a
+similar situation; a cut in the overdensity would produced a wider
+distribution in prolateness values than the one featured by the
+$3\sigma$ sample.
 
@@
 
-\begin{table}
-\begin{center}
-\begin{tabular}{lccc}\hline\hline
-Sample & $\langle\hat{e}_1\cdot \hat{n}\rangle$ & $\langle\hat{e}_2\cdot \hat{n}\rangle$ & $\langle\hat{e}_3\cdot \hat{n}\rangle$\\\hline
-2$\sigma$ & 0.56 & 0.53 &  0.33\\
-3$\sigma$ & 0.51 & 0.51 &  0.46\\
-General & 0.54 & 0.52 & 0.40\\\hline
-\end{tabular}
-\caption{Average values for the cosinus between the three eigenvectors and the vector normal to the orbital plane.
-\label{table:mu}}
-\end{center}
-\end{table}
+%\begin{table}
+%\begin{center}
+%\begin{tabular}{lccc}\hline\hline
+%Sample & $\langle\hat{e}_1\cdot \hat{n}\rangle$ & $\langle\hat{e}_2\cdot \hat{n%}\rangle$ & $\langle\hat{e}_3\cdot \hat{n}\rangle$\\\hline
+%2$\sigma$ & 0.56 & 0.53 &  0.33\\
+%3$\sigma$ & 0.51 & 0.51 &  0.46\\
+%General & 0.54 & 0.52 & 0.40\\\hline
+%\end{tabular}
+%\caption{Average values for the cosinus between the three eigenvectors and the %vector normal to the orbital plane.
+%\label{table:mu}}
+%\end{center}
+%\end{table}
 

### 2014-05-23 paper/main.tex
corrected p value abstract
new plots
writing again

@@
 
+\shorttitle{The Local Group in the Cosmic Web}
+\shortauthors{Forero-Romero \& Gonz\'alez}
+
 \begin{document}
@@
 \title{The Place of the Local Group in the Cosmic Web}
-\author{
-  XXXX\altaffilmark{1},
-  YYYY\altaffilmark{2},
-  ZZZZ\altaffilmark{3}
+\author{J. E. Forero-Romero$^1$, and R. Gonz\'alez$^2$}
+\affil{$^1$ Departamento de F\'{i}sica, Universidad de los Andes,
+  Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
+  $^2$ Instituto de Astrofísica, Pontificia Universidad Cat\'olica,
+  Av. Vicu\~na Mackenna 4860, Santiago, Chile\\  
 }
+\email{je.forero@uniandes.edu.co}
 
-\altaffiltext{1}{Uni A}
-\altaffiltext{2}{Uni B}
-\altaffiltext{3}{Uni C}
 \begin{abstract}
@@
 locations are also located in a narrow range of overdensity
-$0<\delta<4$, ellipticity $0.2<e<1.0$ and prolateness
+$0<\delta<4$, ellipticity $0.1<e<1.0$ and prolateness
 $-0.5<p<0.5$. Furthermore we find a strong anti-alignment between the
@@
 %lg rare
-The configuration of galaxies in the Local Group (LG hereafter) is quite rare to find in the local Universe and in cosmological simulations. 
-The LG is dominated by the two big spirals MW and M31, the next most-luminous galaxy is M33 which is $\sim 10$ times less massive than M31, followed by several less luminous dwarf galaxies, up to a distance of $\sim 3$\mpc.
-The velocity vector of M31, with a low tangential velocity is
-consistent to a head-on collision orbit toward the MW
+The configuration of galaxies in the Local Group (LG hereafter) is
+quite rare to find in the local Universe and in cosmological
+simulations. The LG is dominated by the two big spirals MW and M31, the next
+most-luminous galaxy is M33 which is $\sim 10$ times less massive than
+M31, followed by several less luminous dwarf galaxies, up to a
+distance of $\sim 3$\mpc.   The velocity vector of M31, with a low
+tangential velocity is consistent to a head-on collision orbit toward
+the MW
 \citep{2008MNRAS.386..461C,2012ApJ...753....8V,2012ApJ...753....7S}.
@@
 %larger scales & lg env
-To understand better the properties of the LG and how this uncommon
+To better understand the properties of the LG and how this uncommon
 pair configuration fit in the cosmological context, an immediate
@@
 group. At this scale, there is no evident alignment of the MW-M31
-orbital plane with the local filament or the Virgo-Fornax direction.
-
-However, if we look in a smaller volume below scales of $\sim 6$ \mpc,
-there is a clear alignment of th the MW-M31 orbit with a local plane
-as shown by figure $3$ in \citet{2013AJ....146...69C}.
+orbital plane with the local filament or the Virgo-Fornax
+direction. However, if we look in a smaller volume below scales of
+$\sim 6$ \mpc, there is a clear alignment of th the MW-M31 orbit with
+a local plane as shown by figure $3$ in \citet{2013AJ....146...69C}.
 
 %this paper.
-In this paper we will study the large scale environment of LG
-analogues using the Bolshoi simulation, in particular which kind of
-structures they reside and if there is any correlation or alignment
-with the cosmic web.   Environment is defined by the cosmic web
-components identified by \citet{Tweb}, and we use the LG analogues
-computed by \citet{lganalogues}.
+In this Letter we study the large scale environment of LG 
+analogues in the context of $\Lambda$CDM. We use the Bolshoi
+simulation to explore in what structures they reside and if there is
+any correlation or alignment with the cosmic web. The large scale
+Environment is defined by the cosmic web components identified by
+\citet{Tweb}, and we use the LG analogues computed by
+\citet{lganalogues}.
 
@@
 coordiates and $\phi$ is the gravitational potential renormalized to
-follow the following Poisson equation $\nabla\phi=\delta$ where
+follow the following Poisson equation $\nabla^2\phi=\delta$ where
 $\delta$ is the matter overdensity.
@@
 This tensor is real and symmetric, which means that can be
-diagonalized. We note the eigenvalues as $\lambda_1\geq \lambda_2\geq
+diagonalized. We note its eigenvalues as $\lambda_1\geq \lambda_2\geq
 \lambda_3$ and their corresponding eigenvectors $\hat{e}_1$,
@@
 the three, two, one or zero eigenvalues are larger than this threshold
-the region es classified as peak, filament, sheet or void,
+the region is classified as peak, filament, sheet or void,
 respectively.
 
-In \cite{Tweb} we perform a detailed study for the topology of the
+\cite{Tweb} performed a detailed study for the topology of the
 cosmic web and its visual counterpart as a function of the parameter
-$\lambda_{\rm th}$. We find that reasonable results in terms of the
+$\lambda_{\rm th}$. They found that reasonable results in terms of the
 volume fraction occupied by voids, the visual inspection and the halo
 populations in each web type can be reached by values of $0.2<\lambda_{\rm
-th}<0.4$. In this paper we choose the value of $\lambda_{\rm
-  th}=0.3$. We have veryfied that the main trends reported in this
-paper are unsensitive to the choice of that parameter, as long as it
-is in the range already quoted.
+th}<0.4$. In this Letter we choose the value of $\lambda_{\rm
+  th}=0.3$ to proceed with our analysis. We have veryfied that the
+main trends reported in this paper are unsensitive to the choice of
+that parameter, as long as it is in the range already quoted.
 
 The algorithm to compute the potential is grid based. First we
-interpolate the density into a cubic grid and smooth it with a
-gaussian kernel. Then we obtain the gravitational potential and use
-finite differences to compute the Hessian at every point in the
-grid. Physically speaking, the cosmic web features are scale
-dependent and the grid size has to be chosen with respect to the
-physical scales of the problem at hand.
+interpolate the density into a cubic grid with a Cloud-In-Cell (CIC)
+scheme and smooth it with a gaussian kernel. Then we obtain the
+gravitational potential using FFT methods and use finite differences
+to compute the Hessian at every point in the grid. In our case we have
+used a grid size on and a gaussian smoothing with two times larger as
+the typical separation between the two halos in the Local Group. The
+purpose of this choice is to have both halos in the pair a common
+environment. In this paper we use a grid spacing of $s=1.024$ \hMpc,
+corresponding to a $256^3$ grid in the Bolshoi volume. The scale for
+the gaussian smoothing uses the same value.
 
-In our case we have used a grid size on and a gaussian smoothing with
-two times larger as the typical separation between the two
-halos in the Local Group. The objective is to have both halos in the
-pair a common environment. In this paper we use a grid spacing of
-$s=1.024$ \hMpc, corresponding to a $256^3$ grid in the Bolshoi
-volume. The scale for the gaussian smoothing uses the same value.
-
-We use the matter overdensity, ellipticity and the prolatenes to characterize
-the relative strength of the three eigenvalues. These quantities are
-defined in terms of the eigenvalues as follows
-
+After computing the eigenvalues and eigenvectors on each point of the
+grid we use the matter overdensity, ellipticity and the prolatenes to
+further characterize the web. These quantities are defined in terms of the
+eigenvalues as follows 
+%
 \begin{equation}
@@
 \end{equation}
-
+%
 \begin{equation}
@@
 
-\begin{figure}
+\begin{figure*}
 \begin{center}
-  \includegraphics[width=0.50\textwidth]{density_histogram.pdf}
+  \includegraphics[width=0.48\textwidth]{alignments_e3_filament.pdf} 
+  \includegraphics[width=0.48\textwidth]{alignments_e3_sheet.pdf} 
 \end{center}
-\caption{Overdensity distribution for the pairs in the three samples.
-    \label{fig:density}}  
-\end{figure}
+\caption{Cumulative distributions for the alignment between the normal
+  vector $\hat{n}$ and the third eigenvector $\vec{e}_3$.
+    \label{fig:alignment}}  
+\end{figure*}
 
@@
 \begin{center}
-  \includegraphics[width=0.49\textwidth]{ELL_histogram.pdf}
-  \includegraphics[width=0.49\textwidth]{PROL_histogram.pdf}
+  \includegraphics[width=0.49\textwidth]{ELL_histogram_filament.pdf}
+  \includegraphics[width=0.49\textwidth]{PROL_histogram_filament.pdf}
+  \includegraphics[width=0.49\textwidth]{ELL_histogram_sheet.pdf}
+  \includegraphics[width=0.49\textwidth]{PROL_histogram_sheet.pdf}
 \end{center}
@@
 \end{figure*}
+
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.50\textwidth]{density_histogram.pdf}
+\end{center}
+\caption{Overdensity distribution for the pairs in the three samples.
+    \label{fig:density}}  
+\end{figure}
 
@@
        & $n$ (\%) & $n$ (\%) & $n$ (\%) & $n$ (\%) \\\hline
-2$\sigma$ & 4 (8.5) & 24 (51.0) &  18 (38.2) & 1 (2.1)\\
-3$\sigma$ & 10 (8.1) & 59 (48.3) & 48 (39.3) & 5 (4.0)\\  
-General & 1307 (23.8) & 1470 (26.8) & 1769 (32.3) & 927 (16.9)\\\hline
+2$\sigma$ & 4 (8.7) & 24 (52.2) &  17 (36.7) & 1 (2.2)\\
+3$\sigma$ & 10 (8.3) & 58 (48.3) & 47 (39.2) & 5 (4.2)\\  
+General & 1312 (23.9) & 1472 (26.9) & 1769 (32.3) & 927 (16.9)\\\hline
 \end{tabular}
@@
 \end{table}
+
+\subsection{Alignment along the cosmic web}
 
@@
 
-\begin{figure}
-\begin{center}
-  \includegraphics[width=0.50\textwidth]{alignments_e3.pdf} 
-\end{center}
-\caption{Cumulative distributions for the alignment between the normal
-  vector $\hat{n}$ and the third eigenvector $\vec{e}_3$.
-    \label{fig:alignment}}  
-\end{figure}
-
-%\begin{table}
-%\begin{center}
-%\begin{tabular}{lccc}\hline\hline
-%Sample & $\langle\hat{e}_1\cdot \hat{n}\rangle$ & $\langle\hat{e}_2\cdot \hat{n%}\rangle$ & $\langle\hat{e}_3\cdot \hat{n}\rangle$\\\hline
-%2$\sigma$ & 0.56 & 0.53 &  0.33\\
-%3$\sigma$ & 0.51 & 0.51 &  0.46\\
-%General & 0.54 & 0.52 & 0.40\\\hline
-%\end{tabular}
-%\caption{Average values for the cosinus between the three eigenvectors and the %vector normal to the orbital plane.
-%\label{table:mu}}
-%\end{center}
-%\end{table}
-
-\subsection{Alignment along the cosmic web}
-
 \section{Discussion}

### 2014-05-23 paper/main.tex
new text, new plots, clear trends

@@
 \title{The Place of the Local Group in the Cosmic Web}
-\author{J. E. Forero-Romero$^1$, and R. Gonz\'alez$^2$}
+\author{J. E. Forero-Romero$^1$ and R. Gonz\'alez$^2$}
 \affil{$^1$ Departamento de F\'{i}sica, Universidad de los Andes,
@@
 purpose of this choice is to have both halos in the pair a common
-environment. In this paper we use a grid spacing of $s=1.024$ \hMpc,
+environment. In this paper we use a grid spacing of $s=0.97$ \hMpc,
 corresponding to a $256^3$ grid in the Bolshoi volume. The scale for
@@
 close at $z=0$, i.e. their virial radii overlaps, also we removed a
-couple pairs who merged or change their mass more than $20\%$ at
-present time since they were detected at $z<0.1$.  We also have a
-general sample which...
+couple pairs that merged or change their mass more than $20\%$ at
+present time since they were detected at $z<0.1$.
+
+We also have a third general sample that we use as a control for our
+results. {\bf What are the criteria for this sample?}
 
@@
 \begin{center}
+  \includegraphics[width=0.48\textwidth]{alignments_e1_filament.pdf} 
+  \includegraphics[width=0.48\textwidth]{alignments_e1_sheet.pdf} 
+  \includegraphics[width=0.48\textwidth]{alignments_e2_filament.pdf} 
+  \includegraphics[width=0.48\textwidth]{alignments_e2_sheet.pdf} 
   \includegraphics[width=0.48\textwidth]{alignments_e3_filament.pdf} 
@@
 \end{center}
-\caption{Cumulative distributions for the alignment between the normal
-  vector $\hat{n}$ and the third eigenvector $\vec{e}_3$.
+\caption{Cumulative distributions for the alignment between the unit
+  vector linking the two halos, $\hat{r}$, and the eigenvectors
+  defining the cosmic web.
     \label{fig:alignment}}  
@@
 pairs can be found in filaments while $\sim 40\%$ are in
-in sheets.
-
-These absolute numbers in each environment for each sample are
-presented in Table \ref{table:web_type}.
+in sheets. These absolute numbers in each environment for each sample
+are presented in Table \ref{table:web_type}.
 
@@
 \subsection{Alignment along the cosmic web}
+
+We now explore the alignment of the pairs with respect to the cosmic
+web. First we define the unit vector $\hat{r}$ that links the two
+halos. Then, we compute the dot product of $\hat{r}$ and each one of
+the three eigenvectors for pair in the three samples. In Figure
+\ref{fig:alignment} we show the main result of that study, it
+presents the cumulative distribution of
+$\mu\equiv\hat{e}_3\cdot\hat{r}$ for pairs located in filaments and
+sheets. The straight line corresponds to the expected result for a
+random vector distribution.
+
+From this Figure we first see that there is a clear distinct behavior
+between the general samples and the 3$\sigma$-2$\sigma$ samples. The
+general sample tenst to be aligned along the $\hat{e}_3$ vector, the
+3$\sigma$ sample does not show any strong alignment and the 2$\sigma$
+pairs tend to be perpendicular to the $\hat{e}_3$ vector and slightly
+parallel to $\hat{e}_1$. These trends hold in filaments and walls.
+
+Let's focus on filaments first. That result means that in the general
+sample the two halos tend to lie along the filament, while in the
+2$\sigma$-3$\sigma$ samples they are located perpendicular to the
+filament. If one considers that in these samples the motion is radial,
+that means that the pairs are moving into the filament.
+
+In the case of sheets, the pairs in the general sample tend to lie on
+the sheet plane along the direction of the slowest collapsing
+direction. In the 2$\sigma$ samples the pairs are not constrained to
+the plane anymore and are perpendiculat to the $\hat{e}_3$
+vector. Considering the preferential radial motion of these pairs,
+that mens that the pairs are moving into the pancake all over a plane that
+is itself perpendicular to the sheet.
 

### 2014-07-11 paper/main.tex
new figures in text
starting new paragraph in the introduction

@@
 
+%Tweb definition
+The environment definition we use in this Letter uses the tidal tensor
+field.
+
 %this paper.
@@
 \citet{Tweb}, and we use the LG analogues computed by
-\citet{lganalogues}.
+\citet{lganalogues}. We pay spetial attention to quantify the kind of
+environment that hosts LG pairs and their alignments with respect to
+the prefered directions defined by the T-web.
 
@@
 
-\begin{figure*}
+\begin{figure}
 \begin{center}
-  \includegraphics[width=0.48\textwidth]{alignments_e1_filament.pdf} 
-  \includegraphics[width=0.48\textwidth]{alignments_e1_sheet.pdf} 
-  \includegraphics[width=0.48\textwidth]{alignments_e2_filament.pdf} 
-  \includegraphics[width=0.48\textwidth]{alignments_e2_sheet.pdf} 
-  \includegraphics[width=0.48\textwidth]{alignments_e3_filament.pdf} 
-  \includegraphics[width=0.48\textwidth]{alignments_e3_sheet.pdf} 
+  \includegraphics[width=0.48\textwidth]{alignments_e1_nall_environments.pdf} 
+  \includegraphics[width=0.48\textwidth]{alignments_e2_nall_environments.pdf} 
+  \includegraphics[width=0.48\textwidth]{alignments_e3_nall_environments.pdf} 
+\end{center}
+\caption{Cumulative distributions for the alignment between the normal vector
+$\hat{n}$, and the eigenvectors defining the cosmic web.
+    \label{fig:alignment}}  
+\end{figure}
+
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.48\textwidth]{alignments_e1_rall_environments.pdf} 
+  \includegraphics[width=0.48\textwidth]{alignments_e2_rall_environments.pdf} 
+  \includegraphics[width=0.48\textwidth]{alignments_e3_rall_environments.pdf} 
 \end{center}
@@
   defining the cosmic web.
-    \label{fig:alignment}}  
-\end{figure*}
+    \label{fig:alignment_r}}  
+\end{figure}
+
+%% \begin{figure}
+%% \begin{center}
+%%   \includegraphics[width=0.48\textwidth]{scheme.pdf} 
+%% \caption{Schematic picture of the strongest alignment tendencies in
+%%   the the General and $2\sigma$-$3\sigma$ samples. The alignment
+%%   between the peculiar velocities and the $\hat{e}_3$ eigenvector was
+%%   reported in \citet{ForeroRomero2014} for all halos regardles of its
+%%   mass. The flip in the alignment in the vector connecting the two
+%%   dominant halos in pairs is a summary of the results in Figure
+%%   \ref{fig:alignment}. 
+%% \label{fig:scheme}}
+%% \end{center}
+%% \end{figure}
 
@@
 
-\begin{table}
+\begin{table*}
 \begin{center}
@@
 \end{center}
-\end{table}
+\end{table*}
 

### 2014-07-25 paper/main.tex
updated paper body

@@
 
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.48\textwidth]{median_mass_fraction.pdf} 
+\caption{Mass dependency of the fraction of pairs in the different
+  environemnts.
+\label{fig:median_fraction}}
+\end{center}
+\end{figure}
+
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.31\textwidth]{median_mass_overdensity.pdf} 
+  \includegraphics[width=0.32\textwidth]{median_mass_ellipticity.pdf} 
+  \includegraphics[width=0.32\textwidth]{median_mass_prolateness.pdf} 
+\caption{Mass dependency of the average dark matter overdensity (left),
+  web ellipticity (middle) and web absolute value prolateness (right) at the
+  pair location.
+\label{fig:median_overdensity}}
+\end{center}
+\end{figure*}
+
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.48\textwidth]{median_mass_alignment.pdf} 
+\caption{Mass dependency of the median value for the dot product
+  between the normal vector $\hat{n}$ and each one of the
+  eigenvectors.  The lines show the trends for the general sample.
+\label{fig:median_alignment_n}}
+\end{center}
+\end{figure}
+
 %% \begin{figure}
@@
 
-\begin{figure*}
-\begin{center}
-  \includegraphics[width=0.49\textwidth]{ELL_histogram_filament.pdf}
-  \includegraphics[width=0.49\textwidth]{PROL_histogram_filament.pdf}
-  \includegraphics[width=0.49\textwidth]{ELL_histogram_sheet.pdf}
-  \includegraphics[width=0.49\textwidth]{PROL_histogram_sheet.pdf}
-\end{center}
-\caption{Cumulative distributions for the ellipticity and prolateness.
-    \label{fig:ELL_PROL}}  
-\end{figure*}
+%\begin{figure*}
+%\begin{center}
+%  \includegraphics[width=0.49\textwidth]{ELL_histogram_filament.pdf}
+%  \includegraphics[width=0.49\textwidth]{PROL_histogram_filament.pdf}
+%  \includegraphics[width=0.49\textwidth]{ELL_histogram_sheet.pdf}
+%  \includegraphics[width=0.49\textwidth]{PROL_histogram_sheet.pdf}
+%\end{center}
+%\caption{Cumulative distributions for the ellipticity and prolateness.
+%    \label{fig:ELL_PROL}}  
+%\end{figure*}
 
-\begin{figure*}
-\begin{center}
-  \includegraphics[width=0.49\textwidth]{ELL_delta_scatter.pdf}
-  \includegraphics[width=0.49\textwidth]{PROL_delta_scatter.pdf}
-\end{center}
-\caption{Ellipticity and prolateness versus the overdensity for the pairs
-in the general and $3\sigma$ samples. \label{fig:delta_ELL_PROL}} 
-\end{figure*}
+%\begin{figure*}
+%\begin{center}
+%  \includegraphics[width=0.49\textwidth]{ELL_delta_scatter.pdf}
+%  \includegraphics[width=0.49\textwidth]{PROL_delta_scatter.pdf}
+%\end{center}
+%\caption{Ellipticity and prolateness versus the overdensity for the pairs
+%in the general and $3\sigma$ samples. \label{fig:delta_ELL_PROL}} 
+%\end{figure*}
 
-\begin{figure}
-\begin{center}
-  \includegraphics[width=0.50\textwidth]{density_histogram.pdf}
-\end{center}
-\caption{Overdensity distribution for the pairs in the three samples.
-    \label{fig:density}}  
-\end{figure}
+%\begin{figure}
+%\begin{center}
+%  \includegraphics[width=0.50\textwidth]{density_histogram.pdf}
+%\end{center}
+%\caption{Overdensity distribution for the pairs in the three samples.
+%    \label{fig:density}}  
+%\end{figure}
 

### 2014-07-28 paper/main.tex
paper updated with the latest plots

@@
 \begin{center}
-  \includegraphics[width=0.48\textwidth]{alignments_e1_nall_environments.pdf} 
-  \includegraphics[width=0.48\textwidth]{alignments_e2_nall_environments.pdf} 
-  \includegraphics[width=0.48\textwidth]{alignments_e3_nall_environments.pdf} 
+  \includegraphics[width=0.48\textwidth]{alignments_e1_n_all_environments.pdf} 
+  \includegraphics[width=0.48\textwidth]{alignments_e2_n_all_environments.pdf} 
+  \includegraphics[width=0.48\textwidth]{alignments_e3_n_all_environments.pdf} 
 \end{center}
@@
 \begin{center}
-  \includegraphics[width=0.48\textwidth]{alignments_e1_rall_environments.pdf} 
-  \includegraphics[width=0.48\textwidth]{alignments_e2_rall_environments.pdf} 
-  \includegraphics[width=0.48\textwidth]{alignments_e3_rall_environments.pdf} 
+  \includegraphics[width=0.48\textwidth]{alignments_e1_r_all_environments.pdf} 
+  \includegraphics[width=0.48\textwidth]{alignments_e2_r_all_environments.pdf} 
+  \includegraphics[width=0.48\textwidth]{alignments_e3_r_all_environments.pdf} 
 \end{center}
@@
 
-%% \begin{figure}
-%% \begin{center}
-%%   \includegraphics[width=0.48\textwidth]{scheme.pdf} 
-%% \caption{Schematic picture of the strongest alignment tendencies in
-%%   the the General and $2\sigma$-$3\sigma$ samples. The alignment
-%%   between the peculiar velocities and the $\hat{e}_3$ eigenvector was
-%%   reported in \citet{ForeroRomero2014} for all halos regardles of its
-%%   mass. The flip in the alignment in the vector connecting the two
-%%   dominant halos in pairs is a summary of the results in Figure
-%%   \ref{fig:alignment}. 
-%% \label{fig:scheme}}
-%% \end{center}
-%% \end{figure}
+\begin{figure}
+  \begin{center}
+    \includegraphics[width=0.48\textwidth]{scheme.pdf} 
+    \caption{Schematic picture of the strongest alignment tendencies in
+      the the General and $2\sigma$-$3\sigma$ samples. The alignment
+      between the peculiar velocities and the $\hat{e}_3$ eigenvector was
+      reported in \citet{ForeroRomero2014} for all halos regardles of its
+      mass. 
+      \ref{fig:alignment}. 
+      \label{fig:scheme}}
+  \end{center}
+\end{figure}
 
-%\begin{figure*}
-%\begin{center}
-%  \includegraphics[width=0.49\textwidth]{ELL_histogram_filament.pdf}
-%  \includegraphics[width=0.49\textwidth]{PROL_histogram_filament.pdf}
-%  \includegraphics[width=0.49\textwidth]{ELL_histogram_sheet.pdf}
-%  \includegraphics[width=0.49\textwidth]{PROL_histogram_sheet.pdf}
-%\end{center}
-%\caption{Cumulative distributions for the ellipticity and prolateness.
-%    \label{fig:ELL_PROL}}  
-%\end{figure*}
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.49\textwidth]{alignments_jj_all_environments.pdf}
+\end{center}
+\caption{Alignment between the two angular momentum vectors of the two
+  halos in the pair.
+    \label{fig:jj_alignment}}  
+\end{figure*}
 

### 2014-07-29 paper/main.tex
updated table with the numbers of pairs in different environments

@@
 \begin{center}
-\begin{tabular}{lcccc}\hline\hline
+\begin{tabular}{ccccc}\hline\hline
 Sample & Peak & Filament & Sheet & Void\\
@@
 3$\sigma$ & 10 (8.3) & 58 (48.3) & 47 (39.2) & 5 (4.2)\\  
-General & 1312 (23.9) & 1472 (26.9) & 1769 (32.3) & 927 (16.9)\\\hline
+General ($12.1<\log_{10} M_{\rm h}/\Msun<12.3$)& 8 (1.4) & 334 (55.5) & 259
+(43.0) & 1 (0.1)\\\hline\hline  
 \end{tabular}
 \caption{
-Number of pairs in the four different kinds of environmtns. In
+Number of pairs in the four different kinds of environments. In
 parethesis the same number as a percentage of the

### 2014-08-02 paper/main.tex

@@
   Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
-  $^2$ Instituto de Astrofísica, Pontificia Universidad Cat\'olica,
+  $^2$ Instituto de Astrof\'{i}sica, Pontificia Universidad Cat\'olica,
   Av. Vicu\~na Mackenna 4860, Santiago, Chile\\  
@@
 location in the cosmic web using a cosmological simulation in the
-$\Lambda$ CDM cosmology.
-We use a description for the cosmic web that uses the Hessian of the
-gravitational potential to classify a nieghborhodd in the simulation
-as either peak, sheet, filament or voids. We find that the LG pairs
-are preferentially located in filaments and sheets. Locally their
-locations are also located in a narrow range of overdensity
-$0<\delta<4$, ellipticity $0.1<e<1.0$ and prolateness
-$-0.5<p<0.5$. Furthermore we find a strong anti-alignment between the
-LG angular momentum vector and the filament lines and the sheet 
-planes.  
+$\Lambda$CDM cosmology.
+We use the Hessian of the gravitational potential to define the cosmic web, 
+where regions are classified as either peak, sheet, filament or void.
+%We use a description for the cosmic web that uses the Hessian of the
+%gravitational potential to classify a neighborhod in the simulation
+%as either peak, sheet, filament or void. 
+Results indicate: 
+i) The LG pairs are preferentially located in filaments and sheets,
+ii) There is a strong signature that LG pairs orientation depends on the cosmic web, 
+in particular for pairs in filaments/sheets the orbital angular momentum tends to be perpendicular to the filament direction or the sheet plane.
+iii) They are located in in a narrow range of local overdensity $0<\delta<4$, 
+ellipticity $0.1<e<1.0$ and prolateness $-0.5<p<0.5$. 
+%Furthermore we find a strong anti-alignment between the
+%LG angular momentum vector and the filament lines and the sheet planes.  
 \end{abstract}
@@
 within $2\sigma$ error fron current observational measurements of the
-velocity components and distance to M31, there are only $88$ systems
+velocity components and distance to M31, there are only $46$ systems
 in a cube of $250$ \hmpc side.
@@
 To construct a sample of the MW-M31 pairs at $z\approx 0$, we use a
-series of simulation snapshots  at $z<0.1$ (i.e. in the last $\approx
-1.3$ Gyr before present) spaced by $\approx 150-250$ Myr. This is done
+series of simulation snapshots  at $z<0.1$ (since the last $\approx
+1.3$ Gyr) spaced by $\approx 150-250$ Myr. This is done
 because a particular configuration of MW and M31 is transient and
@@
 
-Pairs are selected allowing a wide range of masses, following an
-isolation critera, constraining by orbital measurements such as
-radial, tangential velocity and separation of the pair, and local
-environment constrains such as local velocity dispersion and local
-overdensity within a sphere of radius $5$ \mpc. A full description of
-the selection criteria can be found in \citet{lganalogues,sat}.
+The LG analogues or General sample in this paper are pairs selected in relative isolation,
+and in a wide range of masses from  $M_{200c}=5 \times 10^{10}$ \msun $ $ to $ 5 \times 10^{13}$ \msun. 
+Isolation criteria includes a pair closer than $1.3$\mpc, and with no massive neighbors within $5$\mpc.
+In addition we require that pairs have no Virgo-like neighbor halo with mass $M_{200c}>1.5 \times 10^{14}\ \rm M_{\odot}$ within $12$ Mpc. 
+We have $5480$ pairs under these general criteria.
+A full description of the selection criteria can be found in \citet{lganalogues,sat}.
 
-We define two samples according to the tolerance in the selection constraints:
+We also define two subsamples more closely related to the MW-M31 
+dynamics  according to the tolerance in additional constraints:
 A sample named $2\sigma$, correspondig to LG analogues constrained by
@@
 
-We also have a third general sample that we use as a control for our
-results. {\bf What are the criteria for this sample?}
+%We also have a third general sample that we use as a control for our
+%results.
 
@@
 \label{sec:results}
+
+\begin{table*}
+\begin{center}
+\begin{tabular}{ccccc}\hline\hline
+Sample & Peak & Filament & Sheet & Void\\
+       & $n$ (\%) & $n$ (\%) & $n$ (\%) & $n$ (\%) \\\hline
+2$\sigma$ & 4 (8.7) & 24 (52.2) &  17 (36.7) & 1 (2.2)\\
+3$\sigma$ & 10 (8.3) & 58 (48.3) & 47 (39.2) & 5 (4.2)\\  
+General ($12.1<\log_{10} M_{\rm h}/\Msun<12.3$)& 8 (1.4) & 334 (55.5) & 259
+(43.0) & 1 (0.1)\\
+General & 1312 (23.9) & 1472 (26.9) & 1769 (32.3) & 927 (16.9)\\
+
+\hline\hline
+\end{tabular}
+\caption{
+Number of pairs in the four different kinds of environments. In
+parethesis the same number as a percentage of the
+total population.
+\label{table:web_type}}
+\end{center}
+\end{table*}
+
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.48\textwidth]{histogram_mass_distro.pdf}
+\caption{Mass distribution of pairs in the different environments
+for the General sample.
+Dashed regions correspond to the mass ranges of $2\sigma$ and $3\sigma$ samples.
+\label{fig:median_fraction}}
+\end{center}
+\end{figure}
 
@@
 \end{center}
-\caption{Cumulative distributions for the alignment between the normal vector
+\caption{Cumulative distributions for the alignment between the normal vector to the pair orbit
 $\hat{n}$, and the eigenvectors defining the cosmic web.
@@
 
-\begin{figure}
-\begin{center}
-  \includegraphics[width=0.48\textwidth]{alignments_e1_r_all_environments.pdf} 
-  \includegraphics[width=0.48\textwidth]{alignments_e2_r_all_environments.pdf} 
-  \includegraphics[width=0.48\textwidth]{alignments_e3_r_all_environments.pdf} 
-\end{center}
-\caption{Cumulative distributions for the alignment between the unit
-  vector linking the two halos, $\hat{r}$, and the eigenvectors
-  defining the cosmic web.
-    \label{fig:alignment_r}}  
-\end{figure}
+%\begin{figure}
+%  \begin{center}
+%    \includegraphics[width=0.48\textwidth]{scheme.pdf}
+%    \caption{Schematic picture of the strongest alignment tendencies in
+%      the the General and $2\sigma$-$3\sigma$ samples. The alignment
+%      between the peculiar velocities and the $\hat{e}_3$ eigenvector was
+%      reported in \citet{ForeroRomero2014} for all halos regardles of its
+%      mass.
+%      \label{fig:scheme}}
+%  \end{center}
+%\end{figure}
+
+%\begin{figure}
+%\begin{center}
+%  \includegraphics[width=0.48\textwidth]{alignments_e1_r_all_environments.pdf} 
+%  \includegraphics[width=0.48\textwidth]{alignments_e2_r_all_environments.pdf} 
+%  \includegraphics[width=0.48\textwidth]{alignments_e3_r_all_environments.pdf} 
+%\end{center}
+%\caption{Cumulative distributions for the alignment between the unit
+%  vector linking the two halos, $\hat{r}$, and the eigenvectors
+%  defining the cosmic web.
+%    \label{fig:alignment_r}}  
+%\end{figure}
+
+%\begin{figure}
+%\begin{center}
+%  \includegraphics[width=0.48\textwidth]{histogram_mass_distro.pdf} 
+%\caption{Mass dependency of the fraction of pairs in the different
+%  environemnts.
+%\label{fig:median_fraction}}
+%\end{center}
+%\end{figure}
 
@@
 \begin{center}
-  \includegraphics[width=0.48\textwidth]{median_mass_fraction.pdf} 
-\caption{Mass dependency of the fraction of pairs in the different
-  environemnts.
-\label{fig:median_fraction}}
+  \includegraphics[width=0.48\textwidth]{median_mass_alignment.pdf}
+\caption{Mass dependency of the median value for the dot product
+  between the normal vector $\hat{n}$ and each one of the
+  eigenvectors.  The lines show the trends for the general sample.
+\label{fig:median_alignment_n}}
 \end{center}
@@
 \begin{center}
-  \includegraphics[width=0.48\textwidth]{median_mass_alignment.pdf} 
-\caption{Mass dependency of the median value for the dot product
-  between the normal vector $\hat{n}$ and each one of the
-  eigenvectors.  The lines show the trends for the general sample.
-\label{fig:median_alignment_n}}
-\end{center}
-\end{figure}
-
-\begin{figure}
-  \begin{center}
-    \includegraphics[width=0.48\textwidth]{scheme.pdf} 
-    \caption{Schematic picture of the strongest alignment tendencies in
-      the the General and $2\sigma$-$3\sigma$ samples. The alignment
-      between the peculiar velocities and the $\hat{e}_3$ eigenvector was
-      reported in \citet{ForeroRomero2014} for all halos regardles of its
-      mass. 
-      \ref{fig:alignment}. 
-      \label{fig:scheme}}
-  \end{center}
-\end{figure}
-
-\begin{figure*}
-\begin{center}
   \includegraphics[width=0.49\textwidth]{alignments_jj_all_environments.pdf}
@@
     \label{fig:jj_alignment}}  
-\end{figure*}
+\end{figure}
 
@@
 
-\begin{table*}
-\begin{center}
-\begin{tabular}{ccccc}\hline\hline
-Sample & Peak & Filament & Sheet & Void\\
-       & $n$ (\%) & $n$ (\%) & $n$ (\%) & $n$ (\%) \\\hline
-2$\sigma$ & 4 (8.7) & 24 (52.2) &  17 (36.7) & 1 (2.2)\\
-3$\sigma$ & 10 (8.3) & 58 (48.3) & 47 (39.2) & 5 (4.2)\\  
-General ($12.1<\log_{10} M_{\rm h}/\Msun<12.3$)& 8 (1.4) & 334 (55.5) & 259
-(43.0) & 1 (0.1)\\\hline\hline  
-\end{tabular}
-\caption{
-Number of pairs in the four different kinds of environments. In
-parethesis the same number as a percentage of the
-total population. 
-\label{table:web_type}}
-\end{center}
-\end{table*}
+This difference between the general and the restricted samples is mostly due 
+the mass ranges covered by each sample. 
+In \citet{lganalogues} the mass range covered by $2\sigma$ and $3\sigma$ 
+is very narrow and it is used to constraint the LG mass, then we show 
+also in table \ref{table:web_type} a subsample of the General sample
+having a similar mass range to $2\sigma$ and $3\sigma$, and it reproduces 
+similar environment fractions.
+
+A more clear view of this environment dependency and pair mass is shown in
+figure \ref{fig:median_fraction}, where we show the mass distribution of pairs
+in the different environments, then high mass pairs tend to be located in 
+peaks and filaments, and less massive ones in voids and sheets.
+Dashed regions represent the $68\%$ confidence intervals of the mass 
+distributions of $2\sigma$ and $3\sigma$ samples.
 
@@
 
-We now explore the alignment of the pairs with respect to the cosmic
-web. First we define the unit vector $\hat{r}$ that links the two
-halos. Then, we compute the dot product of $\hat{r}$ and each one of
-the three eigenvectors for pair in the three samples. In Figure
+We explore the alignment of the pairs with respect to the cosmic
+web. 
+We define the unit vector $\hat{n}$, normal to the pair orbital plane 
+computed from the pair positions and relative velocity.
+%First we define the unit vector $\hat{r}$ that links the two
+%halos. 
+Then, we compute the dot product of $\hat{n}$ and each one of
+the three eigenvectors for the three samples.
+
+In Figure
 \ref{fig:alignment} we show the main result of that study, it
 presents the cumulative distribution of
-$\mu\equiv\hat{e}_3\cdot\hat{r}$ for pairs located in filaments and
-sheets. The straight line corresponds to the expected result for a
+$\mu\equiv\hat{e}_i\cdot\hat{n}$ for the three eigenvectors $i=1,2,3$. 
+Lines indicate the different samples.
+The straight line corresponds to the expected result for a
 random vector distribution.
 
-From this Figure we first see that there is a clear distinct behavior
-between the general samples and the 3$\sigma$-2$\sigma$ samples. The
-general sample tenst to be aligned along the $\hat{e}_3$ vector, the
-3$\sigma$ sample does not show any strong alignment and the 2$\sigma$
-pairs tend to be perpendicular to the $\hat{e}_3$ vector and slightly
-parallel to $\hat{e}_1$. These trends hold in filaments and walls.
+From this Figure we can see two important features:
+First, there is a strong anti-alignment signature between $\hat{n}$ 
+and the third eigenvector, and this signature reverses with the first eigenvector.
+However, in the case of the second eigenvector, no significant deviations are found.
+Second, for $\hat{e}_3$ vector the anti-alignment become stronger for 
+the samples more closely related to the LG, then for 2$\sigma$ it is 
+stronger than for 3$\sigma$, and the latter is stronger than for General 
+sample.
 
-Let's focus on filaments first. That result means that in the general
-sample the two halos tend to lie along the filament, while in the
-2$\sigma$-3$\sigma$ samples they are located perpendicular to the
-filament. If one considers that in these samples the motion is radial,
-that means that the pairs are moving into the filament.
+%Figure \ref{fig:scheme} depicts a scheme of the alignment tendencies
+%for pairs in all samples, where the pair members positions and 
+%velocities tend to align with $\hat{e}_3$ vector.
+%The alignment between the peculiar velocities and the $\hat{e}_3$ 
+%eigenvector was already reported in \citet{ForeroRomero2014} for all
+% halos regardles of its mass.
 
-In the case of sheets, the pairs in the general sample tend to lie on
-the sheet plane along the direction of the slowest collapsing
-direction. In the 2$\sigma$ samples the pairs are not constrained to
-the plane anymore and are perpendiculat to the $\hat{e}_3$
-vector. Considering the preferential radial motion of these pairs,
-that mens that the pairs are moving into the pancake all over a plane that
-is itself perpendicular to the sheet.
+Quantitatively, the anti-alignment feature found with the $\hat{e}_3$ 
+vector means that for 2$\sigma$ sample, $\sim 50\%$ pairs have $\mu<0.2$,
+and $\sim 75\%$ pairs have $\mu<0.4$.
+We also test that does not change significantly on environment type, in particular 
+these trends hold very well for pairs in filaments and walls.
+
+If we consider only pairs in filaments, we have that the pair orbit tends
+to be perpendicular to the filament direction, and both pair members lie 
+along the filament, if we recall the 3$\sigma$-2$\sigma$ samples are 
+constrained with a mostly radial velocity component, then the pairs 
+are moving into the filament.
+In the case of sheets, we have the pair orbital plane  tend to lie within
+ the sheet plane.
+
+These alignment features are in agreement with the scenario that pairs 
+created in-situ or falling into a filament/wall align their orbits with 
+the large scale structure in a relaxation process where pair members
+tend to moves along the slowest collapsing directions.
+However, the most intriguing feature is the dependence of this alignment
+with how close we represent the LG, is still not clear.
+We explore if the pair masses are responsible of this, but we found 
+no dependence at all.
+
+In Figure \ref{fig:median_alignment_n} we show the relation between the median 
+of $\mu\equiv\hat{e}_i\cdot\hat{n}$ and mass for the general sample, and found 
+no significant relation.
+Lines in the figure show the median $\mu$-mass relation for the three 
+eigenvectors in the General sample.
+Dots represent the median $\mu$ for the three eigenvectors in the 
+2$\sigma$-3$\sigma$ samples.
+In the case of $\|\hat{e}_3\cdot\hat{n}\|$, the figure clearly shows for a fixed mass
+range around $1.5-2.0 \times 10^{10}$ \msun, that the median $\mu$ decreases as we
+better constraint the LG samples, being larger for General sample and smaller for 
+2$\sigma$ sample accordingly.
+
+%From this Figure we first see that there is a clear distinct behavior
+%between the general samples and the 3$\sigma$-2$\sigma$ samples. The
+%general sample tend to be aligned along the $\hat{e}_3$ vector, the
+%3$\sigma$ sample does not show any strong alignment and the 2$\sigma$
+%pairs tend to be perpendicular to the $\hat{e}_3$ vector and slightly
+%parallel to $\hat{e}_1$. These trends hold in filaments and walls.
+
+%Let's focus on filaments first. That result means that in the general
+%sample the two halos tend to lie along the filament, while in the
+%2$\sigma$-3$\sigma$ samples they are located perpendicular to the
+%filament. If one considers that in these samples the motion is radial,
+%that means that the pairs are moving into the filament.
+
+%In the case of sheets, the pairs in the general sample tend to lie on
+%the sheet plane along the direction of the slowest collapsing
+%direction. In the 2$\sigma$ samples the pairs are not constrained to
+%the plane anymore and are perpendiculat to the $\hat{e}_3$
+%vector. Considering the preferential radial motion of these pairs,
+%that mens that the pairs are moving into the pancake all over a plane that
+%is itself perpendicular to the sheet.
 
@@
 
-Figure \ref{fig:density} shows that the range of overdensities for the
-general pair sample spans almost two orders of magnitude from
-underdense regions $\delta<0$ to high density regions $\delta\sim 30$,
-with a distribution peaking around $\delta \sim 0$. In contrast the
-$2\sigma$ and $3\sigma$ samples are located within a narrower range of
-overdensities $0.0<\delta<4.0$ peaking at $\delta \sim 1.5$. This is
-consistent with the fact that these samples are mostly found in
-filaments and sheets.
+Figure \ref{fig:median_overdensity} shows dependency of overdensity,
+ellipciticy, and prolateness on pair mass for the different samples.
+General sample is represented by the solid lines with the associated 
+errors covered by the shaded region.
 
-Figure \ref{fig:ELL_PROL} presents the cumulative distribution for
-the ellipticity and prolateness. The general sample presents a wide
-range in ellipticity that can range from $-30<e<30$. For the $2\sigma$
-and $3\sigma$ samples most of the pairs are now located in a narrow
-range for ellipticities in the range $0.1<e<1.0$. This condition on
-the ellipticity together with the fact that $\delta>0$ implies that
-the prolateness in these samples must be bounded by
-$-1.0<p<1.0$. We actually find that they most of the pairs are bounded
-to an even narrower range $0.5<p<0.5$.
+Left panel shows the overdensity dependence on mass where higher mass
+pairs are located in high density regions.
+The $2\sigma$ and $3\sigma$ samples having a narrower mass range as 
+shown in previous figure, are consequently located within a narrower 
+range of overdensities $0.0<\delta<4.0$ peaking at $\delta \sim 1$. 
+This is also consistent with the fact that these samples are mostly 
+found in filaments and sheets. 
+Average overdensity of $2\sigma$ and $3\sigma$ samples show no 
+significant difference from the General sample within the same mass 
+range.
 
-Figure \ref{fig:delta_FA} shows two panels with the joint scatter plot
-for the ellipticity and the prolateness as a function of the
-overdensity. For clarity we only include the general and $3\sigma$
-samples. In the left panel (ellipticity) we see the a simple cut in
-the overdensity is not enough to explain the narrow ranges in the
-ellipticity; the LG pairs in the $3\sigma$ sample are located towards
-low ellipticity values. In the right panel (prolateness) we find a
-similar situation; a cut in the overdensity would produced a wider
-distribution in prolateness values than the one featured by the
-$3\sigma$ sample.
+%Figure \ref{fig:density} shows that the range of overdensities for the
+%general pair sample spans almost two orders of magnitude from
+%underdense regions $\delta<0$ to high density regions $\delta\sim 30$,
+%with a distribution peaking around $\delta \sim 0$. In contrast the
+%$2\sigma$ and $3\sigma$ samples are located within a narrower range of
+%overdensities $0.0<\delta<4.0$ peaking at $\delta \sim 1.5$. This is
+%consistent with the fact that these samples are mostly found in
+%filaments and sheets.
+
+Middle and right panels show web ellipciticy and absolute prolateness
+dependence on mass. Again we noticed that within the same mass range,
+the $2\sigma$ and $3\sigma$ average ellipciticy and prolateness does not
+differ significantly from General sample.
+For the $2\sigma$ and $3\sigma$ samples most of the pairs are located
+in a narrow range for ellipticities in the range $0.1<e<1.0$, and
+prolateness $0.5<p<0.5$.
+
+%the cumulative distribution for
+%the ellipticity and prolateness. The general sample presents a wide
+%range in ellipticity that can range from $-30<e<30$. For the $2\sigma$
+%and $3\sigma$ samples most of the pairs are now located in a narrow
+%range for ellipticities in the range $0.1<e<1.0$. This condition on
+%the ellipticity together with the fact that $\delta>0$ implies that
+%the prolateness in these samples must be bounded by
+%$-1.0<p<1.0$. We actually find that they most of the pairs are bounded
+%to an even narrower range $0.5<p<0.5$.
+
+%Figure \ref{fig:delta_FA} shows two panels with the joint scatter plot
+%for the ellipticity and the prolateness as a function of the
+%overdensity. For clarity we only include the general and $3\sigma$
+%samples. In the left panel (ellipticity) we see the a simple cut in
+%the overdensity is not enough to explain the narrow ranges in the
+%ellipticity; the LG pairs in the $3\sigma$ sample are located towards
+%low ellipticity values. In the right panel (prolateness) we find a
+%similar situation; a cut in the overdensity would produced a wider
+%distribution in prolateness values than the one featured by the
+%$3\sigma$ sample.
+
+\subsection{Spin and Orbital Angular Momentum}
+
+In $4.2$ we defined the unit vector $\hat{n}$, normal to the pair 
+orbital plane which can be asociated with the orbital angular 
+momentum direction $\hat{J}$.
+There, we show several alignment features of the pair orbital
+momentum with the environment.
+In this subsection we explore the alignement of the individual spin
+angular momentum of each pair member $\hat{j_A}$ and $\hat{j_B}$ with
+each other and with the orbital angular momentum.
+
+We show in figure \ref{fig:jj_alignment} the cumulative distribution of
+dot product between the spin of both members in the pair.
+We found a slight alignment of spin vectors for the $2\sigma$ sample.
+However, we found no significant alignment between spin and orbital angular 
+momentum for any sample.
+
+In the LG, the angle between MW and M31 spin is $\sim60^{\circ}$ and the
+angles between spins and orbital angular momentum are $\sim33^{\circ}$
+and $\sim76^{\circ}$ for MW and M31 respectively \citep{2012ApJ...753....9V}.
+Then the LG show no particular alignement aswell.
 
@@
 \label{sec:discussion}
+
+We explored the characteristics of the LG location in the cosmic web.
+
+LG pairs are preferentially located in filaments and sheets. The mass range
+of the pairs sample plays an important role in the fractions for each environment
+type as shown in table $1$ and figure $1$.
+
+There is a clear anti-alignment between the third eigenvector and the vector normal 
+to the pair orbital plane. This feature is not mass dependant as can be shown in
+figure $3$.
+For pairs in filaments this means the pair orbit tends to be perpendicular to the 
+filament direction, and both pair members lie along the filament, and in the case 
+of pairs in sheets, we have the pair orbital plane lie in the sheet plane.
+We also found this anti-alignment becomes stronger for the samples being more 
+closely related to the LG, it means it is stronger for $2\sigma$ sample.
+All these alignment features are consistent with pair orbits relaxing their 
+movements towards the slowest collapsing directions at larger scales.
+
+LG pairs are located in a narrow range of local overdensity, ellipciticy and prolateness.
+And this is consistent with the narrow mass range selection of specific samples.
+
+The LG spin and orbital angular momentum have no particular alignment,
+and we see no significan alignments in our LG pairs, however for the alignment
+between pair spins we found a slight alignment signature for $2\sigma$ sample as
+can be seen in figure $5$.
 
@@
 \section*{Acknowledgements}
+REG was supported by Proyecto Financiamiento Basal PFB06 and Comite Mixto ESO.
 

### 2014-08-04 paper/main.tex
some edits in the abstract + introduction + new references

@@
 We use the Hessian of the gravitational potential to define the cosmic web, 
-where regions are classified as either peak, sheet, filament or void.
-%We use a description for the cosmic web that uses the Hessian of the
-%gravitational potential to classify a neighborhod in the simulation
-%as either peak, sheet, filament or void. 
-Results indicate: 
-i) The LG pairs are preferentially located in filaments and sheets,
-ii) There is a strong signature that LG pairs orientation depends on the cosmic web, 
-in particular for pairs in filaments/sheets the orbital angular momentum tends to be perpendicular to the filament direction or the sheet plane.
-iii) They are located in in a narrow range of local overdensity $0<\delta<4$, 
-ellipticity $0.1<e<1.0$ and prolateness $-0.5<p<0.5$. 
-%Furthermore we find a strong anti-alignment between the
-%LG angular momentum vector and the filament lines and the sheet planes.  
+where regions are classified as either peak, sheet, filament or
+void. 
+The LG in the simulations are split into two samples.
+The first is a general sample composed by halo pairs with
+similar masses and isolation criteria as observed in the LG. 
+The second is a subset with additional kinematic constaints.
+We find that the pairs in the LG sample with all constraints are:
+i) Preferentially located in filaments and sheets,
+ii) located in in a narrow range of local overdensity $0<\delta<4$, 
+web ellipticity $0.1<e<1.0$ and prolateness $-0.5<p<0.5$. 
+iii) Clearly aligned with the cosmic web, in particular for pairs in
+filaments/sheets the orbital angular momentum tends to be
+perpendicular to the filament direction or the sheet plane. A stronger
+alignment is present for the vector linking the two halos, which lies
+along the filament or the sheet plane.  
+We show that the first and second results are expected trends with the
+LG total mass. 
+However, the strong alignment with the cosmic web cannot be explained
+in the same way.
+
 \end{abstract}
@@
 %lg rare
-The configuration of galaxies in the Local Group (LG hereafter) is
-quite rare to find in the local Universe and in cosmological
-simulations. The LG is dominated by the two big spirals MW and M31, the next
+The spatial and kinematic configuration of the Local Group
+(LG) galaxies is rare to find in the local Universe and in cosmological
+simulations. 
+The LG is dominated by the two big spirals MW and M31, the next
 most-luminous galaxy is M33 which is $\sim 10$ times less massive than
 M31, followed by several less luminous dwarf galaxies, up to a
-distance of $\sim 3$\mpc.   The velocity vector of M31, with a low
+distance of $\sim 3$\mpc.   
+The velocity vector of M31, with a low
 tangential velocity is consistent to a head-on collision orbit toward
@@
 average density of the universe
-\citep{2003ApJ...596...19K,2005AJ....129..178K}. In addition, the
+\citep{2003ApJ...596...19K,2005AJ....129..178K}. 
+In addition, the
 closest massive galaxy cluster, the Virgo Cluster, is $\approx
@@
 
-All this combination of features make LG analogues very rare to
-find. Using numerical simulatons \citet{lganalogues} found less than
+All this combination of features make LG analogues rare to
+find. 
+Using numerical simulatons \citet{lganalogues} found less than
 $2\%$ MW-sized halos reside in a pair similar to MW-M31 and in a
-similar environment. Furthermore, if we select pairs constrained
+similar environment. 
+Furthermore, if we select pairs constrained
 within $2\sigma$ error fron current observational measurements of the
 velocity components and distance to M31, there are only $46$ systems
-in a cube of $250$ \hmpc side.
+in a cubic volume of $250$ \hmpc side, giving a number density $\sim
+1.0\times 10^{-6}$Mpc$^{3}$, comparable to the abundance of massive
+clusters.
 
@@
 challenge the \lcdm model.
+
 Another definition of LG analogues is made by
@@
 particular, which are the typical/prefered locations of these systems
-within the Cosmic Web?.
+within the Cosmic Web?. To what extent is this an expected
+configuration in $\Lambda$CDM.
 
@@
 nearby galaxies and groups members of this large structure are the
-Maffei group, NGC $6744$, NGC $5128$, $M101$, $M81$, $NGC1023$, Cen A
+Maffei group, NGC $6744$, NGC $5128$, M$101$, M$81$, NGC$1023$, Cen A
 group. At this scale, there is no evident alignment of the MW-M31
@@
 $\sim 6$ \mpc, there is a clear alignment of th the MW-M31 orbit with
-a local plane as shown by figure $3$ in \citet{2013AJ....146...69C}.
-
-%Tweb definition
-The environment definition we use in this Letter uses the tidal tensor
-field.
+a local plane as shown by Figure $3$ in \citet{2013AJ....146...69C}.
 
@@
 with the constraints from the WMAP satellite
-\citep{hinshaw_etal13}. The simulation followed evolution of dark
+\citep{hinshaw_etal13}. The simulation followed the evolution of dark
 matter in a $250 \hmpc$ box with spatial resolution of $\approx
@@
 coordiates and $\phi$ is the gravitational potential renormalized to
-follow the following Poisson equation $\nabla^2\phi=\delta$ where
+follow the Poisson equation $\nabla^2\phi=\delta$ where
 $\delta$ is the matter overdensity.
@@
 This tensor is real and symmetric, which means that can be
-diagonalized. We note its eigenvalues as $\lambda_1\geq \lambda_2\geq
+diagonalized. 
+We note its eigenvalues as $\lambda_1\geq \lambda_2\geq
 \lambda_3$ and their corresponding eigenvectors $\hat{e}_1$,
-$\hat{e}_2$ and $\hat{e}_3$. The web classification compares each one
-of the three eigenvalues to a threshold value $\lambda_{\rm th}$. If
+$\hat{e}_2$ and $\hat{e}_3$. 
+The web classification compares each one
+of the three eigenvalues to a threshold value $\lambda_{\rm th}$. 
+If
 the three, two, one or zero eigenvalues are larger than this threshold
@@
 cosmic web and its visual counterpart as a function of the parameter
-$\lambda_{\rm th}$. They found that reasonable results in terms of the
+$\lambda_{\rm th}$. 
+They found that reasonable results in terms of the
 volume fraction occupied by voids, the visual inspection and the halo
 populations in each web type can be reached by values of $0.2<\lambda_{\rm
-th}<0.4$. In this Letter we choose the value of $\lambda_{\rm
-  th}=0.3$ to proceed with our analysis. We have veryfied that the
-main trends reported in this paper are unsensitive to the choice of
-that parameter, as long as it is in the range already quoted.
+th}<0.4$. 
+In this Letter we choose the value of $\lambda_{\rm
+  th}=0.3$ to proceed with our analysis. 
+This is only relevant to the classification of the simulation into web
+elements. Other results are completeley independent of this
+choice. Nevertheless we have checked that the main conclusions of this
+work do not depend on the choise of $\lambda_{\rm th}$.
 
@@
 interpolate the density into a cubic grid with a Cloud-In-Cell (CIC)
-scheme and smooth it with a gaussian kernel. Then we obtain the
+scheme and smooth it with a gaussian kernel. 
+Then we obtain the
 gravitational potential using FFT methods and use finite differences
-to compute the Hessian at every point in the grid. In our case we have
+to compute the Hessian at every point in the grid. 
+In our case we have
 used a grid size on and a gaussian smoothing with two times larger as
-the typical separation between the two halos in the Local Group. The
+the typical separation between the two halos in the Local Group. 
+The
 purpose of this choice is to have both halos in the pair a common
 environment. In this paper we use a grid spacing of $s=0.97$ \hMpc,
-corresponding to a $256^3$ grid in the Bolshoi volume. The scale for
+corresponding to a $256^3$ grid in the Bolshoi volume. 
+The scale for
 the gaussian smoothing uses the same value.
 
-After computing the eigenvalues and eigenvectors on each point of the
-grid we use the matter overdensity, ellipticity and the prolatenes to
-further characterize the web. These quantities are defined in terms of the
+We use the matter overdensity, ellipticity and the prolatenes to
+further characterize the web. 
+These quantities are defined in terms of the
 eigenvalues as follows 
@@
 mass.
+
+The data of the BDM halos and the Tweb is publicly available through
+a database located at \url{http://www.cosmosim.org/}. A detailed
+description of the database structure was presented by \cite{Riebe2013}.
 
@@
 
-%\begin{figure}
-%\begin{center}
-%  \includegraphics[width=0.48\textwidth]{alignments_e1_r_all_environments.pdf} 
-%  \includegraphics[width=0.48\textwidth]{alignments_e2_r_all_environments.pdf} 
-%  \includegraphics[width=0.48\textwidth]{alignments_e3_r_all_environments.pdf} 
-%\end{center}
-%\caption{Cumulative distributions for the alignment between the unit
-%  vector linking the two halos, $\hat{r}$, and the eigenvectors
-%  defining the cosmic web.
-%    \label{fig:alignment_r}}  
-%\end{figure}
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.48\textwidth]{alignments_e1_r_all_environments.pdf} 
+  \includegraphics[width=0.48\textwidth]{alignments_e2_r_all_environments.pdf} 
+  \includegraphics[width=0.48\textwidth]{alignments_e3_r_all_environments.pdf} 
+\end{center}
+\caption{Cumulative distributions for the alignment between the unit
+  vector linking the two halos, $\hat{r}$, and the eigenvectors
+  defining the cosmic web.
+    \label{fig:alignment_r}}  
+\end{figure}
 

### 2014-08-05 paper/main.tex
small modifications in the results section

@@
 
+\newcommand{\manuscript}{paper }
 \newcommand{\lcdm}{$\Lambda$CDM }
@@
 \begin{abstract}
-In this Letter we explore the characteristics of the Local Group (LG)
+We explore the characteristics of the Local Group (LG)
 location in the cosmic web using a cosmological simulation in the
-$\Lambda$CDM cosmology.
-We use the Hessian of the gravitational potential to define the cosmic web, 
-where regions are classified as either peak, sheet, filament or
-void. 
-The LG in the simulations are split into two samples.
-The first is a general sample composed by halo pairs with
-similar masses and isolation criteria as observed in the LG. 
-The second is a subset with additional kinematic constaints.
-We find that the pairs in the LG sample with all constraints are:
-i) Preferentially located in filaments and sheets,
-ii) located in in a narrow range of local overdensity $0<\delta<4$, 
-web ellipticity $0.1<e<1.0$ and prolateness $-0.5<p<0.5$. 
-iii) Clearly aligned with the cosmic web, in particular for pairs in
-filaments/sheets the orbital angular momentum tends to be
-perpendicular to the filament direction or the sheet plane. A stronger
-alignment is present for the vector linking the two halos, which lies
-along the filament or the sheet plane.  
-We show that the first and second results are expected trends with the
-LG total mass. 
-However, the strong alignment with the cosmic web cannot be explained
-in the same way.
+$\Lambda$CDM cosmology.  We use the Hessian of the gravitational
+potential to define the cosmic web, where regions are classified as
+either peak, sheet, filament or void.  The LG in the simulations are
+split into two samples.  The first is a general sample composed by
+halo pairs with similar masses and isolation criteria as observed in
+the LG.  The second is a subset with additional kinematic constaints.
+We find that the pairs in the LG sample with all constraints are: i)
+Preferentially located in filaments and sheets, ii) located in in a
+narrow range of local overdensity $0<\delta<4$, web ellipticity
+$0.1<e<1.0$ and prolateness $-0.5<p<0.5$.  iii) Clearly aligned with
+the cosmic web, in particular for pairs in filaments/sheets the
+orbital angular momentum tends to be perpendicular to the filament
+direction or the sheet plane. A stronger alignment is present for the
+vector linking the two halos, which lies along the filament or the
+sheet plane.  We show that the first and second results are expected
+trends with the LG total mass.  However, the strong alignment with the
+cosmic web cannot be explained in the same way.
 
@@
 %this paper.
-In this Letter we study the large scale environment of LG 
+In this \manuscript we study the large scale environment of LG 
 analogues in the context of $\Lambda$CDM. We use the Bolshoi
@@
 
-This Letter is organized as follows. In Section \ref{sec:simulation}
+This \manuscript is organized as follows. In Section \ref{sec:simulation}
 we present the N-body cosmological simulation and the algorithm to
@@
 th}<0.4$. 
-In this Letter we choose the value of $\lambda_{\rm
+In this \manuscript we choose the value of $\lambda_{\rm
   th}=0.3$ to proceed with our analysis. 
@@
 
-The algorithm to compute the potential is grid based. First we
-interpolate the density into a cubic grid with a Cloud-In-Cell (CIC)
-scheme and smooth it with a gaussian kernel. 
-Then we obtain the
-gravitational potential using FFT methods and use finite differences
+The algorithm to compute the potential is grid based. 
+First we interpolate the density into a cubic grid with a
+Cloud-In-Cell (CIC) scheme and smooth it with a gaussian kernel. 
+Then we obtain the gravitational potential using FFT methods and use finite differences
 to compute the Hessian at every point in the grid. 
-In our case we have
-used a grid size on and a gaussian smoothing with two times larger as
-the typical separation between the two halos in the Local Group. 
-The
-purpose of this choice is to have both halos in the pair a common
-environment. In this paper we use a grid spacing of $s=0.97$ \hMpc,
+In our case we have used a grid size on and a gaussian smoothing with
+two times larger as the typical separation between the two halos in the Local Group. 
+The purpose of this choice is to have both halos in the pair a common
+environment. 
+In this \manuscript we use a grid spacing of $s=0.97$ \hMpc,
 corresponding to a $256^3$ grid in the Bolshoi volume. 
-The scale for
-the gaussian smoothing uses the same value.
+The scale for the gaussian smoothing uses the same value.
 
@@
 
-We are also interested in measuring the alignment of the LG halos with
-respect to the cosmic web. To this end we characterize each LG pair by
-the vector that is normal to the orbital plane, which is defined by
-the position and velocities of each halo with respect to the center of
-mass.
+We also measure the alignment of the LG halos with respect to the
+cosmic web defined by the eigenvector.
+To this end we characterize each LG pair by two vectors. 
+The first is $\hat{n}$, the vector marking the axis along the orbital angular
+momentum of the pair, normal to its orbital plane; the second is
+$\hat{r}$, the vector that connects the halos in the pair. 
+We quantify the alignment using the absolute value of the cosinus of
+the angle between the two vectors of interest $\mu=|\hat{e}_i \cdot
+\hat{n}|$ or $\mu=|\hat{e}_i\cdot \hat{r}|$, where $i=1,2,3$.
 
@@
 series of simulation snapshots  at $z<0.1$ (since the last $\approx
-1.3$ Gyr) spaced by $\approx 150-250$ Myr. This is done
-because a particular configuration of MW and M31 is transient and
+1.3$ Gyr) spaced by $\approx 150-250$ Myr. 
+This is done because a particular configuration of MW and M31 is transient and
 corresponds to a relatively small number of systems at one
-snapshot. By using multiple snapshots we can increase the sample of
-systems in such configuration during a period of time in which secular
+snapshot. 
+By using multiple snapshots we can increase the sample of systems in
+such configuration during a period of time in which secular
 cosmological evolution is small.
 
-The LG analogues or General sample in this paper are pairs selected in relative isolation,
-and in a wide range of masses from  $M_{200c}=5 \times 10^{10}$ \msun $ $ to $ 5 \times 10^{13}$ \msun. 
-Isolation criteria includes a pair closer than $1.3$\mpc, and with no massive neighbors within $5$\mpc.
-In addition we require that pairs have no Virgo-like neighbor halo with mass $M_{200c}>1.5 \times 10^{14}\ \rm M_{\odot}$ within $12$ Mpc. 
+The LG analogues or General Sample (GS) in this paper are pairs selected in
+relative isolation, and in a wide range of masses from  $M_{200c}=5
+\times 10^{11}$ \msun $ $ to $ 5 \times 10^{13}$ \msun.  
+Isolation criteria includes a pair closer than $1.3$\mpc, and with no
+massive neighbors within $5$\mpc.
+In addition we require that pairs have no Virgo-like neighbor halo
+with mass $M_{200c}>1.5 \times 10^{14}\ \rm M_{\odot}$ within $12$
+Mpc.  
 We have $5480$ pairs under these general criteria. 
-A full description of the selection criteria can be found in \citet{lganalogues,sat}.
+A full description of the selection criteria can be found in
+\citet{lganalogues,sat}.
 
 We also define two subsamples more closely related to the MW-M31 
-dynamics  according to the tolerance in additional constraints:
+dynamics according to the tolerance in additional constraints.
 A sample named $2\sigma$, correspondig to LG analogues constrained by
@@
 sample named $3\sigma$ for LG analogues constrained by three times
-observational errors accordingly. The number of pairs in each sample
-is $46$ and $120$ respectively, notice we have less pairs than in
-\citet{lganalogues} results, since we removed pairs which are too
-close at $z=0$, i.e. their virial radii overlaps, also we removed a
-couple pairs that merged or change their mass more than $20\%$ at
-present time since they were detected at $z<0.1$.
-
-%We also have a third general sample that we use as a control for our
-%results.
+observational errors accordingly. 
+The number of pairs in each sample is $46$ and $120$ respectively,
+notice we have less pairs than in \citet{lganalogues} results, since
+we removed pairs which are too close at $z=0$, i.e. their virial radii
+overlaps, also we removed a couple pairs that merged or change their
+mass more than $20\%$ at present time since they were detected at
+$z<0.1$.
 
@@
 3$\sigma$ & 10 (8.3) & 58 (48.3) & 47 (39.2) & 5 (4.2)\\  
-General ($12.1<\log_{10} M_{\rm h}/\Msun<12.3$)& 8 (1.4) & 334 (55.5) & 259
+General & 1312 (23.9) & 1472 (26.9) & 1769 (32.3) & 927 (16.9)\\
+General ($12.1<\log_{10} M_{\rm LG}/\Msun<12.3$)& 8 (1.4) & 334 (55.5) & 259
 (43.0) & 1 (0.1)\\
-General & 1312 (23.9) & 1472 (26.9) & 1769 (32.3) & 927 (16.9)\\
-
 \hline\hline
@@
 \caption{
-Number of pairs in the four different kinds of environments. In
-parethesis the same number as a percentage of the
-total population.
+Number of pairs in the four different kinds of environments for each
+of the three samples presented in Section \ref{sec:lg_analogues}. 
+In parethesis the same number as a percentage of the total population.
+The last line in the table corresponds to the general sample with an
+additional mass cut for the total pair mass.  
 \label{table:web_type}}
@@
 \caption{Mass distribution of pairs in the different environments
-for the General sample.
-Dashed regions correspond to the mass ranges of $2\sigma$ and $3\sigma$ samples.
+for the general sample.
+The shaded regions show the mass ranges of $2\sigma$ and $3\sigma$
+samples.  
 \label{fig:median_fraction}}
@@
 \end{figure}
+
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.31\textwidth]{median_mass_overdensity.pdf} 
+  \includegraphics[width=0.32\textwidth]{median_mass_ellipticity.pdf} 
+  \includegraphics[width=0.32\textwidth]{median_mass_prolateness.pdf} 
+\caption{Mass dependency of the average dark matter overdensity (left),
+  web ellipticity (middle) and web absolute value prolateness (right) at the
+  pair location.
+\label{fig:median_overdensity}}
+\end{center}
+\end{figure*}
 
@@
 \end{center}
-\caption{Cumulative distributions for the alignment between the normal vector to the pair orbit
-$\hat{n}$, and the eigenvectors defining the cosmic web.
-    \label{fig:alignment}}  
+\caption{Cumulative distributions for the alignment between the normal
+  vector to the pair orbital plane, $\hat{n}$, and the three eigenvectors in
+  the Tweb.
+    \label{fig:alignment_n}}  
+\end{figure}
+
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.48\textwidth]{alignments_e1_r_all_environments.pdf} 
+  \includegraphics[width=0.48\textwidth]{alignments_e2_r_all_environments.pdf} 
+  \includegraphics[width=0.48\textwidth]{alignments_e3_r_all_environments.pdf} 
+\end{center}
+\caption{Cumulative distributions for the alignment between the vector
+  linking the two halos in the pair, $\hat{r}$, and the three
+  eigenvectors in the Tweb.
+    \label{fig:alignment_r}}  
 \end{figure}
@@
 %\end{figure}
-
-\begin{figure}
-\begin{center}
-  \includegraphics[width=0.48\textwidth]{alignments_e1_r_all_environments.pdf} 
-  \includegraphics[width=0.48\textwidth]{alignments_e2_r_all_environments.pdf} 
-  \includegraphics[width=0.48\textwidth]{alignments_e3_r_all_environments.pdf} 
-\end{center}
-\caption{Cumulative distributions for the alignment between the unit
-  vector linking the two halos, $\hat{r}$, and the eigenvectors
-  defining the cosmic web.
-    \label{fig:alignment_r}}  
-\end{figure}
 
@@
 \end{figure}
-
-\begin{figure*}
-\begin{center}
-  \includegraphics[width=0.31\textwidth]{median_mass_overdensity.pdf} 
-  \includegraphics[width=0.32\textwidth]{median_mass_ellipticity.pdf} 
-  \includegraphics[width=0.32\textwidth]{median_mass_prolateness.pdf} 
-\caption{Mass dependency of the average dark matter overdensity (left),
-  web ellipticity (middle) and web absolute value prolateness (right) at the
-  pair location.
-\label{fig:median_overdensity}}
-\end{center}
-\end{figure*}
 
@@
 The first result we explore is the kind of environment occupied by
-our LGs. We find that the LGs in the general sample are located across
+our LGs. 
+We find that the LGs in the general sample are located across
 all different evironment without any strong preferences; $1/3$  are
@@
 The situation in the restricted $2\sigma$ and $3\sigma$ samples is very
-different. By large the LGs in these samples are located in
-filaments and sheets. In both samples, $\sim 50\%$ of the
-pairs can be found in filaments while $\sim 40\%$ are in
-in sheets. These absolute numbers in each environment for each sample
-are presented in Table \ref{table:web_type}.
+different. 
+By large the LGs in these samples are located in filaments and sheets. 
+In both samples, $\sim 50\%$ of the pairs can be found in filaments
+while $\sim 40\%$ are in sheets. 
+These absolute numbers in each environment for each sample are
+presented in Table \ref{table:web_type}.
 
-This difference between the general and the restricted samples is mostly due 
-the mass ranges covered by each sample. 
+This difference between the general and the restricted samples is
+due the mass ranges covered by each sample. 
 In \citet{lganalogues} the mass range covered by $2\sigma$ and $3\sigma$ 
-is very narrow and it is used to constraint the LG mass, then we show 
-also in table \ref{table:web_type} a subsample of the General sample
-having a similar mass range to $2\sigma$ and $3\sigma$, and it reproduces 
+is very narrow and it is used to constraint the LG mass.
+We show  in table \ref{table:web_type} that subset of the GS
+having a similar mass range to $2\sigma$ and $3\sigma$ reproduces  
 similar environment fractions.
 
-A more clear view of this environment dependency and pair mass is shown in
-figure \ref{fig:median_fraction}, where we show the mass distribution of pairs
-in the different environments, then high mass pairs tend to be located in 
-peaks and filaments, and less massive ones in voids and sheets.
-Dashed regions represent the $68\%$ confidence intervals of the mass 
+Figure \ref{fig:median_fraction} clearly shows the correlation between
+environment an total pair mass.
+Each line represents the mass distribution of pairs in the four
+different environments for the general sample.
+High mass pairs tend to be located in  peaks and filaments while less
+massive ones in voids and sheets. 
+The shaded regions represent the $68\%$ confidence intervals of the mass 
 distributions of $2\sigma$ and $3\sigma$ samples.
+
+\subsection{Web Overdensity, Ellipticity and Anisotropy}
+
+We now describe the preferred place of the LG samples in terms of the
+web overdensity, ellipticiy and anisotropy as defined in Section
+\ref{sec:simulation}.
+
+Figure \ref{fig:median_overdensity} shows dependency of the web overdensity,
+ellipciticy, and prolateness on pair mass for the different samples.
+GS is represented by the solid lines with the associated 
+errors covered by the shaded region. 
+The symbols represents the results for the $2\sigma$ and $3\sigma$
+samples.  
+In all cases it is immediatly clear that the range of values for the
+$2\sigma$ and $3\sigma$ samples are completely expected from its mass
+dependence.
+
+Left panel shows the overdensity dependence on pair mass. 
+Higher mass pairs are located in high density regions.
+The $2\sigma$ and $3\sigma$ samples having a narrower mass range as 
+shown in previous figure, are consequently located within a narrower 
+range of overdensities $0.0<\delta<4.0$ peaking at $\delta \sim 1$. 
+This is also consistent with the fact that these samples are mostly 
+found in filaments and sheets. 
+The average overdensity of $2\sigma$ and $3\sigma$ samples is expected
+from the values in the GS within the same mass range.
+
+Middle and right panels show web ellipciticy and absolute prolateness
+dependence on mass. Again we noticed that within the same mass range,
+the $2\sigma$ and $3\sigma$ average ellipciticy and prolateness does not
+differ significantly from GS
+For the $2\sigma$ and $3\sigma$ samples most of the pairs are located
+in a narrow range for ellipticities in the range $0.1<e<1.0$, and
+prolateness $0.5<p<0.5$.
+
+%the cumulative distribution for
+%the ellipticity and prolateness. The general sample presents a wide
+%range in ellipticity that can range from $-30<e<30$. For the $2\sigma$
+%and $3\sigma$ samples most of the pairs are now located in a narrow
+%range for ellipticities in the range $0.1<e<1.0$. This condition on
+%the ellipticity together with the fact that $\delta>0$ implies that
+%the prolateness in these samples must be bounded by
+%$-1.0<p<1.0$. We actually find that they most of the pairs are bounded
+%to an even narrower range $0.5<p<0.5$.
+
+%Figure \ref{fig:delta_FA} shows two panels with the joint scatter plot
+%for the ellipticity and the prolateness as a function of the
+%overdensity. For clarity we only include the general and $3\sigma$
+%samples. In the left panel (ellipticity) we see the a simple cut in
+%the overdensity is not enough to explain the narrow ranges in the
+%ellipticity; the LG pairs in the $3\sigma$ sample are located towards
+%low ellipticity values. In the right panel (prolateness) we find a
+%similar situation; a cut in the overdensity would produced a wider
+%distribution in prolateness values than the one featured by the
+%$3\sigma$ sample.
 
@@
 
-\subsection{Overdensity, Ellipticity and Anisotropy}
-
-We now describe the preferred place of the LG samples in terms of the
-overdensity, ellipticiy and anisotropy as defined in Section
-\ref{sec:simulation}.
-
-Figure \ref{fig:median_overdensity} shows dependency of overdensity,
-ellipciticy, and prolateness on pair mass for the different samples.
-General sample is represented by the solid lines with the associated 
-errors covered by the shaded region.
-
-Left panel shows the overdensity dependence on mass where higher mass
-pairs are located in high density regions.
-The $2\sigma$ and $3\sigma$ samples having a narrower mass range as 
-shown in previous figure, are consequently located within a narrower 
-range of overdensities $0.0<\delta<4.0$ peaking at $\delta \sim 1$. 
-This is also consistent with the fact that these samples are mostly 
-found in filaments and sheets. 
-Average overdensity of $2\sigma$ and $3\sigma$ samples show no 
-significant difference from the General sample within the same mass 
-range.
-
-%Figure \ref{fig:density} shows that the range of overdensities for the
-%general pair sample spans almost two orders of magnitude from
-%underdense regions $\delta<0$ to high density regions $\delta\sim 30$,
-%with a distribution peaking around $\delta \sim 0$. In contrast the
-%$2\sigma$ and $3\sigma$ samples are located within a narrower range of
-%overdensities $0.0<\delta<4.0$ peaking at $\delta \sim 1.5$. This is
-%consistent with the fact that these samples are mostly found in
-%filaments and sheets.
-
-Middle and right panels show web ellipciticy and absolute prolateness
-dependence on mass. Again we noticed that within the same mass range,
-the $2\sigma$ and $3\sigma$ average ellipciticy and prolateness does not
-differ significantly from General sample.
-For the $2\sigma$ and $3\sigma$ samples most of the pairs are located
-in a narrow range for ellipticities in the range $0.1<e<1.0$, and
-prolateness $0.5<p<0.5$.
-
-%the cumulative distribution for
-%the ellipticity and prolateness. The general sample presents a wide
-%range in ellipticity that can range from $-30<e<30$. For the $2\sigma$
-%and $3\sigma$ samples most of the pairs are now located in a narrow
-%range for ellipticities in the range $0.1<e<1.0$. This condition on
-%the ellipticity together with the fact that $\delta>0$ implies that
-%the prolateness in these samples must be bounded by
-%$-1.0<p<1.0$. We actually find that they most of the pairs are bounded
-%to an even narrower range $0.5<p<0.5$.
-
-%Figure \ref{fig:delta_FA} shows two panels with the joint scatter plot
-%for the ellipticity and the prolateness as a function of the
-%overdensity. For clarity we only include the general and $3\sigma$
-%samples. In the left panel (ellipticity) we see the a simple cut in
-%the overdensity is not enough to explain the narrow ranges in the
-%ellipticity; the LG pairs in the $3\sigma$ sample are located towards
-%low ellipticity values. In the right panel (prolateness) we find a
-%similar situation; a cut in the overdensity would produced a wider
-%distribution in prolateness values than the one featured by the
-%$3\sigma$ sample.
-
 \subsection{Spin and Orbital Angular Momentum}

### 2014-08-05 paper/main.tex
new results

@@
 momentum of the pair, normal to its orbital plane; the second is
-$\hat{r}$, the vector that connects the halos in the pair. 
+$\hat{r}$, the vector that connects the halos in the pair which can be
+related to the alignment of the radial velocities to the web.
 We quantify the alignment using the absolute value of the cosinus of
@@
 in a narrow range for ellipticities in the range $0.1<e<1.0$, and
-prolateness $0.5<p<0.5$.
-
-%the cumulative distribution for
-%the ellipticity and prolateness. The general sample presents a wide
-%range in ellipticity that can range from $-30<e<30$. For the $2\sigma$
-%and $3\sigma$ samples most of the pairs are now located in a narrow
-%range for ellipticities in the range $0.1<e<1.0$. This condition on
-%the ellipticity together with the fact that $\delta>0$ implies that
-%the prolateness in these samples must be bounded by
-%$-1.0<p<1.0$. We actually find that they most of the pairs are bounded
-%to an even narrower range $0.5<p<0.5$.
-
-%Figure \ref{fig:delta_FA} shows two panels with the joint scatter plot
-%for the ellipticity and the prolateness as a function of the
-%overdensity. For clarity we only include the general and $3\sigma$
-%samples. In the left panel (ellipticity) we see the a simple cut in
-%the overdensity is not enough to explain the narrow ranges in the
-%ellipticity; the LG pairs in the $3\sigma$ sample are located towards
-%low ellipticity values. In the right panel (prolateness) we find a
-%similar situation; a cut in the overdensity would produced a wider
-%distribution in prolateness values than the one featured by the
-%$3\sigma$ sample.
+prolateness $|p|<0.5$.
 
@@
 
-We explore the alignment of the pairs with respect to the cosmic
-web. 
-We define the unit vector $\hat{n}$, normal to the pair orbital plane 
-computed from the pair positions and relative velocity.
-%First we define the unit vector $\hat{r}$ that links the two
-%halos. 
-Then, we compute the dot product of $\hat{n}$ and each one of
-the three eigenvectors for the three samples.
+We now study the alignment of the LG with respect to the cosmic web.
 
-In Figure
-\ref{fig:alignment} we show the main result of that study, it
-presents the cumulative distribution of
-$\mu\equiv\hat{e}_i\cdot\hat{n}$ for the three eigenvectors $i=1,2,3$. 
-Lines indicate the different samples.
-The straight line corresponds to the expected result for a
-random vector distribution.
+\subsubsection{Orbital Angular Momentum}
 
-From this Figure we can see two important features:
-First, there is a strong anti-alignment signature between $\hat{n}$ 
-and the third eigenvector, and this signature reverses with the first eigenvector.
-However, in the case of the second eigenvector, no significant deviations are found.
-Second, for $\hat{e}_3$ vector the anti-alignment become stronger for 
-the samples more closely related to the LG, then for 2$\sigma$ it is 
-stronger than for 3$\sigma$, and the latter is stronger than for General 
-sample.
+Figure \ref{fig:alignment_n} and \ref{fig:alignment_r} show  the main result of that study.
+They present the cumulative distribution of
+$\mu\equiv\hat{e}_i\cdot\hat{n}$ and $\mu\equiv\hat{e}_i\cdot\hat{r}$
+for the three eigenvectors $i=1,2,3$.   
+Lines in each panel correspond to different samples.
+The straight line across the diagonal shows the expected
+result for vectors with randomly distributed directions.
 
-%Figure \ref{fig:scheme} depicts a scheme of the alignment tendencies
-%for pairs in all samples, where the pair members positions and 
-%velocities tend to align with $\hat{e}_3$ vector.
-%The alignment between the peculiar velocities and the $\hat{e}_3$ 
-%eigenvector was already reported in \citet{ForeroRomero2014} for all
-% halos regardles of its mass.
+For the alignment of $\hat{n}$ in Figure \ref{fig:alignment_n} there
+are two important features.
+First the alignments themselves. 
+There is a strong anti-alignment signature between $\hat{n}$ and the
+third eigenvector. 
+With respect to the second eigenvector the distribution is consistent
+with no aligment. 
+For the first eigenvector there is a strong alignment, an expected
+result after considering the results with the other eigenvectors and
+keeping in mind that the eigenvectors are orthonormal.
+Second, the alignment strenght changes for the different samples. 
+For the anti-alignment with $\hat{e}_3$ the signal strenghtens as we
+move from the GS to the 3$\sigma$ into the 2$\sigma$ sample.
 
 Quantitatively, the anti-alignment feature found with the $\hat{e}_3$ 
-vector means that for 2$\sigma$ sample, $\sim 50\%$ pairs have $\mu<0.2$,
-and $\sim 75\%$ pairs have $\mu<0.4$.
-We also test that does not change significantly on environment type, in particular 
-these trends hold very well for pairs in filaments and walls.
+vector means that for 2$\sigma$ sample, $\sim 50\%$ pairs have
+$|\mu|<0.2$ ($78$ degrees angle), and $\sim 75\%$ pairs have $|\mu|<0.4$
+($66$ degrees angle). 
+These signals do not change significantly on
+different environments as has been already show in different alignment
+studies that similar \citep{Libeskind2013} or identical
+\citep{ForeroRomero2014} web finding techniques as ours.
+In particular  these trends hold for pairs in filaments and walls.
+If we consider only pairs in filaments, we have that the pair orbital
+angular momentum tends to be perpendicular to the filament direction,
+in the case of sheets it tends to lie within the sheet plane.
 
-If we consider only pairs in filaments, we have that the pair orbit tends
-to be perpendicular to the filament direction, and both pair members lie 
-along the filament, if we recall the 3$\sigma$-2$\sigma$ samples are 
-constrained with a mostly radial velocity component, then the pairs 
-are moving into the filament.
-In the case of sheets, we have the pair orbital plane  tend to lie within
- the sheet plane.
+Can the increase of the alignment strenght in the different samples be
+explained as a consequence of different mass dependencies as the
+results in the previous section? No. 
+In Figure \ref{fig:median_alignment_n} we show the median of
+$\mu\equiv\hat{e}_i\cdot\hat{n}$ in different total mass bins.
+Lines show the median $\mu$-mass relation for the three 
+eigenvectors in the GS, Dots represent the results for the
+2$\sigma$-3$\sigma$ samples. 
+In a mass range around $1.5-2.0 \times 10^{12}$ \msun the median of
+$\mu$ decreases as we increase the constraints on the pairs, not as a
+result of narrowing mass selection.
 
-These alignment features are in agreement with the scenario that pairs 
-created in-situ or falling into a filament/wall align their orbits with 
-the large scale structure in a relaxation process where pair members
-tend to moves along the slowest collapsing directions.
-However, the most intriguing feature is the dependence of this alignment
-with how close we represent the LG, is still not clear.
-We explore if the pair masses are responsible of this, but we found 
-no dependence at all.
+\subsubsection{Radial motion}
 
-In Figure \ref{fig:median_alignment_n} we show the relation between the median 
-of $\mu\equiv\hat{e}_i\cdot\hat{n}$ and mass for the general sample, and found 
-no significant relation.
-Lines in the figure show the median $\mu$-mass relation for the three 
-eigenvectors in the General sample.
-Dots represent the median $\mu$ for the three eigenvectors in the 
-2$\sigma$-3$\sigma$ samples.
-In the case of $\|\hat{e}_3\cdot\hat{n}\|$, the figure clearly shows for a fixed mass
-range around $1.5-2.0 \times 10^{10}$ \msun, that the median $\mu$ decreases as we
-better constraint the LG samples, being larger for General sample and smaller for 
-2$\sigma$ sample accordingly.
+For the alignment of $\hat{r}$ in Figure \ref{fig:alignment_r} there
+are similar features as in the case of $\hat{n}$. 
+In this case we find that the vector $\hat{r}$
+is strongly aligned along the direction defined by
+$\hat{e}_3$ and anti-aligned along $\hat{e}_1$; correspondingly the
+signal along $\hat{e}_2$ is rather weak.
 
-%From this Figure we first see that there is a clear distinct behavior
-%between the general samples and the 3$\sigma$-2$\sigma$ samples. The
-%general sample tend to be aligned along the $\hat{e}_3$ vector, the
-%3$\sigma$ sample does not show any strong alignment and the 2$\sigma$
-%pairs tend to be perpendicular to the $\hat{e}_3$ vector and slightly
-%parallel to $\hat{e}_1$. These trends hold in filaments and walls.
+In this case we also find a stronger signal as we move into more restrictive
+samples, although the signal from the GS is already very
+significant. Quantitatively, the alignment feature with $\hat{e}_3$
+means that for the 2$\sigma$ and 3$\sigma$ samples, $\sim 50\%$ pairs
+have $|\mu|>0.8$ ($36$ degrees angle) and $\sim 25\%$ pairs have
+$|\mu|<0.95$ ($18$ degrees angle).
 
-%Let's focus on filaments first. That result means that in the general
-%sample the two halos tend to lie along the filament, while in the
-%2$\sigma$-3$\sigma$ samples they are located perpendicular to the
-%filament. If one considers that in these samples the motion is radial,
-%that means that the pairs are moving into the filament.
+Considering that the 2$\sigma$ and 3$\sigma$ samples move primarely
+along the radial direction, we can say that the motion of the LG
+halos is mostly done along the $\hat{e}_3$ vectors, consistent with
+recent results that report a strong alignment of halo's peculiar
+velocities along that direction \citep{ForeroRomero2014}.
 
-%In the case of sheets, the pairs in the general sample tend to lie on
-%the sheet plane along the direction of the slowest collapsing
-%direction. In the 2$\sigma$ samples the pairs are not constrained to
-%the plane anymore and are perpendiculat to the $\hat{e}_3$
-%vector. Considering the preferential radial motion of these pairs,
-%that mens that the pairs are moving into the pancake all over a plane that
-%is itself perpendicular to the sheet.
+\subsubsection{Halo Spin}
 
-\subsection{Spin and Orbital Angular Momentum}
+We also explore the alignment of the  angular momentum (spin) of each pair
+member $\hat{j}_A$ and $\hat{j}_B$ with each other, the orbital
+angular momentum and with the cosmic web.
 
-In $4.2$ we defined the unit vector $\hat{n}$, normal to the pair 
-orbital plane which can be asociated with the orbital angular 
-momentum direction $\hat{J}$.
-There, we show several alignment features of the pair orbital
-momentum with the environment.
-In this subsection we explore the alignement of the individual spin
-angular momentum of each pair member $\hat{j_A}$ and $\hat{j_B}$ with
-each other and with the orbital angular momentum.
+Figure \ref{fig:jj_alignment} shows the cumulative distribution of dot
+product between angular momentum of the  two halos. We find a a slight alignment
+of spin vectors for the $2\sigma$ sample with a median aroung
+$|\mu|\sim 0.7$ ($45$ degrees) However, we found no significant
+alignment with the orbital angular momentum or the cosmic web.
 
-We show in figure \ref{fig:jj_alignment} the cumulative distribution of
-dot product between the spin of both members in the pair.
-We found a slight alignment of spin vectors for the $2\sigma$ sample.
-However, we found no significant alignment between spin and orbital angular 
-momentum for any sample.
-
-In the LG, the angle between MW and M31 spin is $\sim60^{\circ}$ and the
-angles between spins and orbital angular momentum are $\sim33^{\circ}$
-and $\sim76^{\circ}$ for MW and M31 respectively \citep{2012ApJ...753....9V}.
-Then the LG show no particular alignement aswell.
+In the LG, the angle between MW and M31 spin is $\sim60^{\circ}$
+($|\mu|=0.5$) and the angles between spins and orbital angular
+momentum are $\sim33^{\circ}$ ($|\mu|=0.83$) and $\sim76^{\circ}$
+($|\mu|=0.24$) for MW and M31 respectively
+\citep{2012ApJ...753....9V}. Consistent with our results of no particular
+alignement.
 
@@
 
+These alignment features are in agreement with the scenario that pairs 
+created in-situ or falling into a filament/wall align their orbits with 
+the large scale structure in a relaxation process where pair members
+tend to moves along the slowest collapsing directions.
+However, the most intriguing feature is the dependence of this alignment
+with how close we represent the LG, is still not clear.
+We explore if the pair masses are responsible of this, but we found 
+no dependence at all.
+
 \section{Conclusions}

### 2014-08-07 paper/main.tex
new version

@@
 $\Lambda$CDM cosmology.  We use the Hessian of the gravitational
-potential to define the cosmic web, where regions are classified as
-either peak, sheet, filament or void.  The LG in the simulations are
-split into two samples.  The first is a general sample composed by
-halo pairs with similar masses and isolation criteria as observed in
-the LG.  The second is a subset with additional kinematic constaints.
-We find that the pairs in the LG sample with all constraints are: i)
-Preferentially located in filaments and sheets, ii) located in in a
-narrow range of local overdensity $0<\delta<4$, web ellipticity
-$0.1<e<1.0$ and prolateness $-0.5<p<0.5$.  iii) Clearly aligned with
-the cosmic web, in particular for pairs in filaments/sheets the
-orbital angular momentum tends to be perpendicular to the filament
-direction or the sheet plane. A stronger alignment is present for the
-vector linking the two halos, which lies along the filament or the
-sheet plane.  We show that the first and second results are expected
-trends with the LG total mass.  However, the strong alignment with the
-cosmic web cannot be explained in the same way.
+potential to classify regions in the cosmic web as a peak, sheet,
+filament or void.  The LG is represented by two samples of halos
+pairs. The first is a general sample composed by halo pairs with
+similar masses and isolation criteria as observed in the LG.  The
+second is a subset with additional kinematic constaints. We find that
+the pairs in the LG sample with all constraints are: i) Preferentially
+located in filaments and sheets, ii) located in in a narrow range of
+local overdensity $0<\delta<4$, web ellipticity $0.1<e<1.0$ and
+prolateness $-0.5<p<0.5$.  iii) Clearly aligned with the cosmic web,
+in particular for pairs in filaments/sheets the orbital angular
+momentum tends to be perpendicular to the filament direction or the
+sheet plane. A stronger alignment is present for the vector linking
+the two halos, which lies along the filament or the sheet plane.  We
+show that the first and second results are expected trends with the LG
+total mass. However, the strong alignment with the cosmic web cannot
+be explained by a simple mass dependency.
 
@@
 
-\subsection{Alignment along the cosmic web}
+\subsection{Alignments withthe cosmic web}
 
-We now study the alignment of the LG with respect to the cosmic web.
+We now study different alignments of the LG with respect to the cosmic web.
 
-\subsubsection{Orbital Angular Momentum}
-
-Figure \ref{fig:alignment_n} and \ref{fig:alignment_r} show  the main result of that study.
-They present the cumulative distribution of
-$\mu\equiv\hat{e}_i\cdot\hat{n}$ and $\mu\equiv\hat{e}_i\cdot\hat{r}$
-for the three eigenvectors $i=1,2,3$.   
+{\bf Orbital Angular Momentum}. Figure \ref{fig:alignment_n} shows the
+cumulative distribution of $\mu\equiv\hat{e}_i\cdot\hat{n}$  for the
+three eigenvectors $i=1,2,3$.    
 Lines in each panel correspond to different samples.
@@
 
-For the alignment of $\hat{n}$ in Figure \ref{fig:alignment_n} there
-are two important features.
+There are two important features in Figure \ref{fig:alignment_n}.
 First the alignments themselves. 
@@
 angular momentum tends to be perpendicular to the filament direction,
-in the case of sheets it tends to lie within the sheet plane.
+in the case of sheets it tends to lie perpendicular to the sheet plane.
 
@@
 
-\subsubsection{Radial motion}
-
-For the alignment of $\hat{r}$ in Figure \ref{fig:alignment_r} there
-are similar features as in the case of $\hat{n}$. 
+{\bf Radial Vector}.  Figure \ref{fig:alignment_r} presents the
+results for the eigenvectors alignments with respect to the vector
+connecting the two halos. 
 In this case we find that the vector $\hat{r}$
@@
 
-In this case we also find a stronger signal as we move into more restrictive
+We also find a stronger signal as we move into more restrictive
 samples, although the signal from the GS is already very
-significant. Quantitatively, the alignment feature with $\hat{e}_3$
+significant. 
+Quantitatively, the alignment feature with $\hat{e}_3$
 means that for the 2$\sigma$ and 3$\sigma$ samples, $\sim 50\%$ pairs
@@
 
-\subsubsection{Halo Spin}
-
-We also explore the alignment of the  angular momentum (spin) of each pair
-member $\hat{j}_A$ and $\hat{j}_B$ with each other, the orbital
-angular momentum and with the cosmic web.
+{\bf Halo Spin}. We also explore the alignment of the  angular
+momentum (spin) of each pair member $\hat{j}_A$ and $\hat{j}_B$ with
+each other, the orbital angular momentum and with the cosmic web.
 
 Figure \ref{fig:jj_alignment} shows the cumulative distribution of dot
-product between angular momentum of the  two halos. We find a a slight alignment
-of spin vectors for the $2\sigma$ sample with a median aroung
+product between angular momentum of the  two halos. We find a a slight
+alignment of spin vectors for the $2\sigma$ sample with a median around
 $|\mu|\sim 0.7$ ($45$ degrees) However, we found no significant
-alignment with the orbital angular momentum or the cosmic web.
+alignment with the orbital angular momentum nor the cosmic web. This
+is also consistent with recent results that show that the spin
+alignment of halos of masses around $10^{12}$\Msun is very weak
+\citep{ForeroRomero2014}.
 
@@
 
-We explored the characteristics of the LG location in the cosmic web.
+The mass range of the LG pairs is tightly correlated with the
+properties of the web where they reside as shown in Table
+\ref{table:web_type} and Figure \ref{fig:median_fraction}. Recent
+analytical \citep{Alonso2014} and numerical studies \citep{Metuki2014}
+have shown that the local overdensity is the dominant web property
+that define the abundance and properties of halos. Quantities derived
+from the tidal tensor play a secondary role.
 
-LG pairs are preferentially located in filaments and sheets. The mass range
-of the pairs sample plays an important role in the fractions for each environment
-type as shown in table $1$ and figure $1$.
+Therefore, in our case, the fact that the preferred LG total mass is
+around $1-4\times 12^{12}$\Msun implies that the preferred environment
+are filaments and sheets with an overdensity close to the average
+value, with values for the ellipticity and prolateness also correlated
+with the overdensity.
 
-There is a clear anti-alignment between the third eigenvector and the vector normal 
-to the pair orbital plane. This feature is not mass dependant as can be shown in
-figure $3$.
-For pairs in filaments this means the pair orbit tends to be perpendicular to the 
-filament direction, and both pair members lie along the filament, and in the case 
-of pairs in sheets, we have the pair orbital plane lie in the sheet plane.
-We also found this anti-alignment becomes stronger for the samples being more 
-closely related to the LG, it means it is stronger for $2\sigma$ sample.
-All these alignment features are consistent with pair orbits relaxing their 
-movements towards the slowest collapsing directions at larger scales.
-
-LG pairs are located in a narrow range of local overdensity, ellipciticy and prolateness.
-And this is consistent with the narrow mass range selection of specific samples.
-
-The LG spin and orbital angular momentum have no particular alignment,
-and we see no significan alignments in our LG pairs, however for the alignment
-between pair spins we found a slight alignment signature for $2\sigma$ sample as
-can be seen in figure $5$.
+However, there are alignment signals with the cosmic web that are not
+mass dependent and seem to be stronger for different LG samples. There
+is a clear anti-alignment between the third eigenvector and the
+orbital angular momentum vector, meaning that this vector is
+perpendicular to filaments and the sheets, depending on the
+particular web environment. We also found that the vector joining the
+LG halos are aligned with the third eigenvector; i.e. the pair is
+aligned with the filaments and lies on the sheets.
 
@@
 tend to moves along the slowest collapsing directions.
-However, the most intriguing feature is the dependence of this alignment
-with how close we represent the LG, is still not clear.
-We explore if the pair masses are responsible of this, but we found 
-no dependence at all.
+
+The most interesting feature is that these alignments are
+tighter as we narrow the kinematic conditions of the LG towards the
+observed values. A deeper understanding requires the study of the full
+formation history and coevolution with the cosmic web, a task beyond
+the scope of the work presented here.
 

### 2014-08-08 paper/main.tex
algunos typo

@@
 \title{The Place of the Local Group in the Cosmic Web}
-\author{J. E. Forero-Romero$^1$ and R. Gonz\'alez$^2$}
+\author{J. E. Forero-Romero$^1$ and R. Gonz\'alez$^{2,3}$}
 \affil{$^1$ Departamento de F\'{i}sica, Universidad de los Andes,
@@
   Av. Vicu\~na Mackenna 4860, Santiago, Chile\\  
+  $^3$ Centro de Astro-Ingenier\'{i}a, Pontificia Universidad Cat\'olica,
+  Av. Vicu\~na Mackenna 4860, Santiago, Chile
 }
@@
 Furthermore, if we select pairs constrained
-within $2\sigma$ error fron current observational measurements of the
+within $2\sigma$ error from current observational measurements of the
 velocity components and distance to M31, there are only $46$ systems
@@
 direction. However, if we look in a smaller volume below scales of
-$\sim 6$ \mpc, there is a clear alignment of th the MW-M31 orbit with
+$\sim 6$ \mpc, there is a clear alignment of the MW-M31 orbit with
 a local plane as shown by Figure $3$ in \citet{2013AJ....146...69C}.
@@
 \begin{center}
-  \includegraphics[width=0.48\textwidth]{alignments_e1_n_all_environments.pdf} 
-  \includegraphics[width=0.48\textwidth]{alignments_e2_n_all_environments.pdf} 
-  \includegraphics[width=0.48\textwidth]{alignments_e3_n_all_environments.pdf} 
+  \includegraphics[width=0.46\textwidth]{alignments_e1_n_all_environments.pdf} 
+  \includegraphics[width=0.46\textwidth]{alignments_e2_n_all_environments.pdf} 
+  \includegraphics[width=0.46\textwidth]{alignments_e3_n_all_environments.pdf} 
 \end{center}
@@
 \begin{center}
-  \includegraphics[width=0.48\textwidth]{alignments_e1_r_all_environments.pdf} 
-  \includegraphics[width=0.48\textwidth]{alignments_e2_r_all_environments.pdf} 
-  \includegraphics[width=0.48\textwidth]{alignments_e3_r_all_environments.pdf} 
+  \includegraphics[width=0.46\textwidth]{alignments_e1_r_all_environments.pdf} 
+  \includegraphics[width=0.46\textwidth]{alignments_e2_r_all_environments.pdf} 
+  \includegraphics[width=0.46\textwidth]{alignments_e3_r_all_environments.pdf} 
 \end{center}
@@
 \section*{Acknowledgements}
-REG was supported by Proyecto Financiamiento Basal PFB06 and Comite Mixto ESO.
+REG was supported by Proyecto Financiamiento Basal PFB-06 'Centro de Astronomia y Tecnologias Afines' and Proyecto Comit\'e Mixto ESO 3312-013-82.
+The Geryon cluster at the Centro de Astro-Ingenieria UC was extensively used for the calculations performed in this paper.
+The Anillo ACT-86, FONDEQUIP AIC-57, and QUIMAL 130008 provided funding for several improvements to the Geryon cluster.
 

### 2014-08-12 paper/main.tex
updated plots in the manuscript
new abstract

@@
 
+%@arxiver{fig1.pdf,fig4.png,fig15.eps}
+
 \shorttitle{The Local Group in the Cosmic Web}
@@
 location in the cosmic web using a cosmological simulation in the
-$\Lambda$CDM cosmology.  We use the Hessian of the gravitational
-potential to classify regions in the cosmic web as a peak, sheet,
-filament or void.  The LG is represented by two samples of halos
-pairs. The first is a general sample composed by halo pairs with
-similar masses and isolation criteria as observed in the LG.  The
-second is a subset with additional kinematic constaints. We find that
-the pairs in the LG sample with all constraints are: i) Preferentially
-located in filaments and sheets, ii) located in in a narrow range of
-local overdensity $0<\delta<4$, web ellipticity $0.1<e<1.0$ and
-prolateness $-0.5<p<0.5$.  iii) Clearly aligned with the cosmic web,
+$\Lambda$CDM cosmology.  
+We use the Hessian of the gravitational potential to classify regions
+in the cosmic web as a peak, sheet, filament or void.  
+The LG is represented by two samples of halo
+pairs. 
+The first is a general sample composed by pairs with
+similar masses and isolation criteria as observed in the LG.  
+The second is a subset with additional kinematic constaints also
+constrained by observations. 
+We find that the pairs in the LG sample with all constraints are: (i)
+preferentially   located in filaments and sheets, (ii) located in in a
+narrow range of local overdensity $0<\delta<2$, web ellipticity $0.1<e<1.0$ and
+prolateness $-0.4<p<0.4$.  (iii) strongly aligned with the cosmic web,
 in particular for pairs in filaments/sheets the orbital angular
 momentum tends to be perpendicular to the filament direction or the
-sheet plane. A stronger alignment is present for the vector linking
-the two halos, which lies along the filament or the sheet plane.  We
-show that the first and second results are expected trends with the LG
-total mass. However, the strong alignment with the cosmic web cannot
-be explained by a simple mass dependency.
+sheet plane. 
+A stronger alignment is present for the vector linking the two halos,
+which lies along the filament or the sheet plane.  
+We show that the first and second results are expected trends with the LG
+total mass. 
+However, the strong alignment with the cosmic web cannot be explained
+by a simple mass dependency. 
+This precise characterization of the expected place of the LG in the
+cosmic web in a $\Lambda$CDM cosmology opens the door to a detailed
+understanding of diverse features characterizing the Milky Way and the
+Andromeda galaxies.
 
@@
 
-%lg rare
 The spatial and kinematic configuration of the Local Group
@@
 \begin{center}
-  \includegraphics[width=0.48\textwidth]{histogram_mass_distro.pdf}
+  \includegraphics[width=0.50\textwidth]{fig1.pdf}
 \caption{Mass distribution of pairs in the different environments
@@
 \begin{center}
-  \includegraphics[width=0.31\textwidth]{median_mass_overdensity.pdf} 
-  \includegraphics[width=0.32\textwidth]{median_mass_ellipticity.pdf} 
-  \includegraphics[width=0.32\textwidth]{median_mass_prolateness.pdf} 
+  \includegraphics[width=0.31\textwidth]{fig2a.pdf}
+  \includegraphics[width=0.32\textwidth]{fig2b.pdf}
+  \includegraphics[width=0.32\textwidth]{fig2c.pdf}
 \caption{Mass dependency of the average dark matter overdensity (left),
@@
 
-\begin{figure}
+\begin{figure*}
 \begin{center}
-  \includegraphics[width=0.46\textwidth]{alignments_e1_n_all_environments.pdf} 
-  \includegraphics[width=0.46\textwidth]{alignments_e2_n_all_environments.pdf} 
-  \includegraphics[width=0.46\textwidth]{alignments_e3_n_all_environments.pdf} 
+  \includegraphics[width=0.32\textwidth]{fig3a.pdf}
+  \includegraphics[width=0.32\textwidth]{fig3b.pdf}
+  \includegraphics[width=0.32\textwidth]{fig3c.pdf}
 \end{center}
@@
     \label{fig:alignment_n}}  
-\end{figure}
+\end{figure*}
 
-\begin{figure}
+\begin{figure*}
 \begin{center}
-  \includegraphics[width=0.46\textwidth]{alignments_e1_r_all_environments.pdf} 
-  \includegraphics[width=0.46\textwidth]{alignments_e2_r_all_environments.pdf} 
-  \includegraphics[width=0.46\textwidth]{alignments_e3_r_all_environments.pdf} 
+  \includegraphics[width=0.32\textwidth]{fig4a.pdf}
+  \includegraphics[width=0.32\textwidth]{fig4b.pdf}
+  \includegraphics[width=0.32\textwidth]{fig4c.pdf}
 \end{center}
@@
     \label{fig:alignment_r}}  
-\end{figure}
-
-%\begin{figure}
-%  \begin{center}
-%    \includegraphics[width=0.48\textwidth]{scheme.pdf}
-%    \caption{Schematic picture of the strongest alignment tendencies in
-%      the the General and $2\sigma$-$3\sigma$ samples. The alignment
-%      between the peculiar velocities and the $\hat{e}_3$ eigenvector was
-%      reported in \citet{ForeroRomero2014} for all halos regardles of its
-%      mass.
-%      \label{fig:scheme}}
-%  \end{center}
-%\end{figure}
-
-%\begin{figure}
-%\begin{center}
-%  \includegraphics[width=0.48\textwidth]{histogram_mass_distro.pdf} 
-%\caption{Mass dependency of the fraction of pairs in the different
-%  environemnts.
-%\label{fig:median_fraction}}
-%\end{center}
-%\end{figure}
+\end{figure*}
 
@@
 \begin{center}
-  \includegraphics[width=0.48\textwidth]{median_mass_alignment.pdf}
+  \includegraphics[width=0.50\textwidth]{fig5.pdf}
 \caption{Mass dependency of the median value for the dot product
@@
 \begin{center}
-  \includegraphics[width=0.49\textwidth]{alignments_jj_all_environments.pdf}
+  \includegraphics[width=0.50\textwidth]{fig6.pdf}
 \end{center}
@@
 \end{figure}
-
-%\begin{figure*}
-%\begin{center}
-%  \includegraphics[width=0.49\textwidth]{ELL_delta_scatter.pdf}
-%  \includegraphics[width=0.49\textwidth]{PROL_delta_scatter.pdf}
-%\end{center}
-%\caption{Ellipticity and prolateness versus the overdensity for the pairs
-%in the general and $3\sigma$ samples. \label{fig:delta_ELL_PROL}} 
-%\end{figure*}
-
-%\begin{figure}
-%\begin{center}
-%  \includegraphics[width=0.50\textwidth]{density_histogram.pdf}
-%\end{center}
-%\caption{Overdensity distribution for the pairs in the three samples.
-%    \label{fig:density}}  
-%\end{figure}
 

### 2014-08-12 paper/main.tex
simulation and web finding algorithm

@@
 
-\title{The Place of the Local Group in the Cosmic Web}
+\title{The Expected Place of the Local Group in the Cosmic Web}
 \author{J. E. Forero-Romero$^1$ and R. Gonz\'alez$^{2,3}$}
@@
 We use the Hessian of the gravitational potential to classify regions
-in the cosmic web as a peak, sheet, filament or void.  
+on scales of $\sim 2$ Mpc as a peak, sheet, filament or void.  
 The LG is represented by two samples of halo
@@
 prolateness $-0.4<p<0.4$.  (iii) strongly aligned with the cosmic web,
-in particular for pairs in filaments/sheets the orbital angular
+in particular for pairs in filaments/sheets the pair orbital angular
 momentum tends to be perpendicular to the filament direction or the
@@
 total mass. 
-However, the strong alignment with the cosmic web cannot be explained
+However, the strong alignments with the cosmic web cannot be explained
 by a simple mass dependency. 
+Additionally, we fail to find a strong correlation of the spin of each
+halo in the pair with the cosmic web.
 This precise characterization of the expected place of the LG in the
@@
   references therein]{1975ApJ...196..313S,2011MNRAS.415L..16A}. 
-Environment around the Local Group has density quite close to the
+The environment around the Local Group has density quite close to the
 average density of the universe
 \citep{2003ApJ...596...19K,2005AJ....129..178K}. 
-In addition, the
-closest massive galaxy cluster, the Virgo Cluster, is $\approx
-16.5\ \mpc$ away \citep{2007ApJ...655..144M}.
+In addition, the closest massive galaxy cluster, the Virgo Cluster, is
+$\approx 16.5\ \mpc$ away \citep{2007ApJ...655..144M}.
 
-All this combination of features make LG analogues rare to
+This combination of features make LG analogues rare to
 find. 
@@
 clusters. 
+A similar abundance was found by \cite{ForeroRomero2011} by comparing the
+formation history of LG pairs in constrained simulations with the
+results of unconstrained cosmological simulations.
 
@@
 challenge the \lcdm model.  
-
-Another definition of LG analogues is made by
-\citet{2008MNRAS.384.1459L}, but despite differences ocurr in the
+Another definition of LG analogues is made
+by \citet{2008MNRAS.384.1459L}, but despite differences ocurr in the
 definitions and resulting fraction of LG analogues, all are in
 agreement with a low frequency of these pairs.
-%lw08 also look lg analogues
 
-%larger scales & lg env
 To better understand the properties of the LG and how this uncommon
 pair configuration fit in the cosmological context, an immediate
-question arise. What else can we say of the LG at larger scales?. In
-particular, which are the typical/prefered locations of these systems
-within the Cosmic Web?. To what extent is this an expected
-configuration in $\Lambda$CDM.
+question arise. 
+What else can we say of the LG at larger scales?
 
-Looking the LG at larger scales we have it is located in a difuse and
+Observationally, the LG is located in a difuse and
 warped filament/wall conecting Virgo Cluster with Fornax Cluster, some
@@
 Maffei group, NGC $6744$, NGC $5128$, M$101$, M$81$, NGC$1023$, Cen A
-group. At this scale, there is no evident alignment of the MW-M31
-orbital plane with the local filament or the Virgo-Fornax
-direction. However, if we look in a smaller volume below scales of
-$\sim 6$ \mpc, there is a clear alignment of the MW-M31 orbit with
-a local plane as shown by Figure $3$ in \citet{2013AJ....146...69C}.
+group. 
+At this scale, there is no evident alignment of the MW-M31 orbital
+plane with the local filament or the Virgo-Fornax direction. However,
+if we look in a smaller volume below scales of $\sim 6$ \mpc, there is
+a clear alignment of the MW-M31 orbit with a local plane as shown by
+Figure $3$ in \citet{2013AJ....146...69C}.
+
+We can then ask, to what extent is this an expected configuration in
+$\Lambda$CDM? In particular, which are the typical/prefered locations
+of these systems within the Cosmic Web?
 
@@
 In this \manuscript we study the large scale environment of LG 
-analogues in the context of $\Lambda$CDM. We use the Bolshoi
-simulation to explore in what structures they reside and if there is
-any correlation or alignment with the cosmic web. The large scale
-Environment is defined by the cosmic web components identified by
+analogues in the context of $\Lambda$CDM. 
+We use the Bolshoi simulation to explore in what structures they
+reside and if there is any correlation or alignment with the cosmic
+web. 
+The large scale environment is defined by the cosmic web components identified by
 \citet{Tweb}, and we use the LG analogues computed by
-\citet{lganalogues}. We pay spetial attention to quantify the kind of
-environment that hosts LG pairs and their alignments with respect to
-the prefered directions defined by the T-web.
+\citet{lganalogues}.
 
-This \manuscript is organized as follows. In Section \ref{sec:simulation}
+This \manuscript is organized as follows. 
+In Section \ref{sec:simulation}
 we present the N-body cosmological simulation and the algorithm to
-define the cosmic web, next in \ref{sec:lg_analogues} we describe the
+define the cosmic web, next in Section \ref{sec:lg_analogues} we describe the
 sample of LG analogues extracted from the simulation. In
-Section \ref{sec:results} we presents our results to continue with a
-discussion about their implications for our Local Group in Section
-\ref{sec:discussion} to finally conclude in Section
-\ref{sec:conclusions}.
+Section \ref{sec:results} we present our results to wrap up with a
+discussion and conclusions in Section
+\ref{sec:discussion}.
 
@@
 choice. Nevertheless we have checked that the main conclusions of this
-work do not depend on the choise of $\lambda_{\rm th}$.
+work do not depend on the precise choice of $\lambda_{\rm th}$.
 
@@
 We also measure the alignment of the LG halos with respect to the
-cosmic web defined by the eigenvector.
+cosmic web defined by their eigenvectors.
 To this end we characterize each LG pair by two vectors. 
@@
 
-\section{Discussion}
+\section{Discussion and Conclusions}
 \label{sec:discussion}
@@
 
-\section{Conclusions}
-\label{sec:conclusions}
-
 \section*{Acknowledgements}

### 2014-08-12 paper/main.tex
updated the prefered environment

@@
 \times 10^{11}$ \msun $ $ to $ 5 \times 10^{13}$ \msun.  
-Isolation criteria includes a pair closer than $1.3$\mpc, and with no
-massive neighbors within $5$\mpc.
+Isolation criteria includes no halos more masive than each member in
+the pair closer than $1.3$\mpc, and with no massive neighbors within $5$\mpc.
 In addition we require that pairs have no Virgo-like neighbor halo
@@
 
-We also define two subsamples more closely related to the MW-M31 
-dynamics according to the tolerance in additional constraints.
+We also define two subsets of restricted samples (RS) more closely
+related to the MW-M31  dynamics according to the tolerance in
+additional constraints. 
 A sample named $2\sigma$, correspondig to LG analogues constrained by
@@
 our LGs. 
-We find that the LGs in the general sample are located across
-all different evironment without any strong preferences; $1/3$  are
-located in sheets, $1/4$ in peaks, $1/4$ in filaments and the remaning
-$1/6$ in voids.
+We find that the LGs in the GS are located across all different
+evironment without any strong preferences; $1/3$  are located in
+sheets, $1/4$ in peaks, $1/4$ in filaments and the remaning $1/6$ in
+voids.
 
-The situation in the restricted $2\sigma$ and $3\sigma$ samples is very
+The situation in the $2\sigma$ and $3\sigma$ samples is very
 different. 
@@
 
-This difference between the general and the restricted samples is
-due the mass ranges covered by each sample. 
+We find that the difference between the GS and the RS 
+can be explained by the total pair mass.
 In \citet{lganalogues} the mass range covered by $2\sigma$ and $3\sigma$ 
-is very narrow and it is used to constraint the LG mass.
-We show  in table \ref{table:web_type} that subset of the GS
-having a similar mass range to $2\sigma$ and $3\sigma$ reproduces  
-similar environment fractions.
+amples is very narrow and it is used to constraint the LG mass.
+We show in Table \ref{table:web_type} that a subset of the GS
+having a similar mass range than the RS reproduces similar environment
+fractions.
 
-Figure \ref{fig:median_fraction} clearly shows the correlation between
+Figure \ref{fig:median_fraction} summarizes this correlation between
 environment an total pair mass.
 Each line represents the mass distribution of pairs in the four
-different environments for the general sample.
+different environments for the GS.
 High mass pairs tend to be located in  peaks and filaments while less

### 2014-08-12 paper/main.tex
overdensity, ellipticity and and prolateness

@@
 
-We now describe the preferred place of the LG samples in terms of the
+We now characterize the preferred place of the LG samples in terms of the
 web overdensity, ellipticiy and anisotropy as defined in Section
@@
 
-Figure \ref{fig:median_overdensity} shows dependency of the web overdensity,
-ellipciticy, and prolateness on pair mass for the different samples.
+Figure \ref{fig:median_overdensity} shows the dependency of these three
+characteristics  on the total pair mass for the different samples.
 GS is represented by the solid lines with the associated 
@@
 samples.   
-In all cases it is immediatly clear that the range of values for the
-$2\sigma$ and $3\sigma$ samples are completely expected from its mass
-dependence.
+In thre three cases it is evident that the range of values for the
+$2\sigma$ and $3\sigma$ samples are completely expected from the mass
+constraint alone.
 
-Left panel shows the overdensity dependence on pair mass. 
+The left panel shows the overdensity dependence on pair mass. 
 Higher mass pairs are located in high density regions.
@@
 shown in previous figure, are consequently located within a narrower 
-range of overdensities $0.0<\delta<4.0$ peaking at $\delta \sim 1$. 
+range of overdensities $0.0<\delta<2.0$ peaking at $\delta \sim 1$. 
 This is also consistent with the fact that these samples are mostly 
 found in filaments and sheets.
-The average overdensity of $2\sigma$ and $3\sigma$ samples is expected
-from the values in the GS within the same mass range.
 
 Middle and right panels show web ellipciticy and absolute prolateness
-dependence on mass. Again we noticed that within the same mass range,
-the $2\sigma$ and $3\sigma$ average ellipciticy and prolateness does not
-differ significantly from GS
-For the $2\sigma$ and $3\sigma$ samples most of the pairs are located
-in a narrow range for ellipticities in the range $0.1<e<1.0$, and
-prolateness $|p|<0.5$.
+dependence on mass. 
+Again we notice that within the $2\sigma$ and $3\sigma$ mass range,
+the average ellipciticy and prolateness does not differ significantly
+from the GS expectation.
+In the RS samples the pairs are located in a narrow range for
+ellipticities $0.1<e<1.0$ and absolute prolateness $|p|<0.4$.
 

### 2014-08-12 paper/main.tex
final version + possible alignment conflict

@@
 halo in the pair with the cosmic web.
-This precise characterization of the expected place of the LG in the
-cosmic web in a $\Lambda$CDM cosmology opens the door to a detailed
-understanding of diverse features characterizing the Milky Way and the
-Andromeda galaxies.
+Applied to the observed LG, there is a potential conflict between
+these alignments and recent claims of an universal subhalo accretion
+direction. 
+This highlights the relevance of achieving a precise characterization
+of the place of the LG in the cosmic web in a the cosmological context
+provided by $\Lambda$CDM.
 
@@
 
-\subsection{Web Overdensity, Ellipticity and Anisotropy}
+\subsection{Web Overdensity, Ellipticity and Prolateness}
 
@@
 with no aligment. 
-For the first eigenvector there is a strong alignment, an expected
-result after considering the results with the other eigenvectors and
-keeping in mind that the eigenvectors are orthonormal.
+While for the first eigenvector there is a strong alignment, an expected
+result considering the results with the other eigenvectors and
+keeping in mind that they are orthonormal.
 Second, the alignment strenght changes for the different samples. 
@@
 vector means that for 2$\sigma$ sample, $\sim 50\%$ pairs have
-$|\mu|<0.2$ ($78$ degrees angle), and $\sim 75\%$ pairs have $|\mu|<0.4$
-($66$ degrees angle). 
+$|\mu|<0.2$ ($>78$ degrees angle), and $\sim 75\%$ pairs have $|\mu|<0.4$
+($>66$ degrees angle). 
 These signals do not change significantly on
 different environments as has been already show in different alignment
-studies that similar \citep{Libeskind2013} or identical
+studies with similar \citep{Libeskind2013} or identical
 \citep{ForeroRomero2014} web finding techniques as ours.
@@
 In Figure \ref{fig:median_alignment_n} we show the median of
-$\mu\equiv\hat{e}_i\cdot\hat{n}$ in different total mass bins.
+$\mu\equiv\hat{e}_i\cdot\hat{n}$ in different mass bins.
 Lines show the median $\mu$-mass relation for the three 
-eigenvectors in the GS, Dots represent the results for the
+eigenvectors in the GS, dots represent the results for the
 2$\sigma$-3$\sigma$ samples. 
-In a mass range around $1.5-2.0 \times 10^{12}$ \msun the median of
-$\mu$ decreases as we increase the constraints on the pairs, not as a
-result of narrowing mass selection.
+Around the total mass $1.5-2.0 \times 10^{12}$ \msun in the RS
+samples, the median of $\mu$ decreases as we tighten constraints
+on the pairs, but not as a result of the narrowing mass selection.
 
@@
 means that for the 2$\sigma$ and 3$\sigma$ samples, $\sim 50\%$ pairs
-have $|\mu|>0.8$ ($36$ degrees angle) and $\sim 25\%$ pairs have
-$|\mu|<0.95$ ($18$ degrees angle).
+have $|\mu|>0.8$ ($<36$ degrees angle) and $\sim 25\%$ pairs have
+$|\mu|>0.95$ ($<18$ degrees angle). Similar to the previous case of
+the $\hat{n}$ vector, the increasing strenght of the
+$\hat{r}$ alignment cannot be explained by a selection on mass.
 
-Considering that the 2$\sigma$ and 3$\sigma$ samples move primarely
-along the radial direction, we can say that the motion of the LG
-halos is mostly done along the $\hat{e}_3$ vectors, consistent with
-recent results that report a strong alignment of halo's peculiar
-velocities along that direction \citep{ForeroRomero2014}.
+Considering that the 2$\sigma$ and 3$\sigma$ samples correspond to
+pairs moving along the radial direction, we can say that the
+motion of the LG halos is mostly done along the $\hat{e}_3$
+vectors. This is consistent with recent results that report a strong
+alignment of halo's peculiar velocities along that direction
+\citep{ForeroRomero2014}.
 
@@
 ($|\mu|=0.24$) for MW and M31 respectively
-\citep{2012ApJ...753....9V}. Consistent with our results of no particular
-alignement.
+\citep{2012ApJ...753....9V}. 
+Consistent with our results of no strong alignement.
 
@@
 have shown that the local overdensity is the dominant web property
-that define the abundance and properties of halos. Quantities derived
-from the tidal tensor play a secondary role.
+that define the abundance and properties of halos. Other quantities
+derived from the tidal tensor play a secondary role defining
+properties such as its formation history.
 
-Therefore, in our case, the fact that the preferred LG total mass is
-around $1-4\times 12^{12}$\Msun implies that the preferred environment
-are filaments and sheets with an overdensity close to the average
-value, with values for the ellipticity and prolateness also correlated
-with the overdensity.
+In our case, the fact that the preferred LG total mass is around
+$1-4\times 12^{12}$\Msun implies that the preferred environment are
+filaments and sheets with an overdensity close to the average
+value. 
+Correspondignly, the values for the ellipticity and prolateness are
+also well defined for the LG pairs given its correlation with the
+total mass.
 
-However, there are alignment signals with the cosmic web that are not
-mass dependent and seem to be stronger for different LG samples. There
-is a clear anti-alignment between the third eigenvector and the
-orbital angular momentum vector, meaning that this vector is
-perpendicular to filaments and the sheets, depending on the
-particular web environment. We also found that the vector joining the
-LG halos are aligned with the third eigenvector; i.e. the pair is
-aligned with the filaments and lies on the sheets.
+We conclude that the typical LG environment and its characteristics is
+a robust results depending mostly on the LG total mass.
+
+However, the alignments with the cosmic web that are not
+mass dependent and seem to be stronger once the kinematic constraints
+are imposed on the GS pairs. There is a clear anti-alignment between
+the third eigenvector and the orbital angular momentum vector, meaning
+that this vector is perpendicular to filaments and the sheets,  We
+also found that the vector joining the LG halos are aligned with the
+third eigenvector. This means that he pair is aligned with the filaments and
+lies on the sheets and its motion is done along these directions.
 
@@
 
+These alignments for the LG pairs could be in contradiction with
+recent findings \citep{2014MNRAS.443.1274L} that report a universal
+trend where the eigenvector $\hat{e}_{3}$ marks the infall direction
+for substructures. For the Milky Way its satellites are located at
+high galactic latitudes, almost perpendicular to the vector pointing towards
+the Andromeda Galaxy, which is the direction that we find aligned with
+$\hat{e}_3$.
+
+If the alignment we find in this paper holds, this would imply that
+infall in the case of the Milky Way is perpendicular to $\hat{e}_3$,
+in contradiction to the universal principle of
+\citep{2014MNRAS.443.1274L}. If the universal accretion alignment
+holds, that would imply that that the Andromeda galaxy is located
+perpendicular to $\hat{e}_3$, in contradiction with the strong
+alignment found in this paper. It would be desirable to have a
+measurement of the cosmic web in the Local Universe to disentangle
+this potential contradiction between different alignments and
+understading the detailed properties of the LG in an explicit
+cosmological context.
+
 \section*{Acknowledgements}
-REG was supported by Proyecto Financiamiento Basal PFB-06 'Centro de Astronomia y Tecnologias Afines' and Proyecto Comit\'e Mixto ESO 3312-013-82.
-The Geryon cluster at the Centro de Astro-Ingenieria UC was extensively used for the calculations performed in this paper.
-The Anillo ACT-86, FONDEQUIP AIC-57, and QUIMAL 130008 provided funding for several improvements to the Geryon cluster.
+JEFR was supported by a FAPA grant by Vicerrector\'ia de
+Investigaciones at Universidad de los Andes in Bogot\'a, Colombia.
+REG was supported by Proyecto Financiamiento Basal PFB-06 'Centro de
+Astronomia y Tecnologias Afines' and Proyecto Comit\'e Mixto ESO
+3312-013-82. 
+The Geryon cluster at the Centro de Astro-Ingenieria UC was
+extensively used for the calculations performed in this paper. The
+Anillo ACT-86, FONDEQUIP AIC-57, and QUIMAL 130008 provided funding
+for several improvements to the Geryon cluster.
 

### 2014-08-13 paper/main.tex
typos, comentarios andrey y nelson

@@
 \begin{abstract}
-We explore the characteristics of the Local Group (LG)
-location in the cosmic web using a cosmological simulation in the
+We explore the characteristics of the
+cosmic web around Local Group(LG) like pairs  using a cosmological simulation in the
 $\Lambda$CDM cosmology.  
@@
 on scales of $\sim 2$ Mpc as a peak, sheet, filament or void.  
-The LG is represented by two samples of halo
+The sample of LG counterparts is represented by two samples of halo
 pairs. 
 The first is a general sample composed by pairs with
-similar masses and isolation criteria as observed in the LG.  
-The second is a subset with additional kinematic constaints also
-constrained by observations. 
+similar masses and isolation criteria as observed for the LG.  
+The second is a subset with additional observed kinematic constaints 
+such as relative pair velocity and separation. 
 We find that the pairs in the LG sample with all constraints are: (i)
-preferentially   located in filaments and sheets, (ii) located in in a
+Preferentially   located in filaments and sheets, (ii) Located in in a
 narrow range of local overdensity $0<\delta<2$, web ellipticity $0.1<e<1.0$ and
-prolateness $-0.4<p<0.4$.  (iii) strongly aligned with the cosmic web,
+prolateness $-0.4<p<0.4$.  (iii) Strongly aligned with the cosmic web,
 in particular for pairs in filaments/sheets the pair orbital angular
@@
 The spatial and kinematic configuration of the Local Group
-(LG) galaxies is rare to find in the local Universe and in cosmological
+(LG) galaxies is very uncommon in the local Universe and in cosmological
 simulations. 
-The LG is dominated by the two big spirals MW and M31, the next
+The LG is dominated by two big spirals: MW and M31, the next
 most-luminous galaxy is M33 which is $\sim 10$ times less massive than
-M31, followed by several less luminous dwarf galaxies, up to a
+M31, followed by several dozen less luminous dwarf galaxies, up to a
 distance of $\sim 3$\mpc.   
 The velocity vector of M31, with a low
-tangential velocity is consistent to a head-on collision orbit toward
+tangential velocity is consistent with a head-on collision orbit toward
 the MW
@@
 
-Another feature of the Local group is the relatively low velocity
+Another feature of the Local Group is the relatively low velocity
 dispersion of nearby galaxies up to $\sim 8$ Mpc \citep[][and
@@
 
-This combination of features make LG analogues rare to
-find. 
+This combination of features makes LG analogues uncommon. 
 Using numerical simulatons \citet{lganalogues} found less than
@@
 simulations finding the typical quantities characterizing the orbital
-parameters of the LG are rare among typical pairs, but not enough to
+parameters of the LG are rare among typical pairs, but not sufficiently rare to
 challenge the \lcdm model.  
-Another definition of LG analogues is made
-by \citet{2008MNRAS.384.1459L}, but despite differences ocurr in the
-definitions and resulting fraction of LG analogues, all are in
-agreement with a low frequency of these pairs.
+Another set of criteria for LG analogues was used
+by \citet{2008MNRAS.384.1459L}, but despite differences in the
+definitions and resulting fraction of LG analogues, results are in
+agreement with a low pairs frequency aswell.
 
 To better understand the properties of the LG and how this uncommon
-pair configuration fit in the cosmological context, an immediate
-question arise. 
-What else can we say of the LG at larger scales?
+pair configuration can be explained in the cosmological context, 
+an immediate question arises: 
+What else can we say of the environment of the LG on larger scales?
 
@@
 Maffei group, NGC $6744$, NGC $5128$, M$101$, M$81$, NGC$1023$, Cen A
-group. 
+group \citep{2013AJ....146...69C}.
 At this scale, there is no evident alignment of the MW-M31 orbital
-plane with the local filament or the Virgo-Fornax direction. However,
+plane with any local filament or the Virgo-Fornax direction. However,
 if we look in a smaller volume below scales of $\sim 6$ \mpc, there is
-a clear alignment of the MW-M31 orbit with a local plane as shown by
-Figure $3$ in \citet{2013AJ....146...69C}.
+a clear alignment of the MW-M31 orbit with a local plane of galaxies
+as shown by Figure $3$ in \citet{2013AJ....146...69C}.
 
@@
 
-This tensor is real and symmetric, which means that can be
+This tensor is real and symmetric, which means that it can be
 diagonalized. 
-We note its eigenvalues as $\lambda_1\geq \lambda_2\geq
+We denote its eigenvalues as $\lambda_1\geq \lambda_2\geq
 \lambda_3$ and their corresponding eigenvectors $\hat{e}_1$,
@@
 to compute the Hessian at every point in the grid. 
-In our case we have used a grid size on and a gaussian smoothing with
+In our case we have used a grid size and a gaussian smoothing with
 two times larger as the typical separation between the two halos in the Local Group. 
@@
 To this end we characterize each LG pair by two vectors. 
-The first is $\hat{n}$, the vector marking the axis along the orbital angular
+The first is $\hat{n}$, the axis along the orbital angular
 momentum of the pair, normal to its orbital plane; the second is
@@
 
-The LG analogues or General Sample (GS) in this paper are pairs selected in
+The LG analogues or the General Sample (GS) in this paper are pairs selected in
 relative isolation, and in a wide range of masses from  $M_{200c}=5
 \times 10^{11}$ \msun $ $ to $ 5 \times 10^{13}$ \msun.  
-Isolation criteria includes no halos more masive than each member in
-the pair closer than $1.3$\mpc, and with no massive neighbors within $5$\mpc.
-In addition we require that pairs have no Virgo-like neighbor halo
+Isolation criteria include pair members closer than $1.3$\mpc,
+ and with no massive neighbors within $5$\mpc.
+In addition, we require that pairs have no Virgo-like neighbor halo
 with mass $M_{200c}>1.5 \times 10^{14}\ \rm M_{\odot}$ within $12$
@@
 The number of pairs in each sample is $46$ and $120$ respectively,
-notice we have less pairs than in \citet{lganalogues} results, since
+notice we have less pairs than in \citet{lganalogues}, since
 we removed pairs which are too close at $z=0$, i.e. their virial radii
-overlaps, also we removed a couple pairs that merged or change their
+overlap, also we removed a couple of pairs that merged or change their
 mass more than $20\%$ at present time since they were detected at
@@
   \includegraphics[width=0.50\textwidth]{fig1.pdf}
-\caption{Mass distribution of pairs in the different environments
+\caption{Mass distribution of pairs in different environments
 for the general sample.
-The shaded regions show the mass ranges of $2\sigma$ and $3\sigma$
+The shaded regions show the $68\%$ confidence interval of the mass ranges for $2\sigma$ and $3\sigma$
 samples.  
@@
 The first result we explore is the kind of environment occupied by
-our LGs. 
-We find that the LGs in the GS are located across all different
+our LGs, and use as reference sample the GS where pairs are much more
+relaxed in mass and kinematic constraints.
+We find that the pairs in the GS are located across all different
 evironment without any strong preferences; $1/3$  are located in
@@
 different. 
-By large the LGs in these samples are located in filaments and sheets. 
+By and large the LGs in these samples are located in filaments and sheets. 
 In both samples, $\sim 50\%$ of the pairs can be found in filaments
@@
 
-We now characterize the preferred place of the LG samples in terms of the
+We now characterize the preferred place of the pair samples in terms of the
 web overdensity, ellipticiy and anisotropy as defined in Section
@@
 
-Middle and right panels show web ellipciticy and absolute prolateness
+Middle and right panels show web ellipticity and absolute prolateness
 dependence on mass. 
 Again we notice that within the $2\sigma$ and $3\sigma$ mass range,
-the average ellipciticy and prolateness does not differ significantly
+the average ellipticity and prolateness does not differ significantly
 from the GS expectation.
@@
 \citep{ForeroRomero2014} web finding techniques as ours.
-In particular these trends hold for pairs in filaments and walls.
+In particular, these trends hold for pairs in filaments and walls.
 If we consider only pairs in filaments, we have that the pair orbital
@@
 
-Can the increase of the alignment strenght in the different samples be
-explained as a consequence of different mass dependencies as the
-results in the previous section? No. 
+Can the increase of the alignment strength in the different samples be
+explained as a consequence of different mass dependencies as in the
+results in the previous section? The answer is no. 
 In Figure \ref{fig:median_alignment_n} we show the median of
@@
 \citep{2012ApJ...753....9V}. 
-Consistent with our results of no strong alignement.
+This is consistent with our results of no strong alignement.
 
@@
 The mass range of the LG pairs is tightly correlated with the
-properties of the web where they reside as shown in Table
+properties of the web in which they reside, as shown in Table
 \ref{table:web_type} and Figure \ref{fig:median_fraction}. Recent
 analytical \citep{Alonso2014} and numerical studies \citep{Metuki2014}
-have shown that the local overdensity is the dominant web property
+have shown that the local overdensity is the dominant web parameter
 that define the abundance and properties of halos. Other quantities
@@
 In our case, the fact that the preferred LG total mass is around
-$1-4\times 12^{12}$\Msun implies that the preferred environment are
+$1-4\times 10^{12}$\Msun $\,$implies that the preferred environment are
 filaments and sheets with an overdensity close to the average
@@
 the scope of the work presented here.
+However, such alignments can be traced in observations by looking for 
+similar pairs samples (or even a more unconstrained pair sample) in galaxy surveys and study the angle between
+pair axis and surrounding filament computed using a filament finder, 
+such as codes presented by \citet{2010MNRAS.407.1449G,2011MNRAS.414..350S}.
 
@@
 for several improvements to the Geryon cluster. 
-
+The authors would like to thank Andrey Kravtsov and Nelson Padilla
+for their useful comments.
 \bibliographystyle{apj}

### 2014-08-13 paper/main.tex
nuevas referencias, grandes cambios en la discusion

@@
 
-\title{The Expected Place of the Local Group in the Cosmic Web}
+\title{The Local Group in the Cosmic Web}
 \author{J. E. Forero-Romero$^1$ and R. Gonz\'alez$^{2,3}$}
@@
 the region is classified as peak, filament, sheet or void,
-respectively.
+respectively.  Because this tensor is also known as the tidal tensor
+we refer to it as the Tweb algorithm.
 
@@
 The algorithm to compute the potential is grid based. 
-First we interpolate the density into a cubic grid with a
-Cloud-In-Cell (CIC) scheme and smooth it with a gaussian kernel. 
+First we interpolate the mass into a cubic grid with a
+Cloud-In-Cell (CIC) scheme and smooth it with a gaussian kernel in order to reduce the grid influence in the computations that follow. 
 Then we obtain the gravitational potential using FFT methods and use finite differences
@@
 having a similar mass range than the RS reproduces similar environment
-fractions.
+fractions. The correlation betwen halo mass and their environment is a
+well known result \citep{1998ApJ...500...14L}.
 
@@
 properties of the web in which they reside, as shown in Table
-\ref{table:web_type} and Figure \ref{fig:median_fraction}. Recent
-analytical \citep{Alonso2014} and numerical studies \citep{Metuki2014}
-have shown that the local overdensity is the dominant web parameter
-that define the abundance and properties of halos. Other quantities
-derived from the tidal tensor play a secondary role defining
-properties such as its formation history.
+\ref{table:web_type} and Figure \ref{fig:median_fraction}. This
+confirms that the local overdensity, the trace of the tidal tensor,
+is the dominant web parameter that define the abundance and properties
+of halos 
+\citep{1998ApJ...500...14L,1999MNRAS.302..111L,2004MNRAS.350.1385S,2009MNRAS.394.1825F,
+  Alonso2014}. Other
+quantities derived from the tidal tensor play a secondary role
+defining properties such as its formation history.
 
@@
 value. 
-Correspondignly, the values for the ellipticity and prolateness are
+Correspondingly, the values for the ellipticity and prolateness are
 also well defined for the LG pairs given its correlation with the
@@
 
-However, the alignments with the cosmic web that are not
-mass dependent and seem to be stronger once the kinematic constraints
+However, the alignments with the cosmic web are 
+mass-independent and seem to be stronger once the kinematic constraints
 are imposed on the GS pairs. There is a clear anti-alignment between
@@
 the scope of the work presented here.
-However, such alignments can be traced in observations by looking for 
-similar pairs samples (or even a more unconstrained pair sample) in galaxy surveys and study the angle between
-pair axis and surrounding filament computed using a filament finder, 
-such as codes presented by \citet{2010MNRAS.407.1449G,2011MNRAS.414..350S}.
 
 These alignments for the LG pairs could be in contradiction with
-recent findings \citep{2014MNRAS.443.1274L} that report a universal
-trend where the eigenvector $\hat{e}_{3}$ marks the infall direction
-for substructures. For the Milky Way its satellites are located at
-high galactic latitudes, almost perpendicular to the vector pointing towards
-the Andromeda Galaxy, which is the direction that we find aligned with
+findings
+\citep{2005ApJ...629..219Z,2008MNRAS.390.1133B,2014MNRAS.443.1274L}
+that report a universal trend where the eigenvector $\hat{e}_{3}$
+(i.e. the filament direction) marks the infall direction for
+substructures. The Milky Way satellites are located at high
+galactic latitudes, almost perpendicular to the vector pointing
+towards the Andromeda Galaxy, which is the direction that we find aligned with
 $\hat{e}_3$.
@@
 infall in the case of the Milky Way is perpendicular to $\hat{e}_3$,
-in contradiction to the universal principle of
-\citep{2014MNRAS.443.1274L}. If the universal accretion alignment
-holds, that would imply that that the Andromeda galaxy is located
-perpendicular to $\hat{e}_3$, in contradiction with the strong
-alignment found in this paper. It would be desirable to have a
-measurement of the cosmic web in the Local Universe to disentangle
-this potential contradiction between different alignments and
-understading the detailed properties of the LG in an explicit
-cosmological context.
+in contradiction to the accretion along filaments. If the universal accretion
+along filaments holds, that would imply that that the Andromeda
+galaxy is located perpendicular to $\hat{e}_3$, in contradiction with the strong
+alignment found in this paper.
+
+This apparent contradition can be solved if one considers that the
+subhalo infall properties depend on the environment at {\it the
+  merger time}, while the alignments for yet unvirialized pairs such as the LG
+depend on the current state of the cosmic web. This also explain the absence
+of a strong alignment with halo spin, because it reflects past
+configurations of the web, not the current one. From this perspective,
+a joint consideration of the alignments between the dominant
+halos in the LG and their satellites, which also feature strong
+signals \citep{2005A&A...431..517K,2013ApJ...766..120C}, should
+inform us about the structural evolution of the cosmic web.
+
+Our results also raise the need to observationally constrain
+the alignments of LG pairs with their cosmic web environment. To this end
+one could use mass reconstructions from large surveys
+\citep{2009MNRAS.394..398W,2011MNRAS.417.1303M,2014arXiv1407.3451W,2014arXiv1406.1004N}
+or filament finders \citep{2010MNRAS.407.1449G,2011MNRAS.414..350S}
+to select a LG sample to quantify the alignments with the filamentary
+structure. 
+This allows not only a direct quantification of how common are the LG
+aligments but also provides a new test of $\Lambda$CDM.
 
@@
 The authors would like to thank Andrey Kravtsov and Nelson Padilla
-for their useful comments.
+for their useful comments; and Yehuda Hoffman for insightful
+conversations on the subject of the Local Group and the Cosmic Web. 
 \bibliographystyle{apj}

### 2014-08-13 paper/main.tex
eccentricity

@@
 
+We explored the main differences between the GS and RS samples which can be
+producing this alignment strength feature, and we have that RS samples contraint
+the tangential velocity, then pair orbits are more eccentric as we tighten pair
+constraints, and for GS sample there is no tangential velocity constraint at all.
+Therefore, to study any relation between orbit eccentricity and alignment, we 
+computed for each halo pair in all samples, an approximate orbit 
+eccentricity assuming a two body orbit with masses set as the virial 
+masses and initial conditions given by current velocity vector and separation.
+We found that eccentricity is not responsible for this alignement feature by
+selecting a subsample of GS having the same eccentricity than 
+2$\sigma$-3$\sigma$ samples, and we found no increase in the alignment of 
+this subsample with GS.
+
 {\bf Radial Vector}.  Figure \ref{fig:alignment_r} presents the

### 2014-08-13 paper/main.tex
punto 2 andrey + revision

--- 2014-08-13 paper/main.tex
@@
 
+In the GS we already see an anti-alignment signature with the third eigenvector,
+lower than for RS samples but still significant, this is an expected result,
+even for random pairs with separations of the same order of the scale-lenght of 
+underlying environment, just because individual pair members are more likely to lie 
+following the density distribution. For instance, in a filamentary density distribution, random 
+pairs are more likely to lie along the filament; and in walls, random pairs are more likely
+to lie in the wall.
+
 Can the increase of the alignment strength in the different samples be
@@
 on the pairs, but not as a result of the narrowing mass selection.
+
+We also explored the main orbit differences between the GS and RS  which could be
+responsible of this alignment strength feature, and we have that RS samples contraint
+the tangential velocity, then pair orbits are more eccentric as we tighten pair
+constraints, and for GS sample there is no tangential velocity constraint at all.
+Therefore, to study any relation between orbit eccentricity and alignment, we 
+computed for each halo pair in all samples, an approximate orbit 
+eccentricity assuming a two body orbit with masses set as the virial 
+masses and initial conditions given by current velocity vector and separation.
+We found that eccentricity is not responsible for this alignement feature by
+selecting a subsample of GS having the same eccentricity than 
+2$\sigma$-3$\sigma$ samples where we found no increase in the alignment when
+compared with the full GS.
 
@@
 These alignments for the LG pairs could be in contradiction with
-findings
+some findings
 \citep{2005ApJ...629..219Z,2008MNRAS.390.1133B,2014MNRAS.443.1274L}
@@
 galactic latitudes, almost perpendicular to the vector pointing
-towards the Andromeda Galaxy, which is the direction that we find aligned with
+towards the Andromeda Galaxy, which is the direction that we found aligned with
 $\hat{e}_3$.
 
-If the alignment we find in this paper holds, this would imply that
+If the alignment we found in this paper holds, this would imply that
 infall in the case of the Milky Way is perpendicular to $\hat{e}_3$,
@@
 
-Our results also raise the need to observationally constrain
+Our results also raise the need to observationally constraint
 the alignments of LG pairs with their cosmic web environment. To this end

### 2014-08-13 paper/main.tex
typos corrected

@@
 similar masses and isolation criteria as observed for the LG.  
-The second is a subset with additional observed kinematic constaints 
+The second is a subset with additional observed kinematic constraints 
 such as relative pair velocity and separation. 
@@
 Applied to the observed LG, there is a potential conflict between
-these alignments and recent claims of an universal subhalo accretion
-direction. 
+these alignments and the evidence for satellite accretion along
+filaments. 
 This highlights the relevance of achieving a precise characterization
-of the place of the LG in the cosmic web in a the cosmological context
+of the place of the LG in the cosmic web in the cosmological context
 provided by $\Lambda$CDM.
@@
 This combination of features makes LG analogues uncommon. 
-Using numerical simulatons \citet{lganalogues} found less than
+Using numerical simulations \citet{lganalogues} found less than
 $2\%$ MW-sized halos reside in a pair similar to MW-M31 and in a
@@
 definitions and resulting fraction of LG analogues, results are in
-agreement with a low pairs frequency aswell.
+agreement with a low pairs frequency as well.
 
@@
 
-Observationally, the LG is located in a difuse and
-warped filament/wall conecting Virgo Cluster with Fornax Cluster, some
+Observationally, the LG is located in a diffuse and
+warped filament/wall connecting Virgo Cluster with Fornax Cluster, some
 nearby galaxies and groups members of this large structure are the
@@
 We can then ask, to what extent is this an expected configuration in
-$\Lambda$CDM? In particular, which are the typical/prefered locations
+$\Lambda$CDM? In particular, which are the typical/preferred locations
 of these systems within the Cosmic Web?
@@
 where $r_{i}$, $i=1,2,3$ refers to the three spatial comoving
-coordiates and $\phi$ is the gravitational potential renormalized to
+coordinates and $\phi$ is the gravitational potential renormalized to
 follow the Poisson equation $\nabla^2\phi=\delta$ where
@@
 This is only relevant to the classification of the simulation into web
-elements. Other results are completeley independent of this
+elements. Other results are completely independent of this
 choice. Nevertheless we have checked that the main conclusions of this
@@
 First we interpolate the mass into a cubic grid with a
-Cloud-In-Cell (CIC) scheme and smooth it with a gaussian kernel in order to reduce the grid influence in the computations that follow. 
+Cloud-In-Cell (CIC) scheme and smooth it with a Gaussian kernel in order to reduce the grid influence in the computations that follow. 
 Then we obtain the gravitational potential using FFT methods and use finite differences
 to compute the Hessian at every point in the grid. 
-In our case we have used a grid size and a gaussian smoothing with
+In our case we have used a grid size and a Gaussian smoothing with
 two times larger as the typical separation between the two halos in the Local Group. 
@@
 corresponding to a $256^3$ grid in the Bolshoi volume. 
-The scale for the gaussian smoothing uses the same value.
+The scale for the Gaussian smoothing uses the same value.
 
@@
 related to the alignment of the radial velocities to the web.
-We quantify the alignment using the absolute value of the cosinus of
+We quantify the alignment using the absolute value of the cosine of
 the angle between the two vectors of interest $\mu=|\hat{e}_i \cdot
@@
 additional constraints. 
-A sample named $2\sigma$, correspondig to LG analogues constrained by
+A sample named $2\sigma$, corresponding to LG analogues constrained by
 two times the observational errors in the orbital values (radial
@@
 of the three samples presented in Section \ref{sec:lg_analogues}. 
-In parethesis the same number as a percentage of the total population.
+In parenthesis the same number as a percentage of the total population.
 The last line in the table corresponds to the general sample with an
@@
   web ellipticity (middle) and web absolute value prolateness (right) at the
-  pair location. 
+  pair location. The shaded contours indicate the $68\%$ confidence region. 
 \label{fig:median_overdensity}}
@@
   eigenvectors.  The lines show the trends for the general sample.
+The error bars in the 2$\sigma$ and 3$\sigma$ points
+  correspond to jackknife estimates. 
 \label{fig:median_alignment_n}}
@@
 
-\subsection{The prefered environment for LGs}
+\subsection{The preferred environment for LGs}
 
@@
 evironment without any strong preferences; $1/3$  are located in
-sheets, $1/4$ in peaks, $1/4$ in filaments and the remaning $1/6$ in
+sheets, $1/4$ in peaks, $1/4$ in filaments and the remaining $1/6$ in
 voids.
@@
 In \citet{lganalogues} the mass range covered by $2\sigma$ and $3\sigma$ 
-amples is very narrow and it is used to constraint the LG mass.
+samples is very narrow and it is used to constraint the LG mass.
 We show in Table \ref{table:web_type} that a subset of the GS
 having a similar mass range than the RS reproduces similar environment
-fractions. The correlation betwen halo mass and their environment is a
+fractions. The correlation between halo mass and their environment is a
 well known result \citep{1998ApJ...500...14L}.
@@
 samples.   
-In thre three cases it is evident that the range of values for the
+In the three cases it is evident that the range of values for the
 $2\sigma$ and $3\sigma$ samples are completely expected from the mass
@@
 
-\subsection{Alignments withthe cosmic web}
+\subsection{Alignments with the cosmic web}
 
@@
 With respect to the second eigenvector the distribution is consistent
-with no aligment. 
+with no alignment. 
 While for the first eigenvector there is a strong alignment, an expected
@@
 keeping in mind that they are orthonormal.
-Second, the alignment strenght changes for the different samples. 
-For the anti-alignment with $\hat{e}_3$ the signal strenghtens as we
+Second, the alignment strength changes for the different samples. 
+For the anti-alignment with $\hat{e}_3$ the signal strengthens as we
 move from the GS to the 3$\sigma$ into the 2$\sigma$ sample.
@@
 lower than for RS samples but still significant, this is an expected result,
-even for random pairs with separations of the same order of the scale-lenght of 
+even for random pairs with separations of the same order of the scale-length of 
 underlying environment, just because individual pair members are more likely to lie 
@@
 We also explored the main orbit differences between the GS and RS  which could be
-responsible of this alignment strength feature, and we have that RS samples contraint
+responsible of this alignment strength feature, and we have that RS samples constraints
 the tangential velocity, then pair orbits are more eccentric as we tighten pair
@@
 masses and initial conditions given by current velocity vector and separation.
-We found that eccentricity is not responsible for this alignement feature by
+We found that eccentricity is not responsible for this alignment feature by
 selecting a subsample of GS having the same eccentricity than 
@@
 $|\mu|>0.95$ ($<18$ degrees angle). Similar to the previous case of
-the $\hat{n}$ vector, the increasing strenght of the
+the $\hat{n}$ vector, the increasing strength of the
 $\hat{r}$ alignment cannot be explained by a selection on mass.
@@
 \citep{2012ApJ...753....9V}. 
-This is consistent with our results of no strong alignement.
+This is consistent with our results of no strong alignment.
 
@@
 
-This apparent contradition can be solved if one considers that the
+This apparent contradiction can be solved if one considers that the
 subhalo infall properties depend on the environment at {\it the
@@
 signals \citep{2005A&A...431..517K,2013ApJ...766..120C}, should
-inform us about the structural evolution of the cosmic web.
+inform us about the structural evolution of the cosmic web around the
+LG.
 
@@
 This allows not only a direct quantification of how common are the LG
-aligments but also provides a new test of $\Lambda$CDM.
+alignments but also provides a new test of $\Lambda$CDM.
 

### 2014-08-13 paper/main.tex
main includes the bbl file

@@
 \begin{document}
+ %@arxiver{fig1.pdf,fig3c.pdf,fig4c.pdf,fig5.pdf}
 
@@
 \bibliographystyle{apj}
-\bibliography{references}
+%\bibliography{references} 
+\begin{thebibliography}{38}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Alonso} {et~al.}(2014){Alonso}, {Eardley}, \&
+  {Peacock}}]{Alonso2014}
+{Alonso}, D., {Eardley}, E., \& {Peacock}, J.~A. 2014, ArXiv e-prints
+
+\bibitem[{{Aragon-Calvo} {et~al.}(2011){Aragon-Calvo}, {Silk}, \&
+  {Szalay}}]{2011MNRAS.415L..16A}
+{Aragon-Calvo}, M.~A., {Silk}, J., \& {Szalay}, A.~S. 2011, \mnras, 415, L16
+
+\bibitem[{{Bailin} {et~al.}(2008){Bailin}, {Power}, {Norberg}, {Zaritsky}, \&
+  {Gibson}}]{2008MNRAS.390.1133B}
+{Bailin}, J., {Power}, C., {Norberg}, P., {Zaritsky}, D., \& {Gibson}, B.~K.
+  2008, \mnras, 390, 1133
+
+\bibitem[{{Conn} {et~al.}(2013){Conn}, {Lewis}, {Ibata}, {Parker}, {Zucker},
+  {McConnachie}, {Martin}, {Valls-Gabaud}, {Tanvir}, {Irwin}, {Ferguson}, \&
+  {Chapman}}]{2013ApJ...766..120C}
+{Conn}, A.~R., {Lewis}, G.~F., {Ibata}, R.~A., {Parker}, Q.~A., {Zucker},
+  D.~B., {McConnachie}, A.~W., {Martin}, N.~F., {Valls-Gabaud}, D., {Tanvir},
+  N., {Irwin}, M.~J., {Ferguson}, A.~M.~N., \& {Chapman}, S.~C. 2013, \apj,
+  766, 120
+
+\bibitem[{{Courtois} {et~al.}(2013){Courtois}, {Pomar{\`e}de}, {Tully},
+  {Hoffman}, \& {Courtois}}]{2013AJ....146...69C}
+{Courtois}, H.~M., {Pomar{\`e}de}, D., {Tully}, R.~B., {Hoffman}, Y., \&
+  {Courtois}, D. 2013, \aj, 146, 69
+
+\bibitem[{{Cox} \& {Loeb}(2008)}]{2008MNRAS.386..461C}
+{Cox}, T.~J., \& {Loeb}, A. 2008, \mnras, 386, 461
+
+\bibitem[{{Fakhouri} \& {Ma}(2009)}]{2009MNRAS.394.1825F}
+{Fakhouri}, O., \& {Ma}, C.-P. 2009, \mnras, 394, 1825
+
+\bibitem[{{Forero-Romero} {et~al.}(2014){Forero-Romero}, {Contreras}, \&
+  {Padilla}}]{ForeroRomero2014}
+{Forero-Romero}, J.~E., {Contreras}, S., \& {Padilla}, N. 2014, \mnras, 443,
+  1090
+
+\bibitem[{{Forero-Romero} {et~al.}(2013){Forero-Romero}, {Hoffman},
+  {Bustamante}, {Gottl{\"o}ber}, \& {Yepes}}]{2013ApJ...767L...5F}
+{Forero-Romero}, J.~E., {Hoffman}, Y., {Bustamante}, S., {Gottl{\"o}ber}, S.,
+  \& {Yepes}, G. 2013, \apjl, 767, L5
+
+\bibitem[{{Forero-Romero} {et~al.}(2009){Forero-Romero}, {Hoffman},
+  {Gottl{\"o}ber}, {Klypin}, \& {Yepes}}]{Tweb}
+{Forero-Romero}, J.~E., {Hoffman}, Y., {Gottl{\"o}ber}, S., {Klypin}, A., \&
+  {Yepes}, G. 2009, \mnras, 396, 1815
+
+\bibitem[{{Forero-Romero} {et~al.}(2011){Forero-Romero}, {Hoffman}, {Yepes},
+  {Gottl{\"o}ber}, {Piontek}, {Klypin}, \& {Steinmetz}}]{ForeroRomero2011}
+{Forero-Romero}, J.~E., {Hoffman}, Y., {Yepes}, G., {Gottl{\"o}ber}, S.,
+  {Piontek}, R., {Klypin}, A., \& {Steinmetz}, M. 2011, \mnras, 417, 1434
+
+\bibitem[{{Gonz{\'a}lez} {et~al.}(2013){Gonz{\'a}lez}, {Kravtsov}, \&
+  {Gnedin}}]{sat}
+{Gonz{\'a}lez}, R.~E., {Kravtsov}, A.~V., \& {Gnedin}, N.~Y. 2013, \apj, 770,
+  96
+
+\bibitem[{{Gonz{\'a}lez} {et~al.}(2014){Gonz{\'a}lez}, {Kravtsov}, \&
+  {Gnedin}}]{lganalogues}
+---. 2014, ApJ in press, http://arxiv.org/abs/1312.2587
+
+\bibitem[{{Gonz{\'a}lez} \& {Padilla}(2010)}]{2010MNRAS.407.1449G}
+{Gonz{\'a}lez}, R.~E., \& {Padilla}, N.~D. 2010, \mnras, 407, 1449
+
+\bibitem[{{Hinshaw} {et~al.}(2013){Hinshaw}, {Larson}, {Komatsu}, {Spergel},
+  {Bennett}, {Dunkley}, {Nolta}, {Halpern}, {Hill}, {Odegard}, {Page}, {Smith},
+  {Weiland}, {Gold}, {Jarosik}, {Kogut}, {Limon}, {Meyer}, {Tucker}, {Wollack},
+  \& {Wright}}]{hinshaw_etal13}
+{Hinshaw}, G., {Larson}, D., {Komatsu}, E., {Spergel}, D.~N., {Bennett}, C.~L.,
+  {Dunkley}, J., {Nolta}, M.~R., {Halpern}, M., {Hill}, R.~S., {Odegard}, N.,
+  {Page}, L., {Smith}, K.~M., {Weiland}, J.~L., {Gold}, B., {Jarosik}, N.,
+  {Kogut}, A., {Limon}, M., {Meyer}, S.~S., {Tucker}, G.~S., {Wollack}, E., \&
+  {Wright}, E.~L. 2013, \apjs, 208, 19
+
+\bibitem[{{Karachentsev}(2005)}]{2005AJ....129..178K}
+{Karachentsev}, I.~D. 2005, \aj, 129, 178
+
+\bibitem[{{Klypin} {et~al.}(2003){Klypin}, {Hoffman}, {Kravtsov}, \&
+  {Gottl{\"o}ber}}]{2003ApJ...596...19K}
+{Klypin}, A., {Hoffman}, Y., {Kravtsov}, A.~V., \& {Gottl{\"o}ber}, S. 2003,
+  \apj, 596, 19
+
+\bibitem[{{Klypin} \& {Holtzman}(1997)}]{1997astro.ph.12217K}
+{Klypin}, A., \& {Holtzman}, J. 1997, ArXiv Astrophysics e-prints
+
+\bibitem[{{Klypin} {et~al.}(2011){Klypin}, {Trujillo-Gomez}, \&
+  {Primack}}]{2011ApJ...740..102K}
+{Klypin}, A.~A., {Trujillo-Gomez}, S., \& {Primack}, J. 2011, \apj, 740, 102
+
+\bibitem[{{Kroupa} {et~al.}(2005){Kroupa}, {Theis}, \&
+  {Boily}}]{2005A&A...431..517K}
+{Kroupa}, P., {Theis}, C., \& {Boily}, C.~M. 2005, \aap, 431, 517
+
+\bibitem[{{Lee} \& {Shandarin}(1998)}]{1998ApJ...500...14L}
+{Lee}, J., \& {Shandarin}, S.~F. 1998, \apj, 500, 14
+
+\bibitem[{{Lemson} \& {Kauffmann}(1999)}]{1999MNRAS.302..111L}
+{Lemson}, G., \& {Kauffmann}, G. 1999, \mnras, 302, 111
+
+\bibitem[{{Li} \& {White}(2008)}]{2008MNRAS.384.1459L}
+{Li}, Y.-S., \& {White}, S.~D.~M. 2008, \mnras, 384, 1459
+
+\bibitem[{{Libeskind} {et~al.}(2013){Libeskind}, {Hoffman}, {Forero-Romero},
+  {Gottl{\"o}ber}, {Knebe}, {Steinmetz}, \& {Klypin}}]{Libeskind2013}
+{Libeskind}, N.~I., {Hoffman}, Y., {Forero-Romero}, J., {Gottl{\"o}ber}, S.,
+  {Knebe}, A., {Steinmetz}, M., \& {Klypin}, A. 2013, \mnras, 428, 2489
+
+\bibitem[{{Libeskind} {et~al.}(2014){Libeskind}, {Knebe}, {Hoffman}, \&
+  {Gottl{\"o}ber}}]{2014MNRAS.443.1274L}
+{Libeskind}, N.~I., {Knebe}, A., {Hoffman}, Y., \& {Gottl{\"o}ber}, S. 2014,
+  \mnras, 443, 1274
+
+\bibitem[{{Mei} {et~al.}(2007){Mei}, {Blakeslee}, {C{\^o}t{\'e}}, {Tonry},
+  {West}, {Ferrarese}, {Jord{\'a}n}, {Peng}, {Anthony}, \&
+  {Merritt}}]{2007ApJ...655..144M}
+{Mei}, S., {Blakeslee}, J.~P., {C{\^o}t{\'e}}, P., {Tonry}, J.~L., {West},
+  M.~J., {Ferrarese}, L., {Jord{\'a}n}, A., {Peng}, E.~W., {Anthony}, A., \&
+  {Merritt}, D. 2007, \apj, 655, 144
+
+\bibitem[{{Mu{\~n}oz-Cuartas} {et~al.}(2011){Mu{\~n}oz-Cuartas}, {M{\"u}ller},
+  \& {Forero-Romero}}]{2011MNRAS.417.1303M}
+{Mu{\~n}oz-Cuartas}, J.~C., {M{\"u}ller}, V., \& {Forero-Romero}, J.~E. 2011,
+  \mnras, 417, 1303
+
+\bibitem[{{Nuza} {et~al.}(2014){Nuza}, {Kitaura}, {Hess}, {Libeskind}, \&
+  {Mueller}}]{2014arXiv1406.1004N}
+{Nuza}, S.~E., {Kitaura}, F.-S., {Hess}, S., {Libeskind}, N.~I., \& {Mueller},
+  V. 2014, ArXiv e-prints
+
+\bibitem[{{Riebe} {et~al.}(2013){Riebe}, {Partl}, {Enke}, {Forero-Romero},
+  {Gottl{\"o}ber}, {Klypin}, {Lemson}, {Prada}, {Primack}, {Steinmetz}, \&
+  {Turchaninov}}]{Riebe2013}
+{Riebe}, K., {Partl}, A.~M., {Enke}, H., {Forero-Romero}, J., {Gottl{\"o}ber},
+  S., {Klypin}, A., {Lemson}, G., {Prada}, F., {Primack}, J.~R., {Steinmetz},
+  M., \& {Turchaninov}, V. 2013, Astronomische Nachrichten, 334, 691
+
+\bibitem[{{Sandage} \& {Tammann}(1975)}]{1975ApJ...196..313S}
+{Sandage}, A., \& {Tammann}, G.~A. 1975, \apj, 196, 313
+
+\bibitem[{{Sheth} \& {Tormen}(2004)}]{2004MNRAS.350.1385S}
+{Sheth}, R.~K., \& {Tormen}, G. 2004, \mnras, 350, 1385
+
+\bibitem[{{Sohn} {et~al.}(2012){Sohn}, {Anderson}, \& {van der
+  Marel}}]{2012ApJ...753....7S}
+{Sohn}, S.~T., {Anderson}, J., \& {van der Marel}, R.~P. 2012, \apj, 753, 7
+
+\bibitem[{{Sousbie}(2011)}]{2011MNRAS.414..350S}
+{Sousbie}, T. 2011, \mnras, 414, 350
+
+\bibitem[{{van der Marel} {et~al.}(2012{\natexlab{a}}){van der Marel}, {Besla},
+  {Cox}, {Sohn}, \& {Anderson}}]{2012ApJ...753....9V}
+{van der Marel}, R.~P., {Besla}, G., {Cox}, T.~J., {Sohn}, S.~T., \&
+  {Anderson}, J. 2012{\natexlab{a}}, \apj, 753, 9
+
+\bibitem[{{van der Marel} {et~al.}(2012{\natexlab{b}}){van der Marel},
+  {Fardal}, {Besla}, {Beaton}, {Sohn}, {Anderson}, {Brown}, \&
+  {Guhathakurta}}]{2012ApJ...753....8V}
+{van der Marel}, R.~P., {Fardal}, M., {Besla}, G., {Beaton}, R.~L., {Sohn},
+  S.~T., {Anderson}, J., {Brown}, T., \& {Guhathakurta}, P. 2012{\natexlab{b}},
+  \apj, 753, 8
+
+\bibitem[{{Wang} {et~al.}(2009){Wang}, {Mo}, {Jing}, {Guo}, {van den Bosch}, \&
+  {Yang}}]{2009MNRAS.394..398W}
+{Wang}, H., {Mo}, H.~J., {Jing}, Y.~P., {Guo}, Y., {van den Bosch}, F.~C., \&
+  {Yang}, X. 2009, \mnras, 394, 398
+
+\bibitem[{{Wang} {et~al.}(2014){Wang}, {Mo}, {Yang}, {Jing}, \&
+  {Lin}}]{2014arXiv1407.3451W}
+{Wang}, H., {Mo}, H.~J., {Yang}, X., {Jing}, Y.~P., \& {Lin}, W.~P. 2014, ArXiv
+  e-prints
+
+\bibitem[{{Zentner} {et~al.}(2005){Zentner}, {Kravtsov}, {Gnedin}, \&
+  {Klypin}}]{2005ApJ...629..219Z}
+{Zentner}, A.~R., {Kravtsov}, A.~V., {Gnedin}, O.~Y., \& {Klypin}, A.~A. 2005,
+  \apj, 629, 219
+
+\end{thebibliography}
 

### 2014-10-09 paper/main.tex
updated caption in figure 3 and 4
updated captions

@@
   the Tweb. 
+The shaded region shows the expectation for a random
+  distribution without any preferential alignment, it encloses the $5\%$ and $95\%$ percentiles of 5000
+  flat distributions for $\mu$ generated with the  same number of
+  points as the $2\sigma$ sample.  
     \label{fig:alignment_n}}  
@@
   linking the two halos in the pair, $\hat{r}$, and the three
-  eigenvectors in the Tweb.
+  eigenvectors in the Tweb. The shaded region is the same as in
+  Figure \ref{fig:alignment_n}.
     \label{fig:alignment_r}}  
@@
   correspond to jackknife estimates. 
+ The shaded region shows the expectation for a random distribution
+ without any preferential alignment, it encloses the $5\%$ and $95\%$
+ percentiles of 5000  flat distributions for $\mu$ generated with the
+ same number of points as the $2\sigma$ sample.   
 \label{fig:median_alignment_n}}
@@
   halos in the pair.
+  The shaded region shows the expectation for a random
+  distribution without a preferential alignment as it is described in
+  Figure \ref{fig:median_alignment_n}.
     \label{fig:jj_alignment}}  

### 2014-10-14 paper/main.tex
starting to update some references

--- 2014-08-13 paper/main.tex
@@
 \documentclass{emulateapj}
-\submitted{{\it Submitted for publication in ApJL}}
+\submitted{{\it Submitted for publication in ApJ}}
 \usepackage{multirow,color,wrapfig,ulem}
@@
 \email{je.forero@uniandes.edu.co}
+\email{regonzar@astro.puc.cl}
 
@@
 alignment of spin vectors for the $2\sigma$ sample with a median around
-$|\mu|\sim 0.7$ ($45$ degrees) However, we found no significant
-alignment with the orbital angular momentum nor the cosmic web. This
-is also consistent with recent results that show that the spin
+$|\mu|\sim 0.7$ ($45$ degrees) which is barely above the no-alignment expectation marked by the shaded region. Furthermore, we found no significant
+alignment with the pair orbital angular momentum nor the cosmic web. This
+absense of alignment consistent with recent results that show that the spin
 alignment of halos of masses around $10^{12}$\Msun is very weak
@@
 \end{document}
+
+Codis->spin
+http://adsabs.harvard.edu/abs/2012MNRAS.427.3320C
+
+I've just read the pre-print you had on the arXiv today (The Local Group in the Cosmic Web).
+You make some interesting comments about the distribution of the LG galaxies and their satellites, i.e.
+about a joint consideration of the MW-M31 orientation and their satellite systems.
+You might find it interesting that I have been working on this issue a lot lately (see in particular Pawlowski, Kroupa & Jerjen, 2013, MNRAS, 435, 1928 and Pawlowski & McGaugh, 2014, MNRAS, 440, 908).
+In addition to the satellite planes (VPOS around the MW, GPoA around M31), the more-distant dwarf galaxies in the LG are part of coherent and surprisingly symmetric structures, too.
+
+Concerning the idea that the distribution of satellite galaxies is shaped by the accretion of sub-halos along filaments, I'd like to point out that this effect is not strong enough to explain the observed, very narrow and coherent satellite structures (e.g.
+the recent Pawlowski et al.
+2014, MNRAS, 442, 2362, or Pawlowski et al., 2012, MNRAS, 424, 80).
+Thus, the accretion of sub-halos along filaments, as seen in dark matter simulations, is inconsistent with the observed satellite structures.
+A different explanation is required for the existence of the (co-orbiting) satellite planes.
+This might be a reason for the apparent conflict of your results and the filamentary

### 2014-10-14 paper/main.tex
updated Catolica-> Catolica de Chile

@@
   Cra. 1 No. 18A-10, Edificio Ip, Bogot\'a, Colombia\\
-  $^2$ Instituto de Astrof\'{i}sica, Pontificia Universidad Cat\'olica,
+  $^2$ Instituto de Astrof\'{i}sica, Pontificia Universidad Cat\'olica de Chile,
   Av. Vicu\~na Mackenna 4860, Santiago, Chile\\  
-  $^3$ Centro de Astro-Ingenier\'{i}a, Pontificia Universidad Cat\'olica,
+  $^3$ Centro de Astro-Ingenier\'{i}a, Pontificia Universidad Cat\'olica de Chile,
   Av. Vicu\~na Mackenna 4860, Santiago, Chile

### 2014-10-20 paper/main.tex
re-escribiendo la discusion sobre alineacion

@@
 
-These alignments for the LG pairs could be in contradiction with
-some findings
-\citep{2005ApJ...629..219Z,2008MNRAS.390.1133B,2014MNRAS.443.1274L}
-that report a universal trend where the eigenvector $\hat{e}_{3}$
-(i.e. the filament direction) marks the infall direction for
-substructures. The Milky Way satellites are located at high
-galactic latitudes, almost perpendicular to the vector pointing
-towards the Andromeda Galaxy, which is the direction that we found aligned with
-$\hat{e}_3$.
+How can we related these alignments to the observed LG? 
+To evaluate this point we use observational information for the
+satellite distribution around the LG galaxies.  The MW satellites are
+located at high galactic latitudes forming a planar structure that
+forms an angle of $42^{\circ}-52^{\circ}$, $\mu=0.6-0.7$ with the
+vector joining the MW and M31; while the M31 satellites are on a plane
+that lies on the same vector. \citep{Pawloski2013,Shaya2013}.
+
+Most $\Lambda$CDM studies find that sub-structure infall direction is
+done along $\hat{e}_{3}$ (the direction of filaments)
+\citep{2005ApJ...629..219Z,2008MNRAS.390.1133B,2014MNRAS.443.1274L}. The
+alignment
 

### 2014-10-20 paper/referee_reply.tex
referee reply

\documentclass{article}
\title{Reply to the first referee report on the draft {\it The Local Group in the Cosmic Web}}
\author{J.E. Forero-Romero \& R. Gonz\'alez}
\date{\today}
\begin{document}
\maketitle
l

The points raised by the referee are boldfaced. Our reply follows each point.

\section{Major Points}
\begin{itemize}

\item
{\bf One of the main aspects of the paper is the alignment between the three eigenvectors of the tidal tensor and the two vectors defined by Local Group analogues (the normal to their orbital plane and the line connecting the two). Figure 3 and Figure 4 show this (variants are shown in figure 5 \& 6 as well). What these figures lack is an estimation - a quantification - of the statistical significance of the result. This can be easily done by constructing 3xN "sister" samples with the same number of elements as the 2sigma, 3sigma and general samples, uniformly drawn in the interval [0,1] and comparing them. For example in the case of figure 3 \& 4 one could imagine plotting the 2 sigma spread in the cumulative distribution of such random distributions. In Fig 5 some kind of spread indicating the variance in the median computations could be included (along with the medians and spread for a uniform distribution). In Figure 6 the authors could also include an expectation from random distributions.}

We have followed the advice from the referee. Now Figures 3, 4, 5 and 6 include a shadowed region quantifying the expectations from a random distribution. The captions include an explanation on how the numbers were estimated.

Our estimation proceeds as follows. We construct a sample of 3D vectors with the same number of elemets as the 2sigma sample. We use the 2sigma sample to show the upper bound on the uncertainties.

These vectors have a random distributions. This allows us to build the integrated $\mu$ distributions. We repeat the exercise 5000 times to compute the median together with the $5\%$ and $95\%$ percentiles for the quantities of interest. In the case of Figures 3,4 and 6 it corresponds to the fraction of elements with values $<\mu$; in the case of Figure 5 it corresponds to the median value of $\mu$.

\item
{\bf My other significant point is the smoothing scale. The study examines the web on a fixed scale namely ~1.4Mpc. However since the scale is fixed it measures different aspects of the environment for different LG analogues. This is explicitely shown in Fig2 left. A halo of mass 5e13Mdot could have a virial radius of upto 1 or 1.3Mpc. For these haloes the smoothing is basically on the scale of Rvir. Whereas for haloes with masses of 5e11 Mdot the virial radius is probably less than 200kpc and your 1.4Mpc smoothing is equivalent to 7 times the virial radius.  Although I am quite sure that the tidal tensor eigenvectors are stable across these different scales, I'm not quite sure the web classification, web ellipticity or web prolateness are. Perhaps you should convince the reader of this issue.}

We tested the robustness of our results with a smaller smoothing scale (0.7 Mpc, from the $512^3$ grid data available on the Multidark Database. This was already mentioned in the paper.

Concerning a larger smoothing scale we base the robustness on already published results. In Forero-Romero et al. 2009  we presented a through study of the environment as defined by the Tweb in terms of the two free parameters of the model: $\lambda_{th}$ and the smoothing scale. In that work we changed the smothing scale from 0.5 Mpc/h up to 12.5 Mpc/h and quantified the changes in the volume and mass filling fractions (VFF and MFF) for each web environment. We found that for the values of $\lambda_{th}\approx 2$ the VFF and MFF only change on the order of $5\%$. In the thorough paper by Cautun et al. 2014 they also show that the web properties are insensitive to changes of factor of $2$ on the smoothing scale. We have added a short paragraph on this point.

\subsection{Minor Issues}
\begin{itemize}

\item
{\bf The general sample spans a greater range of masses than the x-axis. In Section 3 it is given as 5e11 to 5e13, whereas the x axis in fig 2 goes from 1e12 to 1e13, please explain.}

We have extended the mass range to 13.5 in the plots.

\item{ In the discussion the authors say that "the MW satellites are located at high galactic latitude, almost perpendicular to the direction of M31." I take issue wth the "almost perpendicular" comment. The plane of MW satellites is between 32 and 45 degrees from the direction to M31 depending on how it is defined. This is a small point of contention in the literature because people define it differently given the uncertainties and incompleteness limits that drive the fact that most of these galaxies are found at high galactic latitude.

Using a fairly conservative definition (ie the 11 brightest dwarfs for which we have fairly good completeness limits) Pawlowski et al 2012 and Shaya \& Tully 2014 both find something between 32 and 45 degrees. If the authors want to stick to the "almost perpendicular" statement they will need to justify it by citation and explanation}

\item{
I also want to note that the preferential accretion found by Libeskind et al 2014 shows a signal primarily along e3, but also defined as being away from e1. Indeed the accretion is somewhat planar in the e2-e3 plane. So I wouldn't say there is a contradiction.}

\item{Lastly the discussion and interpretation of results regarding the alignment of the orbital plane with the eigenvectors could do with an engagement of the vibrant debate in the literature regarding how massive haloes have a spin flip with respect the filament or wall they are in compared to less massive haloes (e.g. Aragon-Calvo et al 2007, Codis et al 2012, Trowland et al 2013, Libeskind et al 2013, among others), likely due to major mergers.}

\end{itemize}

\end{document}

### 2014-10-21 paper/main.tex
adding text to the alignment discussion

@@
 
-How can we related these alignments to the observed LG? 
+How can we relate these alignments to the observed LG? 
 To evaluate this point we use observational information for the
@@
 done along $\hat{e}_{3}$ (the direction of filaments)
-\citep{2005ApJ...629..219Z,2008MNRAS.390.1133B,2014MNRAS.443.1274L}. The
-alignment
+\citep{2005ApJ...629..219Z,2008MNRAS.390.1133B} or almost over the plane
+defined by the $\hat{e}_2$ and $\hat{e}_3$ \cite{2014MNRAS.443.1274L}.
 
-If the alignment we found in this paper holds, this would imply that
-infall in the case of the Milky Way is perpendicular to $\hat{e}_3$,
-in contradiction to the accretion along filaments. If the universal accretion
-along filaments holds, that would imply that that the Andromeda
-galaxy is located perpendicular to $\hat{e}_3$, in contradiction with the strong
-alignment found in this paper.
+Taking this three points together (the alignment of MW-M31 along
+$\hat{e}_3$, the observed satellite alignments and the preferential
+infall along $\hat{e}_3$) we have that the M31 plane of satellites is
+completely consistent with the average alignment picture we have
+described. However, the planes defined by the MW satellites should
+also be close to parallel with respect to the vector joining MW and
+M31 and the plane of M31 satellites. Instead, this plane has
+$\mu=0.6-0.7$ with respect to these to directions.
 
@@
 halos in the LG and their satellites, which also feature strong
-signals \citep{2005A&A...431..517K,2013ApJ...766..120C}, should
+signals \citep{2005A&A...431..517,Pawloski2013,Shaya2013}, should
 inform us about the structural evolution of the cosmic web around the
@@
 
-Our results also raise the need to observationally constraint
-the alignments of LG pairs with their cosmic web environment. To this end
-one could use mass reconstructions from large surveys
+Our results also raise the need to observationally constraint the
+alignments of LG pairs with their cosmic web environment. To this end one could use mass reconstructions from large surveys
 \citep{2009MNRAS.394..398W,2011MNRAS.417.1303M,2014arXiv1407.3451W,2014arXiv1406.1004N}

### 2014-10-21 paper/referee_reply.tex
lista la referee reply

@@
 This allows us to build the integrated $\mu$ distributions.
-We repeat the exercise 5000 times to compute the median together with the $5\%$ and $95\%$ percentiles for the quantities of interest.
+We repeat the exercise 10000 times to compute the median together with the $5\%$ and $95\%$ percentiles for the quantities of interest.
 In the case of Figures 3,4 and 6 it corresponds to the fraction of elements with values $<\mu$; in the case of Figure 5 it corresponds to the median value of $\mu$.
@@
 
-We tested the robustness of our results with a smaller smoothing scale (0.7 Mpc, from the $512^3$ grid data available on the Multidark Database. This was already mentioned in the paper.
+We tested the robustness of our results with a smaller smoothing scale (0.7 Mpc, from the $512^3$ grid data available on the Multidark Database. This is mentioned in the paper.
 
@@
 2014 they also show that the web properties are insensitive to changes of factor of $2$ on the smoothing scale.
-We have added a short paragraph on this point.
+
+We have added a short paragraph reminding the reader about these points.
 
@@
 
+We have included the exact values in the Discussion section.
+
 \item{
@@
 
+We have made explicit this point in the Discussion section.
+
 \item{Lastly the discussion and interpretation of results regarding the alignment of the orbital plane with the eigenvectors could do with an engagement of the vibrant debate in the literature regarding how massive haloes have a spin flip with respect the filament or wall they are in compared to less massive haloes (e.g.
 Aragon-Calvo et al 2007, Codis et al 2012, Trowland et al 2013, Libeskind et al 2013, among others), likely due to major mergers.}
+
+We have included a paragraph on this discussion.
 

### 2014-10-21 paper/main.tex
full pass over the manuscript

@@
 In addition, the closest massive galaxy cluster, the Virgo Cluster, is
-$\approx 16.5\ \mpc$ away \citep{2007ApJ...655..144M}.
+$\sim 16.5\ \mpc$ away \citep{2007ApJ...655..144M}.
 
@@
 \citep{hinshaw_etal13}. The simulation followed the evolution of dark
-matter in a $250 \hmpc$ box with spatial resolution of $\approx
-1h^{-1}$~kpc and mass resolution of $m_{\rm p}=1.35\times 10^8\ \rm
+matter in a $250 \hmpc$ box with spatial resolution of $\sim
+1h^{-1}$ kpc and mass resolution of $m_{\rm p}=1.35\times 10^8\ \rm
 M_{\odot}$. Halos are identified with the BDM algorithm
@@
 
+We have
+veryfied that the main trends reported in this paper remain unchanged
+if we use the results from a $512^3$ grid smoothed over scales of
+$s=0.48$\hMpc. Small changes of a factor of $\sim2$ in the smoothing
+scale do not significantly impact the cosmic web as it 
+was shown in \cite{Tweb} from the study of the volume and mass
+filling fractions for different smoothing scales. Other works have
+also shown that broad features the cosmic web, as defined in this
+paper, are robust to factor of $\sim2$ changes on the scale defining the web
+\citep{Cautun2014}.
+
 The data of the BDM halos and the Tweb is publicly available through
@@
 
-To construct a sample of the MW-M31 pairs at $z\approx 0$, we use a
-series of simulation snapshots  at $z<0.1$ (since the last $\approx
-1.3$ Gyr) spaced by $\approx 150-250$ Myr. 
+To construct a sample of the MW-M31 pairs at $z\sim 0$, we use a
+series of simulation snapshots  at $z<0.1$ (since the last $\sim
+1.3$ Gyr) spaced by $\sim 150-250$ Myr. 
 This is done because a particular configuration of MW and M31 is transient and
@@
 
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.50\textwidth]{fig1.pdf}
+\caption{Mass distribution of pairs in different environments
+for the general sample.
+The shaded regions show the $68\%$ confidence interval of the mass ranges for $2\sigma$ and $3\sigma$
+samples.  
+\label{fig:median_fraction}}
+\end{center}
+\end{figure}
+
 \begin{table*}
@@
 \end{table*}
-
-\begin{figure}
-\begin{center}
-  \includegraphics[width=0.50\textwidth]{fig1.pdf}
-\caption{Mass distribution of pairs in different environments
-for the general sample.
-The shaded regions show the $68\%$ confidence interval of the mass ranges for $2\sigma$ and $3\sigma$
-samples.  
-\label{fig:median_fraction}}
-\end{center}
-\end{figure}
 
@@
 
-\begin{figure}
+\begin{figure*}
 \begin{center}
-  \includegraphics[width=0.50\textwidth]{fig5.pdf}
+  \includegraphics[width=0.45\textwidth]{fig5a.pdf}
+  \includegraphics[width=0.45\textwidth]{fig5b.pdf}
 \caption{Mass dependency of the median value for the dot product
-  between the normal vector $\hat{n}$ and each one of the
-  eigenvectors.  The lines show the trends for the general sample.
-The error bars in the 2$\sigma$ and 3$\sigma$ points
+  between the normal/radial vector $\hat{n}$/$\hat{r}$ (left/right)
+  and each one of the  eigenvectors.  The lines show the trends for
+  the general sample. The error bars in the 2$\sigma$ and 3$\sigma$ points
   correspond to jackknife estimates. 
@@
 \end{center}
-\end{figure}
+\end{figure*}
 
@@
 \begin{center}
-  \includegraphics[width=0.50\textwidth]{fig6.pdf}
+  \includegraphics[width=0.45\textwidth]{fig6.pdf}
 \end{center}
@@
 even for random pairs with separations of the same order of the scale-length of 
-underlying environment, just because individual pair members are more likely to lie 
-following the density distribution. For instance, in a filamentary density distribution, random 
-pairs are more likely to lie along the filament; and in walls, random pairs are more likely
-to lie in the wall.
+underlying environment, just because individual pair members are more
+likely to lie  following the density distribution. For instance, in a
+filamentary density distribution, random  pairs are more likely to lie
+along the filament; and in walls, random pairs are more likely to lie
+in the wall.
 
@@
 In Figure \ref{fig:median_alignment_n} we show the median of
-$\mu\equiv\hat{e}_i\cdot\hat{n}$ in different mass bins.
+$\mu\equiv\hat{e}_i\cdot\hat{n}$ and $\mu\equiv \hat{e}_i\cdot\hat{r}$
+in different mass bins. 
 Lines show the median $\mu$-mass relation for the three
 eigenvectors in the GS, dots represent the results for the
-2$\sigma$-3$\sigma$ samples. 
-Around the total mass $1.5-2.0 \times 10^{12}$ \msun in the RS
-samples, the median of $\mu$ decreases as we tighten constraints
-on the pairs, but not as a result of the narrowing mass selection.
+2$\sigma$-3$\sigma$ samples.  Around the total mass $1.5-2.0 \times
+10^{12}$ \msun in the RS samples, the median of $\mu$ clearly from the
+2$\sigma$ and 3$\sigma$ samples clearly differs from the GS results.
+Although in the GS the alignments have slight changes with mass, this
+is not enough to explain the results for the reduced samples.
 
-We also explored the main orbit differences between the GS and RS  which could be
-responsible of this alignment strength feature, and we have that RS samples constraints
-the tangential velocity, then pair orbits are more eccentric as we tighten pair
-constraints, and for GS sample there is no tangential velocity constraint at all.
+We also explored the main orbit differences between the GS and RS
+which could be responsible of this alignment strength feature, and we
+have that RS samples constraints the tangential velocity, then pair
+orbits are more eccentric as we tighten pair constraints, and for GS sample there is no tangential velocity constraint at all.
 Therefore, to study any relation between orbit eccentricity and alignment, we 
@@
 $|\mu|\sim 0.7$ ($45$ degrees) which is barely above the no-alignment expectation marked by the shaded region. Furthermore, we found no significant
-alignment with the pair orbital angular momentum nor the cosmic web. This
-absense of alignment consistent with recent results that show that the spin
-alignment of halos of masses around $10^{12}$\Msun is very weak
-\citep{ForeroRomero2014}.
+alignment with the pair orbital angular momentum nor the cosmic web.
+
+The absence of alignment for the spins is consistent with different studies of
+spin alingnemnt that mark the range $10^{12}$\Msun as either a transition mass
+from alignment into anti-alignment or from no-alignment into alignment
+\citep{Hahn2007,AragonCalvo2007,Zhang2009,Codis2012,Trowland2013,Libeskind2013,ForeroRomero2014}. We refer the reader to Table 2 in \cite{ForeroRomero2014}
+for a review on the different results of spin alignment with the
+cosmic web in cosmological simulations. It seems that this transition
+has to do with the changes on the major merger rate as a dark matter
+halo approaches the $10^{12}$\Msun mass \citep{2009MNRAS.399..762F,Codis2012}.
 
@@
 vector joining the MW and M31; while the M31 satellites are on a plane
-that lies on the same vector. \citep{Pawloski2013,Shaya2013}.
+that lies on the same vector \citep{Pawlowski2013,Shaya2013}.
 
@@
 completely consistent with the average alignment picture we have
-described. However, the planes defined by the MW satellites should
+described. However, the plane defined by the MW satellites should
 also be close to parallel with respect to the vector joining MW and
 M31 and the plane of M31 satellites. Instead, this plane has
-$\mu=0.6-0.7$ with respect to these to directions.
+$\mu=0.6-0.7$ with respect to these directions. The spatial location
+of MW satellites raise a potential contradiction with the average expectations
+from $\Lambda$CDM, a point that has been raised before
+\citep{Pawlowski2012,Pawlowski2014}.
 
@@
 subhalo infall properties depend on the environment at {\it the
-  merger time}, while the alignments for yet unvirialized pairs such as the LG
-depend on the current state of the cosmic web. This also explain the absence
-of a strong alignment with halo spin, because it reflects past
-configurations of the web, not the current one. From this perspective,
-a joint consideration of the alignments between the dominant
-halos in the LG and their satellites, which also feature strong
-signals \citep{2005A&A...431..517,Pawloski2013,Shaya2013}, should
-inform us about the structural evolution of the cosmic web around the
-LG.
+  merger time}, while the alignments for yet unvirialized pairs such
+as the dominant galaxis in the LG depend on the current state of the
+cosmic web. This also explain the absence of a strong alignment with
+halo spin, because it reflects past configurations of the web, not the
+current one. From this perspective, a joint consideration of the
+alignments between the dominant halos in the LG and their satellites,
+which also feature strong signals
+\citep{2005A&A...431..517K,Pawlowski2013,Shaya2013}, should inform us
+about the structural evolution of the cosmic web around the LG.
 
-Our results also raise the need to observationally constraint the
-alignments of LG pairs with their cosmic web environment. To this end one could use mass reconstructions from large surveys
+Our results raise the need to observationally constrain the
+alignments of LG pairs with their cosmic web environment. To this end
+one could use mass reconstructions from large surveys
 \citep{2009MNRAS.394..398W,2011MNRAS.417.1303M,2014arXiv1407.3451W,2014arXiv1406.1004N}
-or filament finders \citep{2010MNRAS.407.1449G,2011MNRAS.414..350S}
-to select a LG sample to quantify the alignments with the filamentary
-structure. 
-This allows not only a direct quantification of how common are the LG
-alignments but also provides a new test of $\Lambda$CDM.
+or filament finders \citep{2010MNRAS.407.1449G,2011MNRAS.414..350S} to
+select a LG sample to quantify the alignments with the surrounding
+filamentary structure. This would allow not only a direct
+quantification of how common are the LG alignments but also provide a
+new test of $\Lambda$CDM.  We thank the referee Noam Libeskind for
+suggestions that helped us to clarify and strenghten the results
+presented in the paper.
 

### 2014-10-21 paper/referee_reply.tex
updated referee reply

@@
 \maketitle
-l
 
@@
 \section{Major Points}
+
 \begin{itemize}
@@
 \item
-{\bf One of the main aspects of the paper is the alignment between the three eigenvectors of the tidal tensor and the two vectors defined by Local Group analogues (the normal to their orbital plane and the line connecting the two).
-Figure 3 and Figure 4 show this (variants are shown in figure 5 \& 6 as well).
-What these figures lack is an estimation - a quantification - of the statistical significance of the result.
-This can be easily done by constructing 3xN "sister" samples with the same number of elements as the 2sigma, 3sigma and general samples, uniformly drawn in the interval [0,1] and comparing them.
-For example in the case of figure 3 \& 4 one could imagine plotting the 2 sigma spread in the cumulative distribution of such random distributions.
-In Fig 5 some kind of spread indicating the variance in the median computations could be included (along with the medians and spread for a uniform distribution).
-In Figure 6 the authors could also include an expectation from random distributions.}
+{\bf One of the main aspects of the paper is the alignment between the
+  three eigenvectors of the tidal tensor and the two vectors defined
+  by Local Group analogues (the normal to their orbital plane and the
+  line connecting the two). Figure 3 and Figure 4 show this (variants
+  are shown in figure 5 \& 6 as well). What these figures lack is an
+  estimation - a quantification - of the statistical significance of
+  the result. This can be easily done by constructing 3xN "sister"
+  samples with the same number of elements as the 2sigma, 3sigma and
+  general samples, uniformly drawn in the interval [0,1] and comparing
+  them. For example in the case of figure 3 \& 4 one could imagine
+  plotting the 2 sigma spread in the cumulative distribution of such
+  random distributions. In Fig 5 some kind of spread indicating the
+  variance in the median computations could be included (along with
+  the medians and spread for a uniform distribution). In Figure 6 the
+  authors could also include an expectation from random
+  distributions.}
 
-We have followed the advice from the referee.
-Now Figures 3, 4, 5 and 6 include a shadowed region quantifying the expectations from a random distribution.
-The captions include an explanation on how the numbers were estimated.
+We have followed the advice from the referee. Now Figures 3, 4, 5 and
+6 include a shadowed region quantifying the expectations from a random
+distribution. The captions include an explanation on how the numbers
+were estimated.
 
-Our estimation proceeds as follows. We construct a sample of 3D vectors with the same number of elemets as the 2sigma sample. We use the 2sigma sample to show the upper bound on the uncertainties.
+Our estimation proceeds as follows. We construct a sample of 3D
+vectors with the same number of elemets as the 2sigma sample. We use
+the 2sigma sample to show the upper bound on the uncertainties.
 
-These vectors have a random distributions.
-This allows us to build the integrated $\mu$ distributions.
-We repeat the exercise 10000 times to compute the median together with the $5\%$ and $95\%$ percentiles for the quantities of interest.
-In the case of Figures 3,4 and 6 it corresponds to the fraction of elements with values $<\mu$; in the case of Figure 5 it corresponds to the median value of $\mu$.
+These vectors have a random distributions. This allows us to build the
+integrated $\mu$ distributions. We repeat the exercise 10000 times to
+compute the median together with the $5\%$ and $95\%$ percentiles for
+the quantities of interest. In the case of Figures 3,4 and 6 it
+corresponds to the fraction of elements with values $<\mu$; in the
+case of Figure 5 it corresponds to the median value of $\mu$.
 
 \item
-{\bf My other significant point is the smoothing scale.
-The study examines the web on a fixed scale namely ~1.4Mpc.
-However since the scale is fixed it measures different aspects of the environment for different LG analogues.
-This is explicitely shown in Fig2 left.
-A halo of mass 5e13Mdot could have a virial radius of upto 1 or 1.3Mpc.
-For these haloes the smoothing is basically on the scale of Rvir.
-Whereas for haloes with masses of 5e11 Mdot the virial radius is probably less than 200kpc and your 1.4Mpc smoothing is equivalent to 7 times the virial radius.
-Although I am quite sure that the tidal tensor eigenvectors are stable across these different scales, I'm not quite sure the web classification, web ellipticity or web prolateness are.
-Perhaps you should convince the reader of this issue.}
+{\bf My other significant point is the smoothing scale. The study
+  examines the web on a fixed scale namely ~1.4Mpc. However since the
+  scale is fixed it measures different aspects of the environment for
+  different LG analogues. This is explicitely shown in Fig2 left. A
+  halo of mass 5e13Mdot could have a virial radius of upto 1 or
+  1.3Mpc. For these haloes the smoothing is basically on the scale of
+  Rvir. Whereas for haloes with masses of 5e11 Mdot the virial radius
+  is probably less than 200kpc and your 1.4Mpc smoothing is equivalent
+  to 7 times the virial radius.  Although I am quite sure that the
+  tidal tensor eigenvectors are stable across these different scales,
+  I'm not quite sure the web classification, web ellipticity or web
+  prolateness are. Perhaps you should convince the reader of this
+  issue.}
 
-We tested the robustness of our results with a smaller smoothing scale (0.7 Mpc, from the $512^3$ grid data available on the Multidark Database. This is mentioned in the paper.
+We tested the robustness of our results with a smaller smoothing scale
+(0.7 Mpc, from the $512^3$ grid data available on the Multidark
+Database. This is mentioned in the paper.
 
-Concerning a larger smoothing scale we base the robustness on already published results.
-In Forero-Romero et al.
-2009  we presented a through study of the environment as defined by the Tweb in terms of the two free parameters of the model: $\lambda_{th}$ and the smoothing scale.
-In that work we changed the smothing scale from 0.5 Mpc/h up to 12.5 Mpc/h and quantified the changes in the volume and mass filling fractions (VFF and MFF) for each web environment.
-We found that for the values of $\lambda_{th}\approx 2$ the VFF and MFF only change on the order of $5\%$.
-In the thorough paper by Cautun et al.
-2014 they also show that the web properties are insensitive to changes of factor of $2$ on the smoothing scale.
+Concerning a larger smoothing scale we base the robustness on already
+published results. In Forero-Romero et al. 2009  we presented a
+through study of the environment as defined by the Tweb in terms of
+the two free parameters of the model: $\lambda_{th}$ and the smoothing
+scale. In that work we changed the smothing scale from 0.5 Mpc/h up to
+12.5 Mpc/h and quantified the changes in the volume and mass filling
+fractions (VFF and MFF) for each web environment. We found that for
+the values of $\lambda_{th}\approx 2$ the VFF and MFF only change on
+the order of $5\%$. In the thorough paper by Cautun et al. 2014 they
+also show that the web properties are insensitive to changes of factor
+of $2$ on the smoothing scale.
 
 We have added a short paragraph reminding the reader about these points. 
+\end{itemize}
 
-\subsection{Minor Issues}
+\section{Minor Issues}
+
 \begin{itemize}
-
 \item
@@
 
-\item{ In the discussion the authors say that "the MW satellites are located at high galactic latitude, almost perpendicular to the direction of M31." I take issue wth the "almost perpendicular" comment.
+\item
+{\bf In the discussion the authors say that "the MW satellites are located at high galactic latitude, almost perpendicular to the direction of M31." I take issue wth the "almost perpendicular" comment.
 The plane of MW satellites is between 32 and 45 degrees from the direction to M31 depending on how it is defined.
 This is a small point of contention in the literature because people define it differently given the uncertainties and incompleteness limits that drive the fact that most of these galaxies are found at high galactic latitude.
-
 Using a fairly conservative definition (ie the 11 brightest dwarfs for which we have fairly good completeness limits) Pawlowski et al 2012 and Shaya \& Tully 2014 both find something between 32 and 45 degrees.
@@
 
-\item{
-I also want to note that the preferential accretion found by Libeskind et al 2014 shows a signal primarily along e3, but also defined as being away from e1.
+\item
+{\bf I also want to note that the preferential accretion found by Libeskind et al 2014 shows a signal primarily along e3, but also defined as being away from e1.
 Indeed the accretion is somewhat planar in the e2-e3 plane.
@@
 
-\item{Lastly the discussion and interpretation of results regarding the alignment of the orbital plane with the eigenvectors could do with an engagement of the vibrant debate in the literature regarding how massive haloes have a spin flip with respect the filament or wall they are in compared to less massive haloes (e.g.
+\item
+{\bf Lastly the discussion and interpretation of results regarding the alignment of the orbital plane with the eigenvectors could do with an engagement of the vibrant debate in the literature regarding how massive haloes have a spin flip with respect the filament or wall they are in compared to less massive haloes (e.g.
 Aragon-Calvo et al 2007, Codis et al 2012, Trowland et al 2013, Libeskind et al 2013, among others), likely due to major mergers.}

### 2014-10-27 paper/main.tex
nueva version

@@
 narrow range of local overdensity $0<\delta<2$, web ellipticity $0.1<e<1.0$ and
-prolateness $-0.4<p<0.4$.  (iii) Strongly aligned with the cosmic web,
-in particular for pairs in filaments/sheets the pair orbital angular
-momentum tends to be perpendicular to the filament direction or the
-sheet plane.
-A stronger alignment is present for the vector linking the two halos,
-which lies along the filament or the sheet plane.  
-We show that the first and second results are expected trends with the LG
-total mass. 
-However, the strong alignments with the cosmic web cannot be explained
-by a simple mass dependency. 
-Additionally, we fail to find a strong correlation of the spin of each
-halo in the pair with the cosmic web.
+prolateness $-0.4<p<0.4$.  (iii) Strongly aligned with the cosmic web.
+The alignments are such that he pair orbital angular momentum tends to
+be perpendicular to the smallest tidal eigenvector, $\hat{e}_3$, which
+lies along the filament direction or the sheet plane.
+A stronger alignment is present for the vector linking the two halos with the vector $\hat{e}_3$.
+Additionally, we fail to find a strong correlation of the spin of each halo in the pair with the cosmic web.
+All these trends are expected to a great extent from the selection on
+the LG total mass on the general sample. 
 Applied to the observed LG, there is a potential conflict between
-these alignments and the evidence for satellite accretion along
-filaments. 
-This highlights the relevance of achieving a precise characterization
-of the place of the LG in the cosmic web in the cosmological context
-provided by $\Lambda$CDM.
+the alignments of the different planes of satellites and the numerical
+evidence for satellite accretion along filaments; the direction
+defined by $\hat{e}_3$. This highlights the relevance of achieving a
+precise characterization of the place of the LG in the cosmic web in
+the cosmological context provided by $\Lambda$CDM.
 
@@
 simulations. 
-The LG is dominated by two big spirals: MW and M31, the next
+The LG is dominated by two big spirals: the Milky Way (MW) and M31, the next
 most-luminous galaxy is M33 which is $\sim 10$ times less massive than
@@
 $\sim 16.5\ \mpc$ away \citep{2007ApJ...655..144M}.
+
+In addition, the LG is located in a diffuse and
+warped filament/wall connecting Virgo Cluster with Fornax Cluster, some
+nearby galaxies and groups members of this large structure are the
+Maffei group, NGC $6744$, NGC $5128$, M$101$, M$81$, NGC$1023$, Cen A
+group \citep{2013AJ....146...69C}.
+At this scale, there is no evident alignment of the MW-M31 orbital
+plane with any local filament or the Virgo-Fornax direction. However,
+if we look in a smaller volume below scales of $\sim 6$ \mpc, there is
+a clear alignment of the MW-M31 orbit with a local plane of galaxies
+as shown by Figure $3$ in \citet{2013AJ....146...69C}. On top of that,
+the satellite galaxies in the MW and M31 present different kinds of
+strong alignments along planes \citep{Pawlowski2013,Shaya2013}, which
+are sometimes considered as unusual in the context of the $\Lambda$
+Cold Dark Matter (CDM) model \citep{Pawlowski2012}.
 
@@
 pair configuration can be explained in the cosmological context, 
-an immediate question arises: 
-What else can we say of the environment of the LG on larger scales?
-
-Observationally, the LG is located in a diffuse and
-warped filament/wall connecting Virgo Cluster with Fornax Cluster, some
-nearby galaxies and groups members of this large structure are the
-Maffei group, NGC $6744$, NGC $5128$, M$101$, M$81$, NGC$1023$, Cen A
-group \citep{2013AJ....146...69C}.
-At this scale, there is no evident alignment of the MW-M31 orbital
-plane with any local filament or the Virgo-Fornax direction. However,
-if we look in a smaller volume below scales of $\sim 6$ \mpc, there is
-a clear alignment of the MW-M31 orbit with a local plane of galaxies
-as shown by Figure $3$ in \citet{2013AJ....146...69C}.
-
-We can then ask, to what extent is this an expected configuration in
-$\Lambda$CDM? In particular, which are the typical/preferred locations
-of these systems within the Cosmic Web?
+some questions arise. What else can we say of the environment of the
+LG on larger scales? To what extent is this an expected configuration
+in $\Lambda$CDM? In particular, which are the typical/preferred locations
+of these systems within the Cosmic Web? Are the preferential
+alignments of satellites a result of the location of the LG in the
+Cosmic Web?
 
 %this paper.
-In this \manuscript we study the large scale environment of LG 
-analogues in the context of $\Lambda$CDM. 
+In this \manuscript we address those questions by studying the large
+scale environment of LG  analogues in the context of \lcdm. 
 We use the Bolshoi simulation to explore in what structures they
 reside and if there is any correlation or alignment with the cosmic
-web. 
-The large scale environment is defined by the cosmic web components identified by
-\citet{Tweb}, and we use the LG analogues computed by
+web.  The large scale environment is defined by the cosmic web
+components identified by \citet{Tweb}, and we use the LG analogues computed by
 \citet{lganalogues}.
@@
 The shaded region shows the expectation for a random
-  distribution without any preferential alignment, it encloses the $5\%$ and $95\%$ percentiles of 5000
+  distribution without any preferential alignment, it encloses the $5\%$ and $95\%$ percentiles of 10000
   flat distributions for $\mu$ generated with the  same number of
@@
  without any preferential alignment, it encloses the $5\%$ and $95\%$
- percentiles of 5000  flat distributions for $\mu$ generated with the
+ percentiles of 10000  flat distributions for $\mu$ generated with the
  same number of points as the $2\sigma$ sample.   
@@
 third eigenvector. 
-With respect to the second eigenvector the distribution is consistent
+With respect to the first and second eigenvector the distribution is consistent
 with no alignment. 
-While for the first eigenvector there is a strong alignment, an expected
-result considering the results with the other eigenvectors and
-keeping in mind that they are orthonormal.
 Second, the alignment strength changes for the different samples. 
@@
 
-In the GS we already see an anti-alignment signature with the third eigenvector,
-lower than for RS samples but still significant, this is an expected result,
-even for random pairs with separations of the same order of the scale-length of 
-underlying environment, just because individual pair members are more
-likely to lie  following the density distribution. For instance, in a
-filamentary density distribution, random  pairs are more likely to lie
-along the filament; and in walls, random pairs are more likely to lie
-in the wall.
-
-Can the increase of the alignment strength in the different samples be
-explained as a consequence of different mass dependencies as in the
-results in the previous section? The answer is no. 
-In Figure \ref{fig:median_alignment_n} we show the median of
-$\mu\equiv\hat{e}_i\cdot\hat{n}$ and $\mu\equiv \hat{e}_i\cdot\hat{r}$
-in different mass bins. 
+The alignment strength could be explained to a great extend by 
+a total mass dependency. In Figure \ref{fig:median_alignment_n} we
+show the median of $\mu\equiv\hat{e}_i\cdot\hat{n}$ and $\mu\equiv
+\hat{e}_i\cdot\hat{r}$ in different mass bins. 
 Lines show the median $\mu$-mass relation for the three
@@
 10^{12}$ \msun in the RS samples, the median of $\mu$ clearly from the
-2$\sigma$ and 3$\sigma$ samples clearly differs from the GS results.
-Although in the GS the alignments have slight changes with mass, this
-is not enough to explain the results for the reduced samples.
+2$\sigma$ and 3$\sigma$ samples clearly differs from the GS
+results. However, the uncertainty level on the median for a small
+sample (indicated by the shaded region) makes this trend compatible
+with the values from the GS sample.
 
-We also explored the main orbit differences between the GS and RS
-which could be responsible of this alignment strength feature, and we
-have that RS samples constraints the tangential velocity, then pair
-orbits are more eccentric as we tighten pair constraints, and for GS sample there is no tangential velocity constraint at all.
-Therefore, to study any relation between orbit eccentricity and alignment, we 
-computed for each halo pair in all samples, an approximate orbit 
+We also explored characteristics in the orbits which could be
+responsible of the strengthen alignment feature. We  
+have that RS samples constrains the tangential velocity, as a
+consequence pair orbits are more eccentric as we tighten pair
+constraints. For the GS sample there is no tangential velocity
+constraint at all.
+We studied the relationship between orbit eccentricity and alignment
+computing for each halo pair in all samples an approximate orbit 
 eccentricity assuming a two body orbit with masses set as the virial 
 masses and initial conditions given by current velocity vector and separation.
-We found that eccentricity is not responsible for this alignment feature by
-selecting a subsample of GS having the same eccentricity than 
-2$\sigma$-3$\sigma$ samples where we found no increase in the alignment when
+We found that  selecting a subsample of GS having the same eccentricity than 
+2$\sigma$-3$\sigma$ samples does not increase in the alignment when
 compared with the full GS.
@@
 the $\hat{n}$ vector, the increasing strength of the
-$\hat{r}$ alignment cannot be explained by a selection on mass.
+$\hat{r}$ alignment can be explained to a great extenct by a selection
+on mass.
 
@@
 The absence of alignment for the spins is consistent with different studies of
-spin alingnemnt that mark the range $10^{12}$\Msun as either a transition mass
+spin alingnment that mark the range $10^{12}$\Msun as either a transition mass
 from alignment into anti-alignment or from no-alignment into alignment
@@
 
-However, the alignments with the cosmic web are 
-mass-independent and seem to be stronger once the kinematic constraints
-are imposed on the GS pairs. There is a clear anti-alignment between
+The alignments with the cosmic web have also a mass
+dependency. Although they seem to be stronger once the kinematic constraints
+are imposed on the GS pairs, the results are consistent with the
+a simple mass cut on the GS sample. There is a clear anti-alignment between
 the third eigenvector and the orbital angular momentum vector, meaning
@@
 
-The most interesting feature is that these alignments are
-tighter as we narrow the kinematic conditions of the LG towards the
-observed values. A deeper understanding requires the study of the full
-formation history and coevolution with the cosmic web, a task beyond
-the scope of the work presented here.
-
 How can we relate these alignments to the observed LG? 
@@
 located at high galactic latitudes forming a planar structure that
-forms an angle of $42^{\circ}-52^{\circ}$, $\mu=0.6-0.7$ with the
+forms an angle of $42^{\circ}-52^{\circ}$ ($\mu=0.6-0.7$) with the
 vector joining the MW and M31; while the M31 satellites are on a plane
@@
 \citep{2005ApJ...629..219Z,2008MNRAS.390.1133B} or almost over the plane
-defined by the $\hat{e}_2$ and $\hat{e}_3$ \cite{2014MNRAS.443.1274L}.
+defined by the $\hat{e}_2$ and $\hat{e}_3$ \citep{2014MNRAS.443.1274L}.
 
@@
 M31 and the plane of M31 satellites. Instead, this plane has
-$\mu=0.6-0.7$ with respect to these directions. The spatial location
-of MW satellites raise a potential contradiction with the average expectations
-from $\Lambda$CDM, a point that has been raised before
-\citep{Pawlowski2012,Pawlowski2014}.
+$\mu=0.6-0.7$ with respect to these directions. Therefore, we suggest
+that the spatial location of MW satellites raises a potential
+contradiction with the average expectations from $\Lambda$CDM, a point
+that has been mentioned before \citep{Pawlowski2012,Pawlowski2014}.
 
@@
 one could use mass reconstructions from large surveys
-\citep{2009MNRAS.394..398W,2011MNRAS.417.1303M,2014arXiv1407.3451W,2014arXiv1406.1004N}
-or filament finders \citep{2010MNRAS.407.1449G,2011MNRAS.414..350S} to
-select a LG sample to quantify the alignments with the surrounding
-filamentary structure. This would allow not only a direct
-quantification of how common are the LG alignments but also provide a
-new test of $\Lambda$CDM.  We thank the referee Noam Libeskind for
-suggestions that helped us to clarify and strenghten the results
-presented in the paper.
+\citep{2009MNRAS.394..398W,2011MNRAS.417.1303M,2014MNRAS.445..988N,
+  2014ApJ...794...94W} or filament finders
+\citep{2010MNRAS.407.1449G,2011MNRAS.414..350S} to select a LG sample
+to quantify the alignments with the surrounding filamentary
+structure. This would allow not only a direct quantification of how
+common are the LG alignments but also provide a new test of
+$\Lambda$CDM.
 
@@
 The authors would like to thank Andrey Kravtsov and Nelson Padilla
-for their useful comments; and Yehuda Hoffman for insightful
-conversations on the subject of the Local Group and the Cosmic Web. 
+for their useful comments; Yehuda Hoffman for insightful
+conversations on the subject of the Local Group and the Cosmic Web;
+and the referee Noam Libeskind  that helped us to clarify and
+strenghten the results presented in the paper. 
 \bibliographystyle{apj}
@@
 \end{document}
-
-Codis->spin
-http://adsabs.harvard.edu/abs/2012MNRAS.427.3320C
-
-I've just read the pre-print you had on the arXiv today (The Local Group in the Cosmic Web).
-You make some interesting comments about the distribution of the LG galaxies and their satellites, i.e.
-about a joint consideration of the MW-M31 orientation and their satellite systems.
-You might find it interesting that I have been working on this issue a lot lately (see in particular Pawlowski, Kroupa & Jerjen, 2013, MNRAS, 435, 1928 and Pawlowski & McGaugh, 2014, MNRAS, 440, 908).
-In addition to the satellite planes (VPOS around the MW, GPoA around M31), the more-distant dwarf galaxies in the LG are part of coherent and surprisingly symmetric structures, too.
-
-Concerning the idea that the distribution of satellite galaxies is shaped by the accretion of sub-halos along filaments, I'd like to point out that this effect is not strong enough to explain the observed, very narrow and coherent satellite structures (e.g.
-the recent Pawlowski et al.
-2014, MNRAS, 442, 2362, or Pawlowski et al., 2012, MNRAS, 424, 80).
-Thus, the accretion of sub-halos along filaments, as seen in dark matter simulations, is inconsistent with the observed satellite structures.
-A different explanation is required for the existence of the (co-orbiting) satellite planes.
-This might be a reason for the apparent conflict of your results and the filamentary

### 2014-10-27 paper/referee_reply.tex
latest referee reply

@@
 
-The points raised by the referee are boldfaced. Our reply follows each point.
+We thank the referee for a thorough report on our draft. We have
+addressed all the points stated in the report. The points raised by
+the referee are boldfaced. Our reply follows each point.
 
@@
 We have followed the advice from the referee. Now Figures 3, 4, 5 and
-6 include a shadowed region quantifying the expectations from a random
+6 include a shadowed region quantifying the expectation from a random
 distribution. The captions include an explanation on how the numbers
@@
 vectors with the same number of elemets as the 2sigma sample. We use
-the 2sigma sample to show the upper bound on the uncertainties.
+the smaller sample to estimate the upper bound on the uncertainties.
 
-These vectors have a random distributions. This allows us to build the
-integrated $\mu$ distributions. We repeat the exercise 10000 times to
-compute the median together with the $5\%$ and $95\%$ percentiles for
-the quantities of interest. In the case of Figures 3,4 and 6 it
-corresponds to the fraction of elements with values $<\mu$; in the
-case of Figure 5 it corresponds to the median value of $\mu$.
+These vectors have a random distribution. From them we build
+the integrated $\mu$ distributions with respected to a fixed
+vector. We repeat the exercise 10000 times to compute the median
+together with the $5\%$ and $95\%$ percentiles for the quantities of
+interest. In the case of Figures 3,4 and 6 it corresponds to the
+fraction of elements with values $<\mu$; in the case of Figure 5 it
+corresponds to the median value of $\mu$.
+
+With these error bars we still find that the alignments are
+significant different from the expectations of a random
+distribution. We also find that the different alignments in the
+different samples, at a fixed mass (Figure 6), are consistent between
+themselves.
 
@@
 
-We tested the robustness of our results with a smaller smoothing scale
-(0.7 Mpc, from the $512^3$ grid data available on the Multidark
-Database. This is mentioned in the paper.
+We tested the robustness of our results with a smoothing scale of 0.7
+Mpc, from the $512^3$ grid data available on the Multidark
+Database. This is now mentioned in the paper.
 
-Concerning a larger smoothing scale we base the robustness on already
+Concerning a larger smoothing scale we base the robustness on previously
 published results. In Forero-Romero et al. 2009  we presented a
@@
 fractions (VFF and MFF) for each web environment. We found that for
-the values of $\lambda_{th}\approx 2$ the VFF and MFF only change on
-the order of $5\%$. In the thorough paper by Cautun et al. 2014 they
+the values of $\lambda_{th}\approx 0.3$ the VFF and MFF only change on
+the order of $5\%$. In a thorough paper by Cautun et al. 2014 they
 also show that the web properties are insensitive to changes of factor
@@
 
-We have included a paragraph on this discussion.
+We have included a paragraph on this in the Results section.
 

### 2014-10-27 paper/main.tex
main includes the bib file

@@
 \bibliographystyle{apj}
-\bibliography{references}
+%\bibliography{references} 
+\begin{thebibliography}{48}
+\expandafter\ifx\csname natexlab\endcsname\relax\def\natexlab#1{#1}\fi
+
+\bibitem[{{Alonso} {et~al.}(2014){Alonso}, {Eardley}, \&
+  {Peacock}}]{Alonso2014}
+{Alonso}, D., {Eardley}, E., \& {Peacock}, J.~A. 2014, ArXiv e-prints
+
+\bibitem[{{Aragon-Calvo} {et~al.}(2011){Aragon-Calvo}, {Silk}, \&
+  {Szalay}}]{2011MNRAS.415L..16A}
+{Aragon-Calvo}, M.~A., {Silk}, J., \& {Szalay}, A.~S. 2011, \mnras, 415, L16
+
+\bibitem[{{Arag{\'o}n-Calvo} {et~al.}(2007){Arag{\'o}n-Calvo}, {van de
+  Weygaert}, {Jones}, \& {van der Hulst}}]{AragonCalvo2007}
+{Arag{\'o}n-Calvo}, M.~A., {van de Weygaert}, R., {Jones}, B.~J.~T., \& {van
+  der Hulst}, J.~M. 2007, \apjl, 655, L5
+
+\bibitem[{{Bailin} {et~al.}(2008){Bailin}, {Power}, {Norberg}, {Zaritsky}, \&
+  {Gibson}}]{2008MNRAS.390.1133B}
+{Bailin}, J., {Power}, C., {Norberg}, P., {Zaritsky}, D., \& {Gibson}, B.~K.
+  2008, \mnras, 390, 1133
+
+\bibitem[{{Cautun} {et~al.}(2014){Cautun}, {van de Weygaert}, {Jones}, \&
+  {Frenk}}]{Cautun2014}
+{Cautun}, M., {van de Weygaert}, R., {Jones}, B.~J.~T., \& {Frenk}, C.~S. 2014,
+  \mnras, 441, 2923
+
+\bibitem[{{Codis} {et~al.}(2012){Codis}, {Pichon}, {Devriendt}, {Slyz},
+  {Pogosyan}, {Dubois}, \& {Sousbie}}]{Codis2012}
+{Codis}, S., {Pichon}, C., {Devriendt}, J., {Slyz}, A., {Pogosyan}, D.,
+  {Dubois}, Y., \& {Sousbie}, T. 2012, \mnras, 427, 3320
+
+\bibitem[{{Courtois} {et~al.}(2013){Courtois}, {Pomar{\`e}de}, {Tully},
+  {Hoffman}, \& {Courtois}}]{2013AJ....146...69C}
+{Courtois}, H.~M., {Pomar{\`e}de}, D., {Tully}, R.~B., {Hoffman}, Y., \&
+  {Courtois}, D. 2013, \aj, 146, 69
+
+\bibitem[{{Cox} \& {Loeb}(2008)}]{2008MNRAS.386..461C}
+{Cox}, T.~J., \& {Loeb}, A. 2008, \mnras, 386, 461
+
+\bibitem[{{Fakhouri} \& {Ma}(2009)}]{2009MNRAS.394.1825F}
+{Fakhouri}, O., \& {Ma}, C.-P. 2009, \mnras, 394, 1825
+
+\bibitem[{{Forero-Romero}(2009)}]{2009MNRAS.399..762F}
+{Forero-Romero}, J.~E. 2009, \mnras, 399, 762
+
+\bibitem[{{Forero-Romero} {et~al.}(2014){Forero-Romero}, {Contreras}, \&
+  {Padilla}}]{ForeroRomero2014}
+{Forero-Romero}, J.~E., {Contreras}, S., \& {Padilla}, N. 2014, \mnras, 443,
+  1090
+
+\bibitem[{{Forero-Romero} {et~al.}(2013){Forero-Romero}, {Hoffman},
+  {Bustamante}, {Gottl{\"o}ber}, \& {Yepes}}]{2013ApJ...767L...5F}
+{Forero-Romero}, J.~E., {Hoffman}, Y., {Bustamante}, S., {Gottl{\"o}ber}, S.,
+  \& {Yepes}, G. 2013, \apjl, 767, L5
+
+\bibitem[{{Forero-Romero} {et~al.}(2009){Forero-Romero}, {Hoffman},
+  {Gottl{\"o}ber}, {Klypin}, \& {Yepes}}]{Tweb}
+{Forero-Romero}, J.~E., {Hoffman}, Y., {Gottl{\"o}ber}, S., {Klypin}, A., \&
+  {Yepes}, G. 2009, \mnras, 396, 1815
+
+\bibitem[{{Forero-Romero} {et~al.}(2011){Forero-Romero}, {Hoffman}, {Yepes},
+  {Gottl{\"o}ber}, {Piontek}, {Klypin}, \& {Steinmetz}}]{ForeroRomero2011}
+{Forero-Romero}, J.~E., {Hoffman}, Y., {Yepes}, G., {Gottl{\"o}ber}, S.,
+  {Piontek}, R., {Klypin}, A., \& {Steinmetz}, M. 2011, \mnras, 417, 1434
+
+\bibitem[{{Gonz{\'a}lez} {et~al.}(2013){Gonz{\'a}lez}, {Kravtsov}, \&
+  {Gnedin}}]{sat}
+{Gonz{\'a}lez}, R.~E., {Kravtsov}, A.~V., \& {Gnedin}, N.~Y. 2013, \apj, 770,
+  96
+
+\bibitem[{{Gonz{\'a}lez} {et~al.}(2014){Gonz{\'a}lez}, {Kravtsov}, \&
+  {Gnedin}}]{lganalogues}
+---. 2014, \apj, 793, 91
+
+\bibitem[{{Gonz{\'a}lez} \& {Padilla}(2010)}]{2010MNRAS.407.1449G}
+{Gonz{\'a}lez}, R.~E., \& {Padilla}, N.~D. 2010, \mnras, 407, 1449
+
+\bibitem[{{Hahn} {et~al.}(2007){Hahn}, {Carollo}, {Porciani}, \&
+  {Dekel}}]{Hahn2007}
+{Hahn}, O., {Carollo}, C.~M., {Porciani}, C., \& {Dekel}, A. 2007, \mnras, 381,
+  41
+
+\bibitem[{{Hinshaw} {et~al.}(2013){Hinshaw}, {Larson}, {Komatsu}, {Spergel},
+  {Bennett}, {Dunkley}, {Nolta}, {Halpern}, {Hill}, {Odegard}, {Page}, {Smith},
+  {Weiland}, {Gold}, {Jarosik}, {Kogut}, {Limon}, {Meyer}, {Tucker}, {Wollack},
+  \& {Wright}}]{hinshaw_etal13}
+{Hinshaw}, G., {Larson}, D., {Komatsu}, E., {Spergel}, D.~N., {Bennett}, C.~L.,
+  {Dunkley}, J., {Nolta}, M.~R., {Halpern}, M., {Hill}, R.~S., {Odegard}, N.,
+  {Page}, L., {Smith}, K.~M., {Weiland}, J.~L., {Gold}, B., {Jarosik}, N.,
+  {Kogut}, A., {Limon}, M., {Meyer}, S.~S., {Tucker}, G.~S., {Wollack}, E., \&
+  {Wright}, E.~L. 2013, \apjs, 208, 19
+
+\bibitem[{{Karachentsev}(2005)}]{2005AJ....129..178K}
+{Karachentsev}, I.~D. 2005, \aj, 129, 178
+
+\bibitem[{{Klypin} {et~al.}(2003){Klypin}, {Hoffman}, {Kravtsov}, \&
+  {Gottl{\"o}ber}}]{2003ApJ...596...19K}
+{Klypin}, A., {Hoffman}, Y., {Kravtsov}, A.~V., \& {Gottl{\"o}ber}, S. 2003,
+  \apj, 596, 19
+
+\bibitem[{{Klypin} \& {Holtzman}(1997)}]{1997astro.ph.12217K}
+{Klypin}, A., \& {Holtzman}, J. 1997, ArXiv Astrophysics e-prints
+
+\bibitem[{{Klypin} {et~al.}(2011){Klypin}, {Trujillo-Gomez}, \&
+  {Primack}}]{2011ApJ...740..102K}
+{Klypin}, A.~A., {Trujillo-Gomez}, S., \& {Primack}, J. 2011, \apj, 740, 102
+
+\bibitem[{{Kroupa} {et~al.}(2005){Kroupa}, {Theis}, \&
+  {Boily}}]{2005A&A...431..517K}
+{Kroupa}, P., {Theis}, C., \& {Boily}, C.~M. 2005, \aap, 431, 517
+
+\bibitem[{{Lee} \& {Shandarin}(1998)}]{1998ApJ...500...14L}
+{Lee}, J., \& {Shandarin}, S.~F. 1998, \apj, 500, 14
+
+\bibitem[{{Lemson} \& {Kauffmann}(1999)}]{1999MNRAS.302..111L}
+{Lemson}, G., \& {Kauffmann}, G. 1999, \mnras, 302, 111
+
+\bibitem[{{Li} \& {White}(2008)}]{2008MNRAS.384.1459L}
+{Li}, Y.-S., \& {White}, S.~D.~M. 2008, \mnras, 384, 1459
+
+\bibitem[{{Libeskind} {et~al.}(2013){Libeskind}, {Hoffman}, {Forero-Romero},
+  {Gottl{\"o}ber}, {Knebe}, {Steinmetz}, \& {Klypin}}]{Libeskind2013}
+{Libeskind}, N.~I., {Hoffman}, Y., {Forero-Romero}, J., {Gottl{\"o}ber}, S.,
+  {Knebe}, A., {Steinmetz}, M., \& {Klypin}, A. 2013, \mnras, 428, 2489
+
+\bibitem[{{Libeskind} {et~al.}(2014){Libeskind}, {Knebe}, {Hoffman}, \&
+  {Gottl{\"o}ber}}]{2014MNRAS.443.1274L}
+{Libeskind}, N.~I., {Knebe}, A., {Hoffman}, Y., \& {Gottl{\"o}ber}, S. 2014,
+  \mnras, 443, 1274
+
+\bibitem[{{Mei} {et~al.}(2007){Mei}, {Blakeslee}, {C{\^o}t{\'e}}, {Tonry},
+  {West}, {Ferrarese}, {Jord{\'a}n}, {Peng}, {Anthony}, \&
+  {Merritt}}]{2007ApJ...655..144M}
+{Mei}, S., {Blakeslee}, J.~P., {C{\^o}t{\'e}}, P., {Tonry}, J.~L., {West},
+  M.~J., {Ferrarese}, L., {Jord{\'a}n}, A., {Peng}, E.~W., {Anthony}, A., \&
+  {Merritt}, D. 2007, \apj, 655, 144
+
+\bibitem[{{Mu{\~n}oz-Cuartas} {et~al.}(2011){Mu{\~n}oz-Cuartas}, {M{\"u}ller},
+  \& {Forero-Romero}}]{2011MNRAS.417.1303M}
+{Mu{\~n}oz-Cuartas}, J.~C., {M{\"u}ller}, V., \& {Forero-Romero}, J.~E. 2011,
+  \mnras, 417, 1303
+
+\bibitem[{{Nuza} {et~al.}(2014){Nuza}, {Kitaura}, {He{\ss}}, {Libeskind}, \&
+  {M{\"u}ller}}]{2014MNRAS.445..988N}
+{Nuza}, S.~E., {Kitaura}, F.-S., {He{\ss}}, S., {Libeskind}, N.~I., \&
+  {M{\"u}ller}, V. 2014, \mnras, 445, 988
+
+\bibitem[{{Pawlowski} {et~al.}(2014){Pawlowski}, {Famaey}, {Jerjen}, {Merritt},
+  {Kroupa}, {Dabringhausen}, {L{\"u}ghausen}, {Forbes}, {Hensler}, {Hammer},
+  {Puech}, {Fouquet}, {Flores}, \& {Yang}}]{Pawlowski2014}
+{Pawlowski}, M.~S., {Famaey}, B., {Jerjen}, H., {Merritt}, D., {Kroupa}, P.,
+  {Dabringhausen}, J., {L{\"u}ghausen}, F., {Forbes}, D.~A., {Hensler}, G.,
+  {Hammer}, F., {Puech}, M., {Fouquet}, S., {Flores}, H., \& {Yang}, Y. 2014,
+  \mnras, 442, 2362
+
+\bibitem[{{Pawlowski} {et~al.}(2012){Pawlowski}, {Kroupa}, {Angus}, {de Boer},
+  {Famaey}, \& {Hensler}}]{Pawlowski2012}
+{Pawlowski}, M.~S., {Kroupa}, P., {Angus}, G., {de Boer}, K.~S., {Famaey}, B.,
+  \& {Hensler}, G. 2012, \mnras, 424, 80
+
+\bibitem[{{Pawlowski} {et~al.}(2013){Pawlowski}, {Kroupa}, \&
+  {Jerjen}}]{Pawlowski2013}
+{Pawlowski}, M.~S., {Kroupa}, P., \& {Jerjen}, H. 2013, \mnras, 435, 1928
+
+\bibitem[{{Riebe} {et~al.}(2013){Riebe}, {Partl}, {Enke}, {Forero-Romero},
+  {Gottl{\"o}ber}, {Klypin}, {Lemson}, {Prada}, {Primack}, {Steinmetz}, \&
+  {Turchaninov}}]{Riebe2013}
+{Riebe}, K., {Partl}, A.~M., {Enke}, H., {Forero-Romero}, J., {Gottl{\"o}ber},
+  S., {Klypin}, A., {Lemson}, G., {Prada}, F., {Primack}, J.~R., {Steinmetz},
+  M., \& {Turchaninov}, V. 2013, Astronomische Nachrichten, 334, 691
+
+\bibitem[{{Sandage} \& {Tammann}(1975)}]{1975ApJ...196..313S}
+{Sandage}, A., \& {Tammann}, G.~A. 1975, \apj, 196, 313
+
+\bibitem[{{Shaya} \& {Tully}(2013)}]{Shaya2013}
+{Shaya}, E.~J., \& {Tully}, R.~B. 2013, \mnras, 436, 2096
+
+\bibitem[{{Sheth} \& {Tormen}(2004)}]{2004MNRAS.350.1385S}
+{Sheth}, R.~K., \& {Tormen}, G. 2004, \mnras, 350, 1385
+
+\bibitem[{{Sohn} {et~al.}(2012){Sohn}, {Anderson}, \& {van der
+  Marel}}]{2012ApJ...753....7S}
+{Sohn}, S.~T., {Anderson}, J., \& {van der Marel}, R.~P. 2012, \apj, 753, 7
+
+\bibitem[{{Sousbie}(2011)}]{2011MNRAS.414..350S}
+{Sousbie}, T. 2011, \mnras, 414, 350
+
+\bibitem[{{Trowland} {et~al.}(2013){Trowland}, {Lewis}, \&
+  {Bland-Hawthorn}}]{Trowland2013}
+{Trowland}, H.~E., {Lewis}, G.~F., \& {Bland-Hawthorn}, J. 2013, \apj, 762, 72
+
+\bibitem[{{van der Marel} {et~al.}(2012{\natexlab{a}}){van der Marel}, {Besla},
+  {Cox}, {Sohn}, \& {Anderson}}]{2012ApJ...753....9V}
+{van der Marel}, R.~P., {Besla}, G., {Cox}, T.~J., {Sohn}, S.~T., \&
+  {Anderson}, J. 2012{\natexlab{a}}, \apj, 753, 9
+
+\bibitem[{{van der Marel} {et~al.}(2012{\natexlab{b}}){van der Marel},
+  {Fardal}, {Besla}, {Beaton}, {Sohn}, {Anderson}, {Brown}, \&
+  {Guhathakurta}}]{2012ApJ...753....8V}
+{van der Marel}, R.~P., {Fardal}, M., {Besla}, G., {Beaton}, R.~L., {Sohn},
+  S.~T., {Anderson}, J., {Brown}, T., \& {Guhathakurta}, P. 2012{\natexlab{b}},
+  \apj, 753, 8
+
+\bibitem[{{Wang} {et~al.}(2009){Wang}, {Mo}, {Jing}, {Guo}, {van den Bosch}, \&
+  {Yang}}]{2009MNRAS.394..398W}
+{Wang}, H., {Mo}, H.~J., {Jing}, Y.~P., {Guo}, Y., {van den Bosch}, F.~C., \&
+  {Yang}, X. 2009, \mnras, 394, 398
+
+\bibitem[{{Wang} {et~al.}(2014){Wang}, {Mo}, {Yang}, {Jing}, \&
+  {Lin}}]{2014ApJ...794...94W}
+{Wang}, H., {Mo}, H.~J., {Yang}, X., {Jing}, Y.~P., \& {Lin}, W.~P. 2014, \apj,
+  794, 94
+
+\bibitem[{{Zentner} {et~al.}(2005){Zentner}, {Kravtsov}, {Gnedin}, \&
+  {Klypin}}]{2005ApJ...629..219Z}
+{Zentner}, A.~R., {Kravtsov}, A.~V., {Gnedin}, O.~Y., \& {Klypin}, A.~A. 2005,
+  \apj, 629, 219
+
+\bibitem[{{Zhang} {et~al.}(2009){Zhang}, {Yang}, {Faltenbacher}, {Springel},
+  {Lin}, \& {Wang}}]{Zhang2009}
+{Zhang}, Y., {Yang}, X., {Faltenbacher}, A., {Springel}, V., {Lin}, W., \&
+  {Wang}, H. 2009, \apj, 706, 747
+
+\end{thebibliography}
 

### 2014-10-27 paper/main.tex
version para enviar
fixed minor typo in main

@@
 prolateness $-0.4<p<0.4$.  (iii) Strongly aligned with the cosmic web.
-The alignments are such that he pair orbital angular momentum tends to
+The alignments are such that the pair orbital angular momentum tends to
 be perpendicular to the smallest tidal eigenvector, $\hat{e}_3$, which
@@
 \begin{center}
-  \includegraphics[width=0.45\textwidth]{fig5a.pdf}
+  \includegraphics[width=0.45\textwidth]{fig5.pdf}
   \includegraphics[width=0.45\textwidth]{fig5b.pdf}
